### 2017-01-10 Simulation_Vignette.Rmd
Started RMarkdown vignette

---
title: "MSAD_PCA_Walkthrough"
author: "Gabriel Odom"
date: "January 9, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Multi-State Adaptive-Dynamic PCA Simulation

We create this package, `mvMonitor`, from the foundation laid by Kazor et al (2016). The `mvMonitor` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.

### The Interval Vector
We begin by simulating an autocorrelated interval-step vector $t$, where the autocorrelated errors of $t$ have initial value $\epsilon_1 \sim \mathcal{U}_{[a,b]}$, where $a = 0.01$ and $b = 2$. This $t$ vector will be sinusoidal with period $\omega = 7 * 24 * 60$ (signifying a weekly period in  minute-level observations) and autocorrelation component $\phi = 0.75$.
```{r t_vec_initialized}
omega <- 60 * 24 * 7
phi <- 0.75
a <- 0.01; b <- 2
mean_t_err <- 0.5 * (a + b) # mean of Uniform(0.01,2)
var_t_err <- (b - a) / 12 # variance of Uniform(0.01,2)

# Create an autocorrelated vector of errors for the random variable t
t_err <- vector(length = omega)
# Initialise the errors so that the overall mean and variance match the sim of
# Kazor et al.
t_err[1] <- rnorm(n = 1,
                  mean = mean_t_err * (1 - phi),
                  sd = sqrt(var_t_err * (1 - phi ^ 2)))
for(s in 2:omega){
  t_err[s] <- phi * t_err[(s - 1)] +
    (1 - phi) * rnorm(n = 1,
                      mean = mean_t_err * (1 - phi),
                      sd = sqrt(var_t_err * (1 - phi ^ 2)))
}

# Now for the vector itself
t_star <- vector(length = omega)
t_star[1] <- -cos(2 * pi / omega) + t_err[1]
for(s in 2:omega){
  t_star[s] <- -cos(2 * pi * s / omega) +
    phi * t_err[(s - 1)] + (1 - phi) * t_err[s]
}
# Now we scale the ts to match the ts from the Unif(0.01,2)
t_star_adj <- ((b - a) * (t_star - min(t_star))) /
  (max(t_star) - min(t_star)) + a
```
Now that we have created the underlying autocorrelated and non-stationary process vector $t$, we perform some simple confirmatory graphing techniques.

```{r t_vec_graphs, echo = FALSE}
plot(t_star_adj,
     type = "l",
     main = "Plot of t Scaled to [0.1,2]",
     xlab = "t")
pacf(t_star,
     main = "Partial ACF for the Series t")
```
```{r t_vec_summary}
mean(t_star); var(t_star)
cor(t_star_adj[2:omega], t_star_adj[1:(omega - 1)])
lmtest::dwtest(t_star_adj[2:omega] ~ t_star_adj[1:(omega - 1)])
```

###  Features and State Features
We will simulate three features, with each feaure operating under $k$ different states. We will use $<x(t), y(t), z(t)>$ instead of the $<x_1(t), x_2(t), x_3(t)>$ notation used in Kazor et al. This will assist us when we introduce feature states. Our state notation will be $<x_k(t), y_k(t), z_k(t)>$ for State $k$.

We create the three features under State 1 (normal operating conditions, or \emph{NOC}) as three functions of $t$:
\begin{align}
\textbf{x}(\textbf{t}) &\equiv \textbf{t} + \boldsymbol\varepsilon_1, \\
\textbf{y}(\textbf{t}) &\equiv \textbf{t} ^ 2 - 3 * \textbf{t} + \boldsymbol\varepsilon_2, \\
\textbf{z}(\textbf{t}) &\equiv -\textbf{t} ^ 3 + 3 * \textbf{t} ^ 2 + \boldsymbol\varepsilon_3,
\end{align}
where $\varepsilon_i \sim N(0, 0.01)$.

```{r state_1_init}
library(scatterplot3d)
library(magrittr)
library(dplyr)

normal_df <- data.frame(t = t_star_adj,
                        err1 = rnorm(n = omega, sd = sqrt(0.01)),
                        err2 = rnorm(n = omega, sd = sqrt(0.01)),
                        err3 = rnorm(n = omega, sd = sqrt(0.01)))

###  State 1  ###
normal_df %<>% mutate(x = t + err1,
                     y = t ^ 2 - 3 * t + err2,
                     z = -t ^ 3 + 3 * t ^ 2 + err3)

# plot(normal_df$t)
# plot(normal_df$x)
# plot(normal_df$y)
# plot(normal_df$z)
# scatterplot3d(x = normal_df$x,
#               y = normal_df$y,
#               z = normal_df$x)
# # It checks out

orig_state_mat <- normal_df %>% select(x,y,z) %>% as.matrix
```

Now we can create data for our other two states. These states will be scaled rotations of the current $<x,y,z>$ set. Thus, we need the `rot_and_scale3d()` function from the `Rotation_Playground.R` file.

```{r state_2_init}
source("inst/Rotation_Playground.R")

###  State 2  ###
state2_angles <- list(yaw = 0,
                      pitch = 90,
                      roll = 30)
state2_scales <- c(1,0.5,2)
state2_mat <- orig_state_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                               scale_factors = state2_scales)
scatterplot3d(state2_mat)

###  State 3  ###
state3_angles <- list(yaw = 90,
                      pitch = 0,
                      roll = -30)
state3_scales <- c(0.25,0.1,0.75)
state3_mat <- orig_state_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                               scale_factors = state3_scales)
scatterplot3d(state3_mat)

###  Combination and Cleaning  ###
# Now concatenate these vectors
normal_df$xState2 <- state2_mat[,1]
normal_df$yState2 <- state2_mat[,2]
normal_df$zState2 <- state2_mat[,3]
normal_df$xState3 <- state3_mat[,1]
normal_df$yState3 <- state3_mat[,2]
normal_df$zState3 <- state3_mat[,3]

# Add a State label column
normal_df %<>%
  mutate(state = rep(rep(c(1, 2, 3), each = 60), (24 / 3) * 7))

# Add a date-time column
normal_df %<>%
  mutate(dateTime = seq.POSIXt(from = as.POSIXct("2016-11-27 00:00:00 CST"),
                               by = "min", length.out = 10080))

###  Hourly Switching Process  ###
state1_df <- normal_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
state2_df <- normal_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
state3_df <- normal_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
normal_switch_df <- bind_rows(state1_df, state2_df, state3_df) %>%
  arrange(dateTime)

normal_switch_df %>%
  filter(state == 3) %>%
  select(x, y, z) %>%
  scatterplot3d(xlim = c(-2, 3),
                ylim = c(-3, 1),
                zlim = c(-1, 5))

normal_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d(xlim = c(-2, 3),
                ylim = c(-3, 1),
                zlim = c(-1, 5))

######  Fault Introduction  ###################################################
faultStart <- 8500

###  Fault 1A  ###
# Shift each <x, y, z> by 2
shift <- 2
fault1A_df <- normal_df %>%
  select(dateTime, state, t, x, y, z) %>%
  mutate(x = x + shift,
         y = y + shift,
         z = z + shift)
fault1A_mat <- fault1A_df %>% select(x,y,z) %>% as.matrix

# State 2
fault1A_S2_mat <- fault1A_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault1A_S2_mat)

# State 3
fault1A_S3_mat <- fault1A_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault1A_S3_mat)

# Now concatenate these vectors
fault1A_df$xState2 <- fault1A_S2_mat[,1]
fault1A_df$yState2 <- fault1A_S2_mat[,2]
fault1A_df$zState2 <- fault1A_S2_mat[,3]
fault1A_df$xState3 <- fault1A_S3_mat[,1]
fault1A_df$yState3 <- fault1A_S3_mat[,2]
fault1A_df$zState3 <- fault1A_S3_mat[,3]

# Hourly switching process
fault1A_state1_df <- fault1A_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault1A_state2_df <- fault1A_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault1A_state3_df <- fault1A_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault1A_switch_df <- bind_rows(fault1A_state1_df,
                               fault1A_state2_df,
                               fault1A_state3_df) %>%
  arrange(dateTime)

fault1A_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()

###  Fault 1B  ###
# Shift each x by 2
fault1B_df <- normal_df %>%
  select(dateTime, state, t, x, y, z) %>%
  mutate(x = x + shift)
fault1B_mat <- fault1B_df %>% select(x,y,z) %>% as.matrix

# State 2
fault1B_S2_mat <- fault1B_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault1B_S2_mat)

# State 3
fault1B_S3_mat <- fault1B_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault1B_S3_mat)

# Now concatenate these vectors
fault1B_df$xState2 <- fault1B_S2_mat[,1]
fault1B_df$yState2 <- fault1B_S2_mat[,2]
fault1B_df$zState2 <- fault1B_S2_mat[,3]
fault1B_df$xState3 <- fault1B_S3_mat[,1]
fault1B_df$yState3 <- fault1B_S3_mat[,2]
fault1B_df$zState3 <- fault1B_S3_mat[,3]

# Hourly switching process
fault1B_state1_df <- fault1B_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault1B_state2_df <- fault1B_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault1B_state3_df <- fault1B_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault1B_switch_df <- bind_rows(fault1B_state1_df,
                               fault1B_state2_df,
                               fault1B_state3_df) %>%
  arrange(dateTime)

fault1B_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()

###  Fault 2A  ###
# Drift each <x, y, z> by (step - faultStart) / 10 ^ 3
drift_vec <- (1:omega - faultStart) / 10 ^ 3
drift_vec[drift_vec < 0] <- 0
fault2A_df <- normal_df %>%
  select(dateTime, state, t, x, y, z) %>%
  mutate(x = x + drift_vec,
         y = y + drift_vec,
         z = z + drift_vec)
fault2A_mat <- fault2A_df %>% select(x,y,z) %>% as.matrix

# State 2
fault2A_S2_mat <- fault2A_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault2A_S2_mat)

# State 3
fault2A_S3_mat <- fault2A_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault2A_S3_mat)

# Now concatenate these vectors
fault2A_df$xState2 <- fault2A_S2_mat[,1]
fault2A_df$yState2 <- fault2A_S2_mat[,2]
fault2A_df$zState2 <- fault2A_S2_mat[,3]
fault2A_df$xState3 <- fault2A_S3_mat[,1]
fault2A_df$yState3 <- fault2A_S3_mat[,2]
fault2A_df$zState3 <- fault2A_S3_mat[,3]

# Hourly switching process
fault2A_state1_df <- fault2A_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault2A_state2_df <- fault2A_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault2A_state3_df <- fault2A_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault2A_switch_df <- bind_rows(fault2A_state1_df,
                               fault2A_state2_df,
                               fault2A_state3_df) %>%
  arrange(dateTime)

fault2A_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()

###  Fault 2B  ###
# Drift each <y, z> by (step - faultStart) / 10 ^ 3
fault2B_df <- normal_df %>%
  select(dateTime, state, t, x, y, z) %>%
  mutate(y = y + drift_vec,
         z = z + drift_vec)
fault2B_mat <- fault2B_df %>% select(x,y,z) %>% as.matrix

# State 2
fault2B_S2_mat <- fault2B_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault2B_S2_mat)

# State 3
fault2B_S3_mat <- fault2B_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault2B_S3_mat)

# Now concatenate these vectors
fault2B_df$xState2 <- fault2B_S2_mat[,1]
fault2B_df$yState2 <- fault2B_S2_mat[,2]
fault2B_df$zState2 <- fault2B_S2_mat[,3]
fault2B_df$xState3 <- fault2B_S3_mat[,1]
fault2B_df$yState3 <- fault2B_S3_mat[,2]
fault2B_df$zState3 <- fault2B_S3_mat[,3]

# Hourly switching process
fault2B_state1_df <- fault2B_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault2B_state2_df <- fault2B_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault2B_state3_df <- fault2B_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault2B_switch_df <- bind_rows(fault2B_state1_df,
                               fault2B_state2_df,
                               fault2B_state3_df) %>%
  arrange(dateTime)

fault2B_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()

###  Fault 3A  ###
# Amplify t for each <x, y, z> by 3 * (omega - step) * t / (2 * omega)
amplify_vec <- 2 * (1:omega - faultStart) / (omega - faultStart) + 1
amplify_vec[amplify_vec < 1] <- 1
fault3A_df <- normal_df %>%
  select(dateTime, state, t, err1, err2, err3) %>%
  mutate(t = amplify_vec * t) %>%
  mutate(x = t + err1,
         y = t ^ 2 - 3 * t + err2,
         z = -t ^ 3 + 3 * t ^ 2 + err3)
fault3A_mat <- fault3A_df %>% select(x,y,z) %>% as.matrix

# State 2
fault3A_S2_mat <- fault3A_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault3A_S2_mat)

# State 3
fault3A_S3_mat <- fault3A_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault3A_S3_mat)

# Now concatenate these vectors
fault3A_df$xState2 <- fault3A_S2_mat[,1]
fault3A_df$yState2 <- fault3A_S2_mat[,2]
fault3A_df$zState2 <- fault3A_S2_mat[,3]
fault3A_df$xState3 <- fault3A_S3_mat[,1]
fault3A_df$yState3 <- fault3A_S3_mat[,2]
fault3A_df$zState3 <- fault3A_S3_mat[,3]

# Hourly switching process
fault3A_state1_df <- fault3A_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault3A_state2_df <- fault3A_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault3A_state3_df <- fault3A_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault3A_switch_df <- bind_rows(fault3A_state1_df,
                               fault3A_state2_df,
                               fault3A_state3_df) %>%
  arrange(dateTime)

fault3A_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()

###  Fault 3B  ###
# Dampen t for z by log|t|
t_log <- normal_df$t
t_log[faultStart:omega] <- log(t_log[faultStart:omega])
fault3B_df <- normal_df %>%
  select(dateTime, state, t, err1, err2, err3) %>%
  mutate(t_damp = t_log) %>%
  mutate(x = t + err1,
         y = t ^ 2 - 3 * t + err2,
         z = -t_damp ^ 3 + 3 * t_damp ^ 2 + err3)
fault3B_mat <- fault3B_df %>% select(x,y,z) %>% as.matrix

# State 2
fault3B_S2_mat <- fault3B_mat %*% rot_and_scale3d(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault3B_S2_mat)

# State 3
fault3B_S3_mat <- fault3B_mat %*% rot_and_scale3d(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault3B_S3_mat)

# Now concatenate these vectors
fault3B_df$xState2 <- fault3B_S2_mat[,1]
fault3B_df$yState2 <- fault3B_S2_mat[,2]
fault3B_df$zState2 <- fault3B_S2_mat[,3]
fault3B_df$xState3 <- fault3B_S3_mat[,1]
fault3B_df$yState3 <- fault3B_S3_mat[,2]
fault3B_df$zState3 <- fault3B_S3_mat[,3]

# Hourly switching process
fault3B_state1_df <- fault3B_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault3B_state2_df <- fault3B_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault3B_state3_df <- fault3B_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault3B_switch_df <- bind_rows(fault3B_state1_df,
                               fault3B_state2_df,
                               fault3B_state3_df) %>%
  arrange(dateTime)

fault3B_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()

######  The Seven Data Frames  ################################################
# The normal_df data frame is without fault. We will remove rows faultStart to
# omega, and replace these rows with the same rows from each each of the fault
# data frames.
# Turn all the data frames into xts objects for Kazor's function to work.
# NOTE - this follows a depreciated version of zoo, so we need the dateTime
# column as the rownames of the data frame, not as an index.
# EDITED NOTE - B. Barnard and I rebuilt Kazor's code as a functional package.
# The functions in these packages use xts matrices as inputs.
library(xts)
normal_switch_xts <- xts(normal_switch_df[,-1],
                         order.by = normal_switch_df[,1])

# Fault 1A
normal_w_fault1A_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                              fault1A_switch_df[faultStart:omega,])
fault1A_xts <- xts(normal_w_fault1A_df[,-1], order.by = normal_switch_df[,1])

# Fault 1B
normal_w_fault1B_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault1B_switch_df[faultStart:omega,])
fault1B_xts <- xts(normal_w_fault1B_df[,-1], order.by = normal_switch_df[,1])

# Fault 2A
normal_w_fault2A_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault2A_switch_df[faultStart:omega,])
fault2A_xts <- xts(normal_w_fault2A_df[,-1], order.by = normal_switch_df[,1])

# Fault 2B
normal_w_fault2B_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault2B_switch_df[faultStart:omega,])
fault2B_xts <- xts(normal_w_fault2B_df[,-1], order.by = normal_switch_df[,1])

# Fault 3A
normal_w_fault3A_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault3A_switch_df[faultStart:omega,])
fault3A_xts <- xts(normal_w_fault3A_df[,-1], order.by = normal_switch_df[,1])

# Fault 3B
normal_w_fault3B_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault3B_switch_df[faultStart:omega,])
fault3B_xts <- xts(normal_w_fault3B_df[,-1], order.by = normal_switch_df[,1])

faults_ls <- list(normal = normal_switch_xts,
                  fault1A = fault1A_xts,
                  fault1B = fault1B_xts,
                  fault2A = fault2A_xts,
                  fault2B = fault2B_xts,
                  fault3A = fault3A_xts,
                  fault3B = fault3B_xts)

# Double check that faults are visible and according to plan:
# faults_ls$fault1A %>% select(x) %>% plot.ts()
# faults_ls$fault1A %>% select(y) %>% plot.ts()
# faults_ls$fault1A %>% select(z) %>% plot.ts()
# faults_ls$fault1B %>% select(x) %>% plot.ts()
# faults_ls$fault1B %>% select(y) %>% plot.ts()
# faults_ls$fault1B %>% select(z) %>% plot.ts()
# faults_ls$fault2A %>% select(x) %>% plot.ts()
# faults_ls$fault2A %>% select(y) %>% plot.ts()
# faults_ls$fault2A %>% select(z) %>% plot.ts()
# faults_ls$fault2B %>% select(x) %>% plot.ts()
# faults_ls$fault2B %>% select(y) %>% plot.ts()
# faults_ls$fault2B %>% select(z) %>% plot.ts()
# faults_ls$fault3A %>% select(x) %>% plot.ts()
# faults_ls$fault3A %>% select(y) %>% plot.ts()
# faults_ls$fault3A %>% select(z) %>% plot.ts()
# faults_ls$fault3B %>% select(x) %>% plot.ts()
# faults_ls$fault3B %>% select(y) %>% plot.ts()
# faults_ls$fault3B %>% select(z) %>% plot.ts()
faults_ls$fault1A$x %>% plot.xts()
faults_ls$fault1A$y %>% plot.xts()
faults_ls$fault1A$z %>% plot.xts()
faults_ls$fault1B$x %>% plot.xts()
faults_ls$fault1B$y %>% plot.xts()
faults_ls$fault1B$z %>% plot.xts()
faults_ls$fault2A$x %>% plot.xts()
faults_ls$fault2A$y %>% plot.xts()
faults_ls$fault2A$z %>% plot.xts()
faults_ls$fault2B$x %>% plot.xts()
faults_ls$fault2B$y %>% plot.xts()
faults_ls$fault2B$z %>% plot.xts()
faults_ls$fault3A$x %>% plot.xts()
faults_ls$fault3A$y %>% plot.xts()
faults_ls$fault3A$z %>% plot.xts()
faults_ls$fault3B$x %>% plot.xts()
faults_ls$fault3B$y %>% plot.xts()
faults_ls$fault3B$z %>% plot.xts()

######  MSAD-PCA Implementation  ##############################################
# Sys.time()
# results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
#                          labelVector = faults_ls$normal[,1],
#                          trainObs = 2880,
#                          updateFreq = 1440)
# Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# # 1 second for 2880 train (two days), and 1440 update (one day).
# 
# falseAlarmRate_SPE <- sum(results_ls$Alarms[,1] == "Alarm") /
#   nrow(results_ls$Alarms)
# falseAlarmRate_T2 <- sum(results_ls$Alarms[,2] == "Alarm") /
#   nrow(results_ls$Alarms)
# 
# faultTime <- zoo::index(faults_ls$normal[faultStart,])
# # Why don't we have 10080 - 2880 rows in the Alarm matrix??
# str(results_ls$Alarms)

```

### 2017-01-10 Simulation_Vignette.Rmd
More vignette edits

@@
 # plot(normal_df$z)
-# scatterplot3d(x = normal_df$x,
-#               y = normal_df$y,
-#               z = normal_df$x)
 # # It checks out
@@
 orig_state_mat <- normal_df %>% select(x,y,z) %>% as.matrix
+```
+Let's take a look at our 3D scatterplot:
+```{r state1_scatter}
+scatterplot3d(x = normal_df$x,
+              y = normal_df$y,
+              z = normal_df$x)
 ```
@@
 Thus, we need the `rot_and_scale3d()` function from the `Rotation_Playground.R` file.
-
+The first state is yaw, pitch, and roll rotated by (0, 90, 30) degrees, and the scales are multiplied by (1, 0.5, 2).
 ```{r state_2_init}
@@
                                                scale_factors = state2_scales)
+```
+We can see the effects of the rotation and scaling.
+```{r state_2_scatter}
 scatterplot3d(state2_mat)
-
+```
+The second state is yaw, pitch, and roll rotated by (90, 0, -30) degrees, and the scales are multiplied by (0.25, 0.1, 0.75).
+```{r state_3_init}
 ###  State 3  ###
@@
                                                scale_factors = state3_scales)
+```
+We can see the difference that State 3 creates.
+```{r state_3_scatter}
 scatterplot3d(state3_mat)
+```
 
+Now, let's combine all these state observations into one data frame, which we will then subset based on the state indicator.
+```{r combine_state_data}
 ###  Combination and Cleaning  ###
@@
   arrange(dateTime)
+```
+
+Let's take 
+```{r}
 

### 2017-01-12 Simulation_Vignette.Rmd
Large commit from offline work.

@@
 
-Let's take 
-```{r}
+Let's take a look at the individual states, and their combined product.
+```{r state_scatterplots}
+
+normal_switch_df %>%
+  filter(state == 1) %>%
+  select(x, y, z) %>%
+  scatterplot3d(xlim = c(-2, 3),
+                ylim = c(-3, 1),
+                zlim = c(-1, 5))
+
+normal_switch_df %>%
+  filter(state == 2) %>%
+  select(x, y, z) %>%
+  scatterplot3d(xlim = c(-2, 3),
+                ylim = c(-3, 1),
+                zlim = c(-1, 5))
 
@@
                 zlim = c(-1, 5))
+```
 
-######  Fault Introduction  ###################################################
+###  Fault Introduction
+We now create the faults for individual states and all states.
+We will introduce these faults 1000 time units after the end of training (to evauluate false positive rates).
+The first fault is to add 2 to each $<\textbf{x}(\textbf{t}), \textbf{y}(\textbf{t}), \textbf{z}(\textbf{t})>$.
+```{r fault1A_intro}
 faultStart <- 8500
@@
   arrange(dateTime)
-
+```
+Now, let's take a look at our process after introducing fault 1A.
+```{r fault1A_scatter}
 fault1A_switch_df %>%
@@
   scatterplot3d()
-
+```
+The second fault (Fault 1B) is to add 2 to feature $<\textbf{x}(\textbf{t})>$ only.
+```{r fault1B_intro}
 ###  Fault 1B  ###
@@
   arrange(dateTime)
-
+```
+We now look at the effect of Fault 1B on the scatterplot of the process.
+```{r fault1B_scatter}
 fault1B_switch_df %>%
@@
   scatterplot3d()
+```
 
+The third fault we introduce (Fault 2A) is a drift in each feature by $10 ^ {-3} * (\text{step} - 8500)$.
+```{r fault2A_intro}
 ###  Fault 2A  ###
@@
                                                   scale_factors = state2_scales)
-scatterplot3d(fault2A_S2_mat)
+# scatterplot3d(fault2A_S2_mat)
 
@@
                                                   scale_factors = state3_scales)
-scatterplot3d(fault2A_S3_mat)
+# scatterplot3d(fault2A_S3_mat)
 
@@
   arrange(dateTime)
-
+```
+Now we look at the scatterplot under this drift fault.
+```{r fault2A_scatter}
 fault2A_switch_df %>%
@@
   scatterplot3d()
+```
 
+The fourth fault we introduce (Fault 2B) is a drift in features $\textbf{y}$ and $\textbf{z}$ by $10 ^ {-3} * (\text{step} - 8500)$.
+```{r fault2B_intro}
 ###  Fault 2B  ###
@@
   arrange(dateTime)
-
+```
+We now inspect the effect of Fault 2B.
+```{r fault2B_scatter}
 fault2B_switch_df %>%
@@
   scatterplot3d()
+```
 
+Our fifth fault (Fault 3A) is to amplify the underlying $\textbf{t}$ signal vector as $\frac{3}{2 * 10080} * (10080 - \text{step}) * \textbf{t}$.
+```{r fault3A_intro}
 ###  Fault 3A  ###
@@
   arrange(dateTime)
-
+```
+Now inspect the effect of this fault
+```{r fault3A_scatter}
 fault3A_switch_df %>%
@@
   scatterplot3d()
-
+```
+Our last fault under consideration, Fault 3B, is a dampening fault to $\textbf{t}$ as $\log \textbf{t}$. As $\textbf{t}$ is bdd within $[0.01, 2]$, $\log\textbf{t}\in[-4.61, 0.7]$.
+```{r fault3B_intro}
 ###  Fault 3B  ###
@@
                                                   scale_factors = state2_scales)
-scatterplot3d(fault3B_S2_mat)
+# scatterplot3d(fault3B_S2_mat)
 
@@
                                                   scale_factors = state3_scales)
-scatterplot3d(fault3B_S3_mat)
+# scatterplot3d(fault3B_S3_mat)
 
@@
   arrange(dateTime)
-
+```
+We inspect the effect of the last fault on our scatterplot.
+```{r fault3B_scatter}
 fault3B_switch_df %>%
@@
   scatterplot3d()
+```
 
-######  The Seven Data Frames  ################################################
-# The normal_df data frame is without fault. We will remove rows faultStart to
-# omega, and replace these rows with the same rows from each each of the fault
-# data frames.
-# Turn all the data frames into xts objects for Kazor's function to work.
-# NOTE - this follows a depreciated version of zoo, so we need the dateTime
-# column as the rownames of the data frame, not as an index.
-# EDITED NOTE - B. Barnard and I rebuilt Kazor's code as a functional package.
-# The functions in these packages use xts matrices as inputs.
+###  The Seven Data Frames
+The normal_df data frame is without fault.
+We will remove rows 8500 to 10080, and replace these rows with the same rows from each each of the fault data frames.
+We then store each of these seven `xts` matrices in a list.
+
+Implementation notes: turn all the data frames into `xts` objects for Kazor's function to work, which we believe follows a depreciated version of `zoo`, so we need the `dateTime` column as the rownames of the data frame, not as an index.
+EDITED NOTE - B.
+Barnard and I rebuilt Kazor's code as a functional package called `mvMonitoring`.
+The functions in these packages use `xts` matrices as inputs.
+```{r fault_dataframes}
 library(xts)

### 2017-01-12 Simulation_Vignette.Rmd
Finished commenting the data generation portion. Now I'm moving to comment the individual functions themselves.

@@
                   fault3B = fault3B_xts)
+```
 
+### Feature Time-series Plots
+Now that we've created and stored these feature, we can use time-series plots to confirm our multi-state vision as well as quickly ascertain the fault behavior.
+```{r feature_ts_plots}
 # Double check that faults are visible and according to plan:
@@
 faults_ls$fault3B$z %>% plot.xts()
+```
 
-######  MSAD-PCA Implementation  ##############################################
-# Sys.time()
-# results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
-#                          labelVector = faults_ls$normal[,1],
-#                          trainObs = 2880,
-#                          updateFreq = 1440)
-# Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
-# # 1 second for 2880 train (two days), and 1440 update (one day).
-# 
-# falseAlarmRate_SPE <- sum(results_ls$Alarms[,1] == "Alarm") /
-#   nrow(results_ls$Alarms)
-# falseAlarmRate_T2 <- sum(results_ls$Alarms[,2] == "Alarm") /
-#   nrow(results_ls$Alarms)
-# 
-# faultTime <- zoo::index(faults_ls$normal[faultStart,])
-# # Why don't we have 10080 - 2880 rows in the Alarm matrix??
-# str(results_ls$Alarms)
+## Multi-State AD-PCA Implementation
+We now throw all this data we've just generated into our package.
+CURRENT ISSUES: remove only alarmed observations, not flagged observations.
+Set up a replicate structure to repeat this proccess 1000 times.
+```{r msad-pca}
+Sys.time()
+results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
+                         labelVector = faults_ls$normal[,1],
+                         trainObs = 2880,
+                         updateFreq = 1440)
+Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
+# 1 second for 2880 train (two days), and 1440 update (one day).
+
+falseAlarmRate_SPE <- sum(results_ls$Alarms[,1] == "Alarm") /
+  nrow(results_ls$Alarms)
+falseAlarmRate_T2 <- sum(results_ls$Alarms[,2] == "Alarm") /
+  nrow(results_ls$Alarms)
+
+faultTime <- zoo::index(faults_ls$normal[faultStart,])
+# Why don't we have 10080 - 2880 rows in the Alarm matrix??
+str(results_ls$Alarms)
 

### 2017-01-13 Simulation_Vignette.Rmd
Finished vignette edits

@@
 Sys.time()
-results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
+results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
                          labelVector = faults_ls$normal[,1],

### 2017-01-24 Simulation_Vignette.Rmd
Now removing only alarmed observations. CURRENT ISSUE: even when we drop alpha from 0.001 to 0.1, we don't see any alarmed observations. We'd expect to see a few just by random chance.

--- 2017-01-12 Simulation_Vignette.Rmd
@@
 Sys.time()
-results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
+results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
                          labelVector = faults_ls$normal[,1],
                          trainObs = 2880,
-                         updateFreq = 1440)
+                         updateFreq = 1440,
+                         alpha = 0.1)
 Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;

### 2017-01-24 R/faultFilter.R

@@ -65,10 +65,10 @@ faultFilter <- function(trainData,
   # 3 (the default value of faultsToTriggerAlarm) flagged observations in a row
   alarmCheck <- rep(TRUE, faultsToTriggerAlarm)
   for(i in faultsToTriggerAlarm:nrow(faultObj)){
-    if(all.equal(faultObj[(i - faultsToTriggerAlarm + 1):i,2]) == alarmCheck){
+    if(identical(faultObj[(i - faultsToTriggerAlarm + 1):i,2], alarmCheck)){
       faultObj[i,5] <- 1
     }
-    if(all.equal(faultObj[(i - faultsToTriggerAlarm + 1):i,4]) == alarmCheck){
+    if(identical(faultObj[(i - faultsToTriggerAlarm + 1):i,4], alarmCheck)){
       faultObj[i,5] <- 1
     }
   }

### 2017-01-24 R/processMonitor.R

@@ -30,8 +30,8 @@ processMonitor <- function(data,
                               faultsToTriggerAlarm = faultsToTriggerAlarm),
                         lazy_eval(ls)))
   fault_xts <- faultObj_ls$faultObj
-  obsToKeepNew <- faultObj_ls$nonFlaggedTestObs
-  obsToKeep <- faultObj_ls$nonFlaggedTestObs
+  obsToKeepNew <- faultObj_ls$nonAlarmedTestObs
+  obsToKeep <- faultObj_ls$nonAlarmedTestObs
 
   while(nrow(obsToKeepNew) == updateFreq){
     n <- nrow(obsToKeepNew)
@@ -55,16 +55,19 @@ processMonitor <- function(data,
       obsToKeep <- rbind(obsToKeep, obsToKeepNew)
     }
   }
+  faultNames <- colnames(fault_xts)
+  faultNames[5] <- "Alarm"
+  colnames(fault_xts) <- faultNames
 
   # browser()
 
   # alarms_xts1 <- faultAlarm(fault_xts,
   #                           faultsToTrigger = faultsToTriggerAlarm,
   #                           faultObs = NULL)
-  alarms_xts2 <- faultObj_ls$alarmedTestObs
+  alarms_xts <- faultObj_ls$alarmedTestObs
 
   list(FaultChecks = fault_xts,
        Non_Flagged_Obs = obsToKeep,
-       Alarms = alarms_xts2)
+       Alarms = alarms_xts)
 }
 

### 2017-01-24 R/threshold.R

@@ -8,7 +8,7 @@
 #' @export
 #'
 #' @examples
-threshold <- function(pca_object, alpha = 0.05, ...){
+threshold <- function(pca_object, alpha = 0.001, ...){
   UseMethod("threshold")
 }
 

### 2017-01-24 Simulation_Vignette.Rmd
Alarm identification and removal fixed. now the code is finding one alarm-worthy observation out of 1440 observations after training on 2880 observations. My instinct is that the T2 statistic is throwing the alarm, as there are 2.5x as many observations flagged by the T2 statistic as by the SPE statistic.

--- 2017-01-12 Simulation_Vignette.Rmd
@@
 Sys.time()
-results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
+results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
                          labelVector = faults_ls$normal[,1],
                          trainObs = 2880,
-                         updateFreq = 1440)
+                         updateFreq = 1440,
+                         alpha = 0.001,
+                         faultsToTriggerAlarm = 3)
 Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;

### 2017-01-24 R/faultFilter.R

@@ -63,12 +63,14 @@ faultFilter <- function(trainData,
 
   # Now we iterate through the faultObj xts object by row, checking when we see
   # 3 (the default value of faultsToTriggerAlarm) flagged observations in a row
-  alarmCheck <- rep(TRUE, faultsToTriggerAlarm)
+  alarmCheck <- rep(1, faultsToTriggerAlarm)
   for(i in faultsToTriggerAlarm:nrow(faultObj)){
-    if(identical(faultObj[(i - faultsToTriggerAlarm + 1):i,2], alarmCheck)){
+    x1 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i,2])
+    if(identical(x1, alarmCheck)){
       faultObj[i,5] <- 1
     }
-    if(identical(faultObj[(i - faultsToTriggerAlarm + 1):i,4], alarmCheck)){
+    x2 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i,4])
+    if(identical(x2, alarmCheck)){
       faultObj[i,5] <- 1
     }
   }

### 2017-01-24 Simulation_Vignette.Rmd
Added alarm codes to check method-specific false alarm rates: 1 = T2, 2 = SPE, 3 = Both. At three flags to trigger and alpha = 0.001, SPE throws no false alarms in 1440 rows and T2 throws 1. However, SPE throws no false alarms even when alpha is as large as 0.07, while for this alpha the T2 false alarm rate is nearly 16 percent.

@@
 
-falseAlarmRate_SPE <- sum(results_ls$Alarms[,1] == "Alarm") /
-  nrow(results_ls$Alarms)
-falseAlarmRate_T2 <- sum(results_ls$Alarms[,2] == "Alarm") /
-  nrow(results_ls$Alarms)
+# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
+falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
+  nrow(results_ls$FaultChecks)
+# The SPE false alarm rate hits 0 at alpha = 0.07.
+falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
+  nrow(results_ls$FaultChecks)
+# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
+# T2 statistic throws too many false alarms for my taste.
 
-faultTime <- zoo::index(faults_ls$normal[faultStart,])
-# Why don't we have 10080 - 2880 rows in the Alarm matrix??
-str(results_ls$Alarms)
-
+# Why don't we have 10080 - 2880 rows in the Alarm matrix?? We need to set the
+# simulation run so that this mspMonitor function crawls over all 10080 rows.
+# Right now, the code does not "learn" after each run. At each updateFreq, we
+# need the function to append the non-alarmed test data to the training data,
+# and then rerun mspMonitor on the next updateFreq observations.
 ```

### 2017-01-24 R/faultFilter.R

@@ -57,30 +57,31 @@ faultFilter <- function(trainData,
 
   # This bit will find the observations which have not been flagged by either
   # statistic. However, we need to find and report the alarmed observations as
-  # well. We first add a column for alarm status.
+  # well. We first add a column for SPE and T2 alarm status.
   faultObj <- cbind(faultObj, rep(0, nrow(faultObj)))
   # nonFlaggedObs <- faultObj[faultObj[,2] == FALSE & faultObj[,4] == FALSE, ]
 
   # Now we iterate through the faultObj xts object by row, checking when we see
   # 3 (the default value of faultsToTriggerAlarm) flagged observations in a row
   alarmCheck <- rep(1, faultsToTriggerAlarm)
+  # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
   for(i in faultsToTriggerAlarm:nrow(faultObj)){
-    x1 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i,2])
+    x1 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i, 4])
     if(identical(x1, alarmCheck)){
       faultObj[i,5] <- 1
     }
-    x2 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i,4])
+    x2 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i, 2])
     if(identical(x2, alarmCheck)){
-      faultObj[i,5] <- 1
+      faultObj[i,5] <- faultObj[i,5] + 2
     }
   }
   # We seperate out the non-alarmed observations, and we keep as many as we
   # need to update the algorithm.
-  nonAlarmedObs <- faultObj[faultObj[,5] != 1, ]
+  nonAlarmedObs <- faultObj[faultObj[,5] == 0, ]
   keptObsIndex <- head(index(nonAlarmedObs), n = updateFreq)
   keptObs <- testData[keptObsIndex]
 
-  alarmedObs <- faultObj[faultObj[,5] == 1, ]
+  alarmedObs <- faultObj[faultObj[,5] != 0, ]
 
   object <- list(faultObj = faultObj,
                  nonAlarmedTestObs = keptObs,

### 2017-01-24 R/processMonitor.R

@@ -59,12 +59,8 @@ processMonitor <- function(data,
   faultNames[5] <- "Alarm"
   colnames(fault_xts) <- faultNames
 
-  # browser()
-
-  # alarms_xts1 <- faultAlarm(fault_xts,
-  #                           faultsToTrigger = faultsToTriggerAlarm,
-  #                           faultObs = NULL)
   alarms_xts <- faultObj_ls$alarmedTestObs
+  colnames(alarms_xts) <- faultNames
 
   list(FaultChecks = fault_xts,
        Non_Flagged_Obs = obsToKeep,

### 2017-01-25 Simulation_Vignette.Rmd
CURRENT ISSUE: Number of alarmed and non-alarmed observations can be less than or even greater than the number of training observations. WTF?

@@
 # T2 statistic throws too many false alarms for my taste.
+# These values were before we split the update observations by a third. These
+# false alarm rates increased dramatically (0.19, 0.41), so we increased the 
+# number of training observations to 4320 (three days worth, up from 2880). The
+# false alarm rates dropped back, but not nearly as low (0.0031, 0.0884).
 
-# Why don't we have 10080 - 2880 rows in the Alarm matrix?? We need to set the
-# simulation run so that this mspMonitor function crawls over all 10080 rows.
-# Right now, the code does not "learn" after each run. At each updateFreq, we
-# need the function to append the non-alarmed test data to the training data,
-# and then rerun mspMonitor on the next updateFreq observations.
+# CURRENT ISSUE: The number of alarmed and non-alarmed observations does not
+# sum to 10080 - trainObs. For 2880 training observations, the sum of alarmed
+# and non-alarmed observations was 83 + 4195 = 4278 < 10080 - 2880 = 7200,
+# while for 4320 training observations, the sum was 506 + 5256 = 5762 > 10080 -
+# 4320 = 5760. What in the actual hell?
 ```

### 2017-01-25 Simulation_Vignette.Rmd
In processMonitor, we changed the n in the while() loop to be the total rows kept, rather than the rows kept after each iteration. I think this is the right thing to do, but I need to continue testing it. Further, I fixed the alarm_xts return. Previously it was only returning the alarmed observations from the last iteration of the while() loop. It now returns all the alarmed observations.
CURRENT ISSUE: we have an infectious off-by-one error in processMonitor. For three groups, the sum of the alarmed and non-alarmed observations is +6 over the total tested observations.

@@
                          labelVector = faults_ls$normal[,1],
-                         trainObs = 2880,
+                         trainObs = 4320,
                          updateFreq = 1440,

### 2017-01-25 R/faultFilter.R

@@ -83,6 +83,7 @@ faultFilter <- function(trainData,
 
   alarmedObs <- faultObj[faultObj[,5] != 0, ]
 
+  # The faultObj is an xts with the same number of observations as testData.
   object <- list(faultObj = faultObj,
                  nonAlarmedTestObs = keptObs,
                  alarmedTestObs = alarmedObs)

### 2017-01-25 R/processMonitor.R

@@ -36,7 +36,9 @@ processMonitor <- function(data,
   obsToKeep <- faultObj_ls$nonAlarmedTestObs
 
   while(nrow(obsToKeepNew) == updateFreq){
-    n <- nrow(obsToKeepNew)
+    # browser()
+    # How many ok observations have we found so far with faultFilter?
+    n <- nrow(obsToKeep)
     if(n < trainObs){
       trainData <- rbind(data[(n + 1):trainObs,], obsToKeep)
       }else{
@@ -46,11 +48,17 @@ processMonitor <- function(data,
     testTime <- index(obsToKeep[nrow(obsToKeep)])
     faultObj_ls <- do.call(faultFilter,
                            args = c(list(trainData = trainData,
+      # Train on all observations after the last observation in obsToKeep. This
+      # is what the date/ means for xts objects.
                                          testData = data[paste0(testTime, "/")],
                                          updateFreq = updateFreq,
                                          faultsToTriggerAlarm = faultsToTriggerAlarm),
                                     lazy_eval(ls)))
 
+    # Update the monitoring statistic values in the fault matrix. Because of
+    # the adaptive nature of the algorithm, many observations which would have
+    # been alarmed under the first run of faultFilter are now within normal
+    # limits. We update the fault matrix with new statistic values and flags.
     fault_xts[index(faultObj_ls$faultObj),] <- faultObj_ls$faultObj
     obsToKeepNew <- faultObj_ls$nonAlarmedTestObs
     if(nrow(obsToKeepNew) != 0){
@@ -61,8 +69,7 @@ processMonitor <- function(data,
   faultNames[5] <- "Alarm"
   colnames(fault_xts) <- faultNames
 
-  alarms_xts <- faultObj_ls$alarmedTestObs
-  colnames(alarms_xts) <- faultNames
+  alarms_xts <- fault_xts[fault_xts[,5] != 0, ]
 
   list(FaultChecks = fault_xts,
        Non_Alarmed_Obs = obsToKeep,

### 2017-01-25 Simulation_Vignette.Rmd
Returned the n calculation within the while() loop of processMonitor to its original value. I need to think about why I did that the way I did. Further, we resolved the off-by-one error: the "date/" subset operation for xts objects is the "date" and all following rows, rather than all rows following "date". This caused "date" to be counted twice for each run of the while() loop.

@@
 # false alarm rates dropped back, but not nearly as low (0.0031, 0.0884).
-
-# CURRENT ISSUE: The number of alarmed and non-alarmed observations does not
-# sum to 10080 - trainObs. For 2880 training observations, the sum of alarmed
-# and non-alarmed observations was 83 + 4195 = 4278 < 10080 - 2880 = 7200,
-# while for 4320 training observations, the sum was 506 + 5256 = 5762 > 10080 -
-# 4320 = 5760. What in the actual hell?
 ```

### 2017-01-25 R/processMonitor.R

@@ -38,7 +38,7 @@ processMonitor <- function(data,
   while(nrow(obsToKeepNew) == updateFreq){
     # browser()
     # How many ok observations have we found so far with faultFilter?
-    n <- nrow(obsToKeep)
+    n <- nrow(obsToKeepNew)
     if(n < trainObs){
       trainData <- rbind(data[(n + 1):trainObs,], obsToKeep)
       }else{
@@ -46,11 +46,13 @@ processMonitor <- function(data,
       }
 
     testTime <- index(obsToKeep[nrow(obsToKeep)])
+    # Train on all observations after the last observation in obsToKeep. This
+    # is what the date/ means for xts objects (date/ means that date and all
+    # after it, this is why we remove the first row).
+    testData <- data[paste0(testTime, "/")]
     faultObj_ls <- do.call(faultFilter,
                            args = c(list(trainData = trainData,
-      # Train on all observations after the last observation in obsToKeep. This
-      # is what the date/ means for xts objects.
-                                         testData = data[paste0(testTime, "/")],
+                                         testData = testData[-1,],
                                          updateFreq = updateFreq,
                                          faultsToTriggerAlarm = faultsToTriggerAlarm),
                                     lazy_eval(ls)))

### 2017-01-26 Simulation_Vignette.Rmd
Begin testing for "Dynamic" option addition. CURRENT ISSUE: when some states have alarms and others do not, how do we bind these together? How do we bind an xts object of zero width to an xts object with width?

@@
 Sys.time()
-results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
+results_ls <- mvMonitoring::mspTrain(data = faults_ls$normal[,2:4],
                          labelVector = faults_ls$normal[,1],
@@
                          alpha = 0.001,
-                         faultsToTriggerAlarm = 3)
+                         faultsToTriggerAlarm = 3,
+                         lagsIncluded = 2)
 Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;

### 2017-01-26 R/faultFilter.R

@@ -22,6 +22,8 @@ faultFilter <- function(trainData,
                         faultsToTriggerAlarm,
                         ...){
 
+  # browser()
+
   ls <- lazy_dots(...)
   muTrain <- colMeans(trainData)
   sigmaTrain <- cov(trainData)

### 2017-01-26 R/mspTrain.R

@@ -51,17 +51,16 @@ mspTrain <- function(data,
                        faultsToTriggerAlarm = 3,
                        ...){
 
-  # browser()
-
   ls <- lazy_dots(...)
 
   # Lag the data
   if(Dynamic == TRUE){
     data <- lag(zoo(data), 0:-lagsIncluded)
   }
+  data <- xts(data[-(1:lagsIncluded),])
 
   classes <- unique(labelVector)
-  classData <- cbind(labelVector, data)
+  classData <- cbind(labelVector[-(1:lagsIncluded),], data)
   data_ls <- lapply(1:length(classes), function(i){
     data_df <- classData[classData[,1] == classes[i],]
     data_df[, -1]

### 2017-01-26 R/processMonitor.R

@@ -28,11 +28,9 @@ processMonitor <- function(data,
 
   ls <- lazy_dots(...)
 
-  # browser()
-
   faultObj_ls <- do.call(faultFilter,
                 args = c(list(trainData = data[1:trainObs,],
-                              testData = data[(trainObs + 1):nrow(data)],
+                              testData = data[(trainObs + 1):nrow(data), ],
                               updateFreq = updateFreq,
                               faultsToTriggerAlarm = faultsToTriggerAlarm),
                         lazy_eval(ls)))

### 2017-01-28 Simulation_Vignette.Rmd
mspMonitor function written and partially documented, but tests fail somewhere in the faultDetect call. ERROR: observation %*% P : non-conformable arguments. However, this should not be the case, as the observations should be 1 * 9 row vectors and P is a 9 * 3 projection matrix. USE mspMonitor IN DEV ONLY.

@@
 We now throw all this data we've just generated into our package.
-CURRENT ISSUES: remove only alarmed observations, not flagged observations.
-Set up a replicate structure to repeat this proccess 1000 times.
 ```{r msad-pca}
@@
 ```
+
+## Test the Multi-State Monitoring function
+```{r test_msad-pca}
+# Create six observations with lags 0:2 included
+laggedTestObs <- faults_ls$normal[10073:10080, -1]
+laggedTestObs <- stats::lag(laggedTestObs, 0:-2)
+laggedTestObs <- cbind(faults_ls$normal[10073:10080, 1], laggedTestObs)
+laggedTestObs <- laggedTestObs[-(7:8),]
+mspMonitor(observations = laggedTestObs[,-1],
+           labelVector = laggedTestObs[,1],
+           trainingSummary = results_ls$TrainingSpecs)
+```

### 2017-01-28 R/faultFilter.R

@@ -101,18 +101,10 @@ faultFilter <- function(trainData,
   keptObsIndex <- head(index(nonAlarmedObs), n = updateFreq)
   keptObs <- testData[keptObsIndex]
 
-  # From the threshold object, we want to preserve the SPE and T2 threshold
-  # values, as well as the class-specific preojection matrices
-  critVals <- c(thresholdObj$SPE_threshold, thresholdObj$T2_threshold)
-  names(critVals) <- c("SPE", "T2")
-  projectionMatrix <- thresholdObj$projectionMatrix
-  trainSpecs_ls <- list(thresholds = critVals,
-                        projectionMatrix = projectionMatrix)
-
   # The faultObj is an xts with the same number of observations as testData.
   object <- list(faultObj = faultObj,
                  nonAlarmedTestObs = keptObs,
-                 trainSpecs = trainSpecs_ls)
+                 trainSpecs = thresholdObj)
   class(object) <- "fault_ls"
   object
 }

### 2017-01-28 R/mspMonitor.R

@@ -1,0 +1,51 @@
+#' Real-Time Process Monitoring Function
+#'
+#' @description
+#'
+#' @param observations an n * p xts matrix. For real-time monitoring via batch
+#' file, n = 1, so this must be a matrix of a single row.
+#' @param labelVector an n * 1 integer vector of class memberships
+#' @param trainingSummary the TrainingSpecs list returned by the mspTrain()
+#' function. This list contains --for each class-- the SPE and T2 thresholds,
+#' as well the projection matrix.
+#' @param ... Lazy dots for additional internal arguments
+#'
+#' @return an n * (p + 5) xts matrix, where the columns (p + 1):(p + 5) are the
+#' monitoring statistics and corresponding fault flags, and an empty alarm
+#' column
+#'
+#' @details
+#'
+#' @export
+#'
+#' @examples
+mspMonitor <- function(observations,
+                       labelVector,
+                       trainingSummary,
+                       ...){
+  classes <- unique(labelVector)
+  obsNames <- names(observations)
+
+  # If our user accidentally sends in a vector instead of an xts matrix
+  if(is.null(dim(observations))){
+    observations <- matrix(observations, nrow = 1)
+    warning("Observation not an xts object.", immediate. = TRUE)
+  }
+  classData <- cbind(labelVector, observations)
+
+  # Apply the fault detection function to each row, accounting for the chance
+  # that rows come from different classes
+  dataAndFaults <- lapply(1:nrow(classData), function(i){
+    faultObj <- faultDetect(threshold_object = trainingSummary[[classData[1,i]]],
+                            observation = classData[-1, i])
+    cbind(classData[,i], faultObj)
+  })
+  obsAndFlags <- do.call(rbind, dataAndFaults)
+  obsAndFlags <- cbind(obsAndFlags, 0)
+
+  # Reapply the names
+  faultObjNames <- c("SPE", "SPE_Flag", "T2", "T2_Flag", "Alarm")
+  names(obsAndFlags) <- append(obsNames, faultObjNames)
+
+  obsAndFlags
+}

### 2017-01-28 R/processMonitor.R

@@ -92,7 +92,7 @@ processMonitor <- function(data,
   alarmObs <- data[alarmIndex]
   alarms_xts <- cbind(alarmObs, alarms_xts)
 
-  # Training Thresholds and Projection Matrix
+  # thresholdObj: Training Thresholds and Projection Matrix
   trainSpecs <- faultObj_ls$trainSpecs
 
   list(FaultChecks = fault_xts,

### 2017-01-30 Simulation_Vignette.Rmd
Documentation completed for the mspMonitor function.

--- 2017-01-26 Simulation_Vignette.Rmd
@@
 # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
-falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
-  nrow(results_ls$FaultChecks)
+(falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
+  nrow(results_ls$FaultChecks))
 # The SPE false alarm rate hits 0 at alpha = 0.07.
-falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
-  nrow(results_ls$FaultChecks)
+(falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
+  nrow(results_ls$FaultChecks))
 # The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
@@
 ```
+
+## Test the Multi-State Monitoring function
+```{r test_msad-pca}
+# Create six observations with lags 0:2 included
+laggedTestObs <- faults_ls$normal[10073:10080, -1]
+laggedTestObs <- stats::lag(laggedTestObs, 0:-2)
+laggedTestObs <- cbind(faults_ls$normal[10073:10080, 1], laggedTestObs)
+laggedTestObs <- laggedTestObs[-(7:8),]
+testDataandFlags <- mspMonitor(observations = laggedTestObs[,-1],
+           labelVector = laggedTestObs[,1],
+           trainingSummary = results_ls$TrainingSpecs)
+```

### 2017-01-30 R/mspMonitor.R

@@ -1,6 +1,7 @@
 #' Real-Time Process Monitoring Function
 #'
-#' @description
+#' @description Monitor and flag (if necessary) incoming multivariate process
+#' observations
 #'
 #' @param observations an n * p xts matrix. For real-time monitoring via batch
 #' file, n = 1, so this must be a matrix of a single row.
@@ -14,7 +15,16 @@
 #' monitoring statistics and corresponding fault flags, and an empty alarm
 #' column
 #'
-#' @details
+#' @details This function is designed to be ran at specific time intervals
+#' (every 10 seconds, 30 seconds, 1 minute, 5 minutes, 10 minutes, etc), from a
+#' batch file which calls this function and mspWarning(). This function takes
+#' in the specific observations to monitor and their class memberships (if any)
+#' and returns an xts matrix of these observations concatenated with their flag
+#' status and an empty alarm column. Users should then append these rows onto
+#' the existing daily observations matrix. The mspWarning() function will then
+#' take in the daily observation xts matrix with rows returned by this function
+#' and check the monitoring statistic flag indicators to see if an alarm status
+#' has been reached. For further details, see the mspWarning() function.
 #'
 #' @export
 #'

### 2017-01-30 R/faultAlarm.R
Rewrote faultAlarm as mspWarning. Built and documented the function. Currently in testing. Function works as intended for some of the if() checks, but I'm still testing the others. Also, the mspMonitor function adds a column of NAs under Alarm, so that the user knows which rows have been checked. Finally, we moved the vignettes to a vignette file.

@@ -1,41 +1,0 @@
-#' The Alarm function
-#'
-#' @param faultsToTrigger
-#' @param faultObs
-#' @param faultDF
-#'
-#' @return
-#' @export
-#'
-#' @importFrom xts xts
-#' @importFrom zoo index
-#' @importFrom utils tail
-#'
-#' @examples
-faultAlarm <- function(faultDF, faultsToTrigger = 3, faultObs = NULL){
-  if(is.null(faultObs)){
-
-    SPE_alarm <- sapply(faultsToTrigger:nrow(faultDF), function(i){
-      ifelse(all(faultDF[(i - faultsToTrigger + 1):i, 2] == TRUE), "Alarm", "Normal")
-    })
-    T2_alarm <- sapply(faultsToTrigger:nrow(faultDF), function(i){
-      ifelse(all(faultDF[(i - faultsToTrigger + 1):i, 4] == TRUE), "Alarm", "Normal")
-    })
-    xts(matrix(c(SPE_alarm, T2_alarm), ncol = 2),
-        order.by = index(faultDF[faultsToTrigger:nrow(faultDF),]))
-
-  }else{
-
-    if(nrow(faultDF) >= faultsToTrigger){
-      check_xts <- rbind(tail(faultDF, n = 2), faultObs)
-      if(all(check_xts[,2]) == TRUE){
-        warning("SPE detects process fault.", immediate. = TRUE)
-      }
-      if(all(check_xts[,4]) == TRUE){
-        warning("T2 detects process fault.", immediate. = TRUE)
-      }
-    }
-
-  }
-}
-

### 2017-01-30 R/mspMonitor.R

@@ -51,7 +51,7 @@ mspMonitor <- function(observations,
     cbind(classData[i,], faultObj)
   })
   obsAndFlags <- do.call(rbind, dataAndFaults)
-  obsAndFlags <- cbind(obsAndFlags, 0)
+  obsAndFlags <- cbind(obsAndFlags, NA)
   colnames(obsAndFlags)[ncol(obsAndFlags)] <- "Alarm"
 
   obsAndFlags

### 2017-01-30 R/mspWarning.R

@@ -1,0 +1,68 @@
+#' The Alarm function
+#'
+#' @description Trigger an alarm, if necessary, for incoming multivariate
+#' process observations
+#'
+#' @param mspMonitor_object An xts matrix returned by the mspMonitor() function
+#' @param faultsToTriggerAlarm Specifies how many sequential faults will cause
+#' an alarm to trigger. Defaults to 3.
+#'
+#' @return An xts matrix of the same dimensions as mspMonitor_object, with a
+#' non-NA alarm status
+#'
+#' @details This function and the mspMonitor function are designed to be ran
+#' via a script within a batch. The file flow is as follows: every time
+#' interval, run the mspMonitor function to add a flag status to each incoming
+#' observation, and return this new xts matrix. Then, pass this same xts matrix
+#' to the mspWarning function, which will check if the process has recorded
+#' three or more sequential monitoring statistic flags in a row. Of note, since
+#' these functions are expected to be repeatedly ran in real time, this
+#' function will only check for an alarm within the last row of the xts matrix.
+#' To check multiple rows for an alarm state, please use the mspTrain function,
+#' which was designed to check multiple past observations.
+#'
+#' @export
+#'
+#'
+#' @examples
+mspWarning <- function(mspMonitor_object, faultsToTriggerAlarm = 3){
+  data_xts <- mspMonitor_object
+  n <- nrow(data_xts)
+
+  # If we see flags on the last row, then we continue
+  if(data_xts[n, "SPE_Flag"] == 1 || data_xts[n, "T2_Flag"] == 1){
+
+    # If we also have enough observations to even trigger an alarm, then we
+    # continue
+    if(n >= faultsToTriggerAlarm){
+
+      # We create the Alarm Standard
+      alarmCheck <- rep(1, faultsToTriggerAlarm)
+
+      # Now that we are checking the alarm state for observation n, we write a
+      # 0 over the previous NA value. This shows us that NAs mean the state for
+      # that specific observation have not been checked.
+      data_xts[n, "Alarm"] <- 0
+
+      # We now check the last few SPE flags
+      x1 <- as.vector(data_xts[(n - faultsToTriggerAlarm + 1):n, "SPE_Flag"])
+      if(identical(x1, alarmCheck)){
+        data_xts[n, "Alarm"] <- 1
+      }
+
[…]

### 2017-01-31 R/rotateScaleMatrix.R
Added the rotation and scaling matrix functions to the package as rotationMatrix() and rotateScaleMatrix(). The vignette file now builds completely, so our next step will be trying to build the PDF documentation file, again. (I've been working to clean up the vignette file for 5 hours now.)

@@ -1,0 +1,33 @@
+#' Three-Dimensional Rotation and Scaling Matrix
+#'
+#' @description Render a 3-Dimensional projection matrix given positive or
+#' negative degree changes in yaw, pitch, and / or roll and increment or
+#' decrement feature scales.
+#'
+#' @param rot_angles a list or vector containg the rotation angles in the order
+#' following: yaw, pitch, roll. Defaults to <0,0,0>.
+#' @param scale_factors a list or vector containing the values by which to
+#' multiply each dimension. Defaults to <1,1,1>.
+#'
+#' @return A 3 * 3 projection matrix of the degree and scale changes entered.
+#'
+#' @details See the function commentary of "rotate_3D" for a brief explination
+#' of how these angles behave in scatterplot3d functionality (from package
+#' scatterplot3d).
+#'
+#' @export
+#'
+#' @examples
+rotateScale3D <- function(rot_angles = c(0,0,0),
+                            scale_factors = c(1,1,1)){
+
+  rot_angles <- unlist(rot_angles)
+  yaw <- rot_angles[1]
+  pitch <- rot_angles[2]
+  roll <- rot_angles[3]
+
+  scale_factors <- unlist(scale_factors)
+  V <- diag(scale_factors, nrow = 3, ncol = 3)
+
+  rotate_3D(yaw, pitch, roll) %*% V
+}

### 2017-01-31 R/rotationMatrix.R

@@ -1,0 +1,44 @@
+#' Three-Dimensional Rotation Matrix
+#'
+#' @description Render a 3-Dimensional projection matrix given positive or
+#' negative degree changes in yaw, pitch, and / or roll.
+#'
+#' @param yaw z-axis change in degrees; look left (+) or right (-). Consider
+#' this a rotation on the x-y plane.
+#' @param pitch y-axis change in degrees; look up (-) or down (+). Consider
+#' this a rotation on the x-z plane.
+#' @param roll x-axis change in degrees; this change appears as if you touch
+#' head to shoulders: right roll (+) and left roll (-).
+#'
+#' @return A 3 * 3 projection matrix of the degree changes entered.
+#'
+#' @details When plotting with the package scatterplot3d, the default perpective
+#' is such that the pitch action appears as a roll while the roll action appears
+#' as a pitch.
+#'
+#' @export
+#'
+#' @examples
+rotate_3D <- function(yaw, pitch, roll){
+
+  thetaX <- roll * pi / 180
+  thetaY <- pitch * pi / 180
+  thetaZ <- yaw * pi / 180
+
+  Rx <- c(1,           0,            0,
+          0, cos(thetaX), -sin(thetaX),
+          0, sin(thetaX),  cos(thetaX))
+  Rx <- matrix(Rx, ncol = 3, nrow = 3)
+
+  Ry <- c( cos(thetaY),  0, sin(thetaY),
+           0,            1,           0,
+           -sin(thetaY), 0, cos(thetaY))
+  Ry <- matrix(Ry, ncol = 3, nrow = 3)
+
+  Rz <- c(cos(thetaZ), -sin(thetaZ), 0,
+          sin(thetaZ),  cos(thetaZ), 0,
+          0,            0,           1)
+  Rz <- matrix(Rz, ncol = 3, nrow = 3)
+
+  Rz %*% Ry %*% Rx
+}

### 2017-01-31 vignettes/Simulation_Vignette.R
FINALLY!!!! I managed to build the documentation PDF. It took, seriously, about 6 hours to figure out 1 god dang line of code. Next steps: add packages from the vignette as "suggested" packages, and work on writing function examples.

@@ -75,14 +75,15 @@ scatterplot3d(x = normal_df$x,
               z = normal_df$x)
 
 ## ----state_2_init--------------------------------------------------------
-source("C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring/inst/Rotation_Playground.R")
+# source("C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring/inst/Rotation_Playground.R")
+# source("Users\gabrielodom\Documents\GitHub\mvMonitoring\mvMonitoring\inst\Rotation_Playground.R")
 
 ###  State 2  ###
 state2_angles <- list(yaw = 0,
                       pitch = 90,
                       roll = 30)
 state2_scales <- c(1,0.5,2)
-state2_mat <- orig_state_mat %*% rot_and_scale3d(rot_angles = state2_angles,
+state2_mat <- orig_state_mat %*% mvMonitoring::rotateScale3D(rot_angles = state2_angles,
                                                scale_factors = state2_scales)
 
 ## ----state_2_scatter-----------------------------------------------------
@@ -94,7 +95,7 @@ state3_angles <- list(yaw = 90,
                       pitch = 0,
                       roll = -30)
 state3_scales <- c(0.25,0.1,0.75)
-state3_mat <- orig_state_mat %*% rot_and_scale3d(rot_angles = state3_angles,
+state3_mat <- orig_state_mat %*% mvMonitoring::rotateScale3D(rot_angles = state3_angles,
                                                scale_factors = state3_scales)
 
 ## ----state_3_scatter-----------------------------------------------------
@@ -175,12 +176,12 @@ fault1A_df <- normal_df %>%
 fault1A_mat <- fault1A_df %>% select(x,y,z) %>% as.matrix
 
 # State 2
-fault1A_S2_mat <- fault1A_mat %*% rot_and_scale3d(rot_angles = state2_angles,
+fault1A_S2_mat <- fault1A_mat %*% mvMonitoring::rotateScale3D(rot_angles = state2_angles,
                                                   scale_factors = state2_scales)
 scatterplot3d(fault1A_S2_mat)
 
 # State 3
-fault1A_S3_mat <- fault1A_mat %*% rot_and_scale3d(rot_angles = state3_angles,
[…]

### 2017-02-01 R/faultDetect.R
Package rough documentation complete. Still have problems building the PDF file on Windows. Made all edits, now pushing and switching to Mac.

@@ -1,25 +1,30 @@
-#' Fault Detection
+#' Process Fault Detection
 #'
-#' @description Detect if a single observation is beyond normal parameters
+#' @description Detect if a single multivariate observation is beyond normal
+#' parameters.
 #'
 #' @param threshold_object An object of classes "threshold" and "pca" returned
 #' by the internal threshold() function.
-#' @param observation A single row of an xts data matrix to test against the
+#' @param observation A single row of an xts data matrix to compare against the
 #' thresholds
 #' @param ... Lazy dots for additional internal arguments
 #'
-#' @return A named 1 row, 4 column matrix of the SPE statistic value ("SPE"),
+#' @return A named 1 * 4 matrix of the SPE statistic value ("SPE"),
 #' SPE fault indicator ("SPE_Flag"), T2 statistic value ("T2"), and T2 fault
 #' indicator for the single row observation passed to this function ("T2_Flag").
 #'
-#' @details This function takes in the threshold object returned by the
-#' threshold.R function and a single observation which needs fault detection.
-#' The function then returns a row vector of the SPE test statistics, a logical
-#' indicator indicating if this statistic is beyond the threshold, the T2
-#' statistic, and an indicator if this statistic is beyond the threshold. These
-#' threshold values are passed in through the threshold object after calculation
-#' from the training data set in the threshold() function.
-
+#' @details This function takes in a threshold object returned by the
+#' threshold() function and a single observation as a matrix or xts row. The
+#' function then returns a row vector of the SPE test statistics, a logical
+#' indicator marking if this statistic is beyond the threshold, the Hotelling's
+#' T2 statistic, and an indicator if this statistic is beyond the threshold.
+#' Observations with monitoring statistics beyond the calculated threshold are
+#' marked with a 1, while within-parameter observations are marked with a 0.
+#' These threshold values are passed from the threshold() function through this
+#' function via a returned threshold object. This object will be used in higher
+#' function calls.
+#'
+#' This internal function is called by faultFilter().
 #'
 #' @export
 #'

### 2017-02-01 R/faultFilter.R

@@ -1,29 +1,36 @@
-#' Fault Filtering
+#' Process Fault Filtering
 #'
-#' @description  Flag and filter out observations beyond normal parameters
+#' @description  Flag and filter out observations beyond normal parameters,
+#' then return the observations within normal operating conditions.
 #'
-#' @param trainData An xts data matrix of initial training observations. This
-#' will be updated by a rolling window
-#' @param testData The rest of the data, also updated by a rolling window
-#' @param updateFreq How many observations wide is the rolling window?
+#' @param trainData An xts data matrix of initial training observations
+#' @param testData The data not included in the training data set
+#' @param updateFreq How many observations from the test data matrix will be
+#' returned to update the training data matrix and move it forward?
 #' @param ... Lazy dots for additional internal arguments
 #' @param faultsToTriggerAlarm Specifies how many sequential faults will cause
 #' an alarm to trigger. Defaults to 3.
 #'
-#' @return A list of class "fault_ls" with the following: faultObj - an xts
-#' flag matrix with the same number of rows as "testData". This flag matrix has
-#' these columns - the SPE test statistic for each observation in "testData",
-#' an SPE indicator recording 0 if the test statistic is less than or equal to
-#' the critical value (from the threshold object), a T2 test statistic, a
-#' similar T2 indicator, and a final column indicating if there have been three
-#' flags in a row for either the SPE or T2 monitoring statistics or both;
-#' nonAlarmedTestObs - an xts matrix of all the rows of the training data which
-#' were not alarmed; trainSpecs - a list of: a vector of critical values from
-#' the SPE and T2 densities from the 1 - alpha quantile (see threshold()), and
-#' the class-specific projection matrix.
+#' @return A list of class "fault_ls" with the following: faultObj = an xts
+#' flagging matrix with the same number of rows as "testData". This flag matrix
+#' has the following five columns: the SPE test statistic for each observation
+#' in "testData", an SPE indicator recording 0 if the test statistic is less
+#' than or equal to the critical value passed through from the threshold object,
+#' a T2 test statistic, a similar T2 indicator, and a final column indicating
+#' if there have been three flags in a row for either the SPE or T2 monitoring
+#' statistics or both. nonAlarmedTestObs = an xts matrix of all the rows of the
+#' training data which were not alarmed. trainSpecs = the threshold object
+#' returned by the internal threshold() function. See this function's help file
+#' for more details.
 #'
[…]

### 2017-02-01 R/mspMonitor.R

@@ -1,30 +1,37 @@
 #' Real-Time Process Monitoring Function
 #'
 #' @description Monitor and flag (if necessary) incoming multivariate process
-#' observations
+#' observations.
 #'
-#' @param observations an n * p xts matrix. For real-time monitoring via batch
-#' file, n = 1, so this must be a matrix of a single row.
+#' @param observations an n * p xts matrix. For real-time monitoring via a
+#' script within a batch file, n = 1, so this must be a matrix of a single
+#' row.
 #' @param labelVector an n * 1 integer vector of class memberships
 #' @param trainingSummary the TrainingSpecs list returned by the mspTrain()
 #' function. This list contains --for each class-- the SPE and T2 thresholds,
 #' as well the projection matrix.
 #' @param ... Lazy dots for additional internal arguments
 #'
-#' @return an n * (p + 5) xts matrix, where the columns (p + 1):(p + 5) are the
+#' @return An n * (p + 5) xts matrix, where the last five columns are the
 #' monitoring statistics and corresponding fault flags, and an empty alarm
 #' column
 #'
 #' @details This function is designed to be ran at specific time intervals
 #' (every 10 seconds, 30 seconds, 1 minute, 5 minutes, 10 minutes, etc), from a
-#' batch file which calls this function and mspWarning(). This function takes
-#' in the specific observations to monitor and their class memberships (if any)
-#' and returns an xts matrix of these observations concatenated with their flag
-#' status and an empty alarm column. Users should then append these rows onto
-#' the existing daily observations matrix. The mspWarning() function will then
-#' take in the daily observation xts matrix with rows returned by this function
-#' and check the monitoring statistic flag indicators to see if an alarm status
-#' has been reached. For further details, see the mspWarning() function.
+#' batch file hosted script which calls this function and mspWarning(). This
+#' function takes in the specific observations to monitor and their class
+#' memberships (if any) and returns an xts matrix of these observations column
+#' concatenated with their monitoring statistic values, flag statuses, and an
+#' empty alarm column. Users should then append these rows onto a previously
+#' existing daily observations matrix. The mspWarning() function will then take
+#' in the daily observation xts matrix with updated rows returned by this
+#' function and check the monitoring statistic flag indicators to see if an
+#' alarm status has been reached. For further details, see the mspWarning()
+#' function.
+#'
+#' This function calls the faultDetect() function, and requires the training
+#' information returned by the mspTrain function. This function will return
+#' the xts matrix necessary for the mspWarning() function.
 #'
 #' @export
 #'

### 2017-02-01 R/mspTrain.R

@@ -16,37 +16,42 @@
 #' trigger an alarm
 #' @param ... Lazy dots for additional internal arguments
 #'
-#' @return A list of the following components: FaultChecks - an xts data matrix
-#' containing the SPE monitoring statistic and logical flagging indicator, the
-#' Hotelling's T2 monitoring statitisic and logical flagging indicator, and the
-#' Alarm indicator; Non_Alarmed_Obs - an xts data matrix of all the non-Alarmed
-#' observations; Alarms - and an xts data matrix of the features and specific
-#' alarms for Alarmed observations, where the alarm code is as follows: 0 = no
-#' alarm, 1 = Hotelling's T2 alarm, 2 = SPE alarm, and 3 = both alarms:
-#' TrainingSpecs - a list of k lists (one for each class) containing: a vector
-#' of class-specific critical values from the SPE and T2 densities from the 1 -
-#' alpha quantile (see the internal threshold() function), and the class-
-#' specific projection matrix.
+#' @return A list of the following components: FaultChecks = an xts data matrix
+#' containing the SPE monitoring statistic and corresponding logical flagging
+#' indicator, the Hotelling's T2 monitoring statitisic and corresponding logical
+#' flagging indicator, and the Alarm indicator. Non_Alarmed_Obs = an xts data
+#' matrix of all the non-Alarmed observations. Alarms = and an xts data matrix
+#' of the features and specific alarms for Alarmed observations, where the alarm
+#' code is as follows: 0 = no alarm, 1 = Hotelling's T2 alarm, 2 = Squared
+#' Prediction Error alarm, and 3 = both alarms. TrainingSpecs = a list of k
+#' lists, one for each class, with each list containing the specific threshold
+#' object returned by the internal threshold() function for that class. See this
+#' function's help file for more details.
 #'
 #' @details This function is designed to identify and sort out sequences of
 #' observations which fall outside normal operating conditions. We assume that
 #' the process data are time-dependent in both seasonal and non-stationary
 #' effects (which necessitate the Adaptive and Dynamic components, respectively).
-#' We further assume that this process data is drawn from a process under
+#' We further assume that this data is drawn from a multivariate process under
 #' multiple mutually exclusive states, implying that the linear dimension
 #' reduction projection matrices may be different for each state. Therefore, in
-#' summary, this function splits the data by classes, lags the features to
-#' account for correlation between sequential observations, and re-estimates
+#' summary, this function lags the features to account for correlation between
+#' sequential observations, splits the data by classes, and re-estimates
[…]

### 2017-02-01 R/mspWarning.R

@@ -1,25 +1,28 @@
-#' The Alarm function
+#' Process Alarms
 #'
 #' @description Trigger an alarm, if necessary, for incoming multivariate
-#' process observations
+#' process observations.
 #'
 #' @param mspMonitor_object An xts matrix returned by the mspMonitor() function
 #' @param faultsToTriggerAlarm Specifies how many sequential faults will cause
 #' an alarm to trigger. Defaults to 3.
 #'
 #' @return An xts matrix of the same dimensions as mspMonitor_object, with a
-#' non-NA alarm status
+#' recorded negative or positive and type-specific alarm status
 #'
-#' @details This function and the mspMonitor function are designed to be ran
-#' via a script within a batch. The file flow is as follows: every time
-#' interval, run the mspMonitor function to add a flag status to each incoming
-#' observation, and return this new xts matrix. Then, pass this same xts matrix
-#' to the mspWarning function, which will check if the process has recorded
+#' @details This function and the mspMonitor() function are designed to be ran
+#' via a script within a batch. The file flow is as follows: at each time
+#' interval, run the mspMonitor() function on the daily observation matrix to
+#' add a flag status to the most recent incoming observation in the matrix, and
+#' return this new xts matrix. Then, pass this updated daily observation matrix
+#' to the mspWarning() function, which will check if the process has recorded
 #' three or more sequential monitoring statistic flags in a row. Of note, since
 #' these functions are expected to be repeatedly ran in real time, this
 #' function will only check for an alarm within the last row of the xts matrix.
 #' To check multiple rows for an alarm state, please use the mspTrain function,
 #' which was designed to check multiple past observations.
+#'
+#' This function requires an xts matrix returned by the mspMonitor() function.
 #'
 #' @export
 #'

### 2017-02-01 R/pca.R

@@ -2,28 +2,31 @@
 #'
 #' @description Calculate the principal components analysis for a data matrix,
 #' and also find the squared prediction error (SPE) and Hotelling's T2 test
-#' statistic values for each observation in this data matrix
+#' statistic values for each observation in this data matrix.
 #'
 #' @param data A centred-and-scaled data matrix or xts matrix
 #' @param var.amnt How much energy should be preserved in the projection?
 #' Defaults to 0.95.
 #' @param ... Lazy dots for additional internal arguments
 #'
-#' @return A list of class "pca" with the following: projectionMatrix - the q
+#' @return A list of class "pca" with the following: projectionMatrix = the q
 #' eigenvectors corresponding to the q largest eigenvalues as a p * q projection
-#' matrix; LambdaInv - the diagonal matrix of inverse eigenvalues; SPE - the
+#' matrix. LambdaInv = the diagonal matrix of inverse eigenvalues. SPE = the
 #' vector of SPE test statistic values for each of the n observations contained
-#' in the data matrix; and T2 - the vector of Hotelling's T2 test statistic
+#' in the data matrix. T2 = the vector of Hotelling's T2 test statistic
 #' for each of the same n observations.
 #'
-#' @details This function takes in a training data matrix (without the label
-#' column) and the energy preservation proportion (defaulting to 95% per Kazor
-#' et al (2016)). This proportion is the sum of the q largest eigenvalues over
-#' the sum of all p eigenvalues, where q is the number of columns of the p * q
-#' projection matrix P. This function then returns the projection matrix P, a
-#' diagonal matrix of the reciprocal eigenvalues (LambdaInv), a vector of the
-#' SPE test statistic values corresponding to the rows of the data matrix, and
-#' a T2 test statistic vector similar to the SPE vector.
+#' @details This function takes in a training data matrix, without the label
+#' column, and the energy preservation proportion, which defaults to 95 percent
+#' per Kazor et al (2016). This proportion is the sum of the q largest
+#' eigenvalues divided by the sum of all p eigenvalues, where q is the number
+#' of columns of the p * q projection matrix P. This function then returns the
+#' projection matrix P, a diagonal matrix of the reciprocal eigenvalues
+#' (LambdaInv), a vector of the SPE test statistic values corresponding to the
+#' rows of the data matrix, and a T2 test statistic vector similar to the SPE
+#' vector.
+#'
+#' This internal function is called by faultFilter().
 #'
 #' @export
 #'

### 2017-02-01 R/processMonitor.R

@@ -5,25 +5,29 @@
 #' @param data An xts data matrix
 #' @param trainObs How many train observations will be used
 #' @param ... Lazy dots for additional internal arguments
-#' @param updateFreq How many non-flagged rows to collect before we update
+#' @param updateFreq How many non-flagged rows to collect before the function
+#' updates
 #' @param faultsToTriggerAlarm the number of sequential faults needed to
 #' trigger an alarm
 #'
-#' @return A list of the following components: FaultChecks - a class specific
-#' xts data matrix containing the SPE monitoring statistic and logical flagging
-#' indicator, the Hotelling's T2 monitoring statitisic and logical flagging
-#' indicator, and the Alarm indicator; Non_Alarmed_Obs - a class specific xts
-#' data matrix of all the non-Alarmed observations; Alarms - and a class
-#' specific xts data matrix of the features and specific alarms for Alarmed
-#' observations, where the alarm code is as follows: 0 = no alarm, 1 =
-#' Hotelling's T2 alarm, 2 = SPE alarm, and 3 = both alarms; trainSpecs - a
-#' list of: a vector of critical values from the SPE and T2 densities from the
-#' 1 - alpha quantile (see threshold()), and the class-specific projection
-#' matrix.
+#' @return A list of the following components: FaultChecks = a class specific
+#' xts data matrix containing the SPE monitoring statistic and corresponding
+#' logical flagging indicator, the Hotelling's T2 monitoring statitisic and
+#' corresponding logical flagging indicator, and the Alarm indicator.
+#' Non_Alarmed_Obs = a class specific xts data matrix of all the observations
+#' with alarm states equal to 0. Alarms = a class-specific xts data matrix of
+#' the features and specific alarms for Alarmed observations, where the alarm
+#' code is as follows: 0 = no alarm, 1 = Hotelling's T2 alarm, 2 = Squared
+#' Prediction Error alarm, and 3 = both alarms. trainSpecs = the threshold
+#' object returned by the internal threshold() function. See this function's
+#' help file for more details.
 #'
-#' @details This function is the class-specific implementation of the Adaptive
-#' PCA described in the details of the mspTrain function. See that function for
-#' further details.
+#' @details This function is the class-specific implementation of the Adaptive-
+#' Dynamic PCA described in the details of the mspTrain function. See that
+#' function's help file for further details.
+#'
+#' This internal function is called by mspTrain(). This function calls the
+#' faultFilter() function.
 #'
 #' @export
 #'

### 2017-02-01 R/rotateScaleMatrix.R

@@ -15,6 +15,9 @@
 #' of how these angles behave in scatterplot3d functionality (from package
 #' scatterplot3d).
 #'
+#' This function is used only in data generation of the package vignette. This
+#' function calls rotate3D().
+#'
 #' @export
 #'
 #' @examples
@@ -29,5 +32,5 @@ rotateScale3D <- function(rot_angles = c(0,0,0),
   scale_factors <- unlist(scale_factors)
   V <- diag(scale_factors, nrow = 3, ncol = 3)
 
-  rotate_3D(yaw, pitch, roll) %*% V
+  rotate3D(yaw, pitch, roll) %*% V
 }

### 2017-02-01 R/rotationMatrix.R

@@ -16,10 +16,13 @@
 #' is such that the pitch action appears as a roll while the roll action appears
 #' as a pitch.
 #'
+#' This function is used only in data generation of the package vignette. This
+#' function is called by rotateScale3D().
+#'
 #' @export
 #'
 #' @examples
-rotate_3D <- function(yaw, pitch, roll){
+rotate3D <- function(yaw, pitch, roll){
 
   thetaX <- roll * pi / 180
   thetaY <- pitch * pi / 180

### 2017-02-01 R/threshold.R

@@ -1,7 +1,7 @@
 #' Non-parametric Threshold Estimation
 #'
 #' @description Calculate the non-parametric critical value estimates for the
-#' SPE and T2 monitoring test statistics
+#' SPE and T2 monitoring test statistics.
 #'
 #' @param pca_object A list with class "pca" from the internal pca() function
 #' @param alpha The upper 1 - alpha quantile of the SPE and T2 densities from
@@ -9,19 +9,23 @@
 #' @param ... Lazy dots for additional internal arguments
 #'
 #' @return A list with classes "threshold" and "pca" containing: SPE_threshold
-#' - the 1 - alpha quantile of the SPE density; T2_threshold - the 1 - alpha
-#' quantile of the T2 density; projectionMatrix - a projection matrix from the
-#' data feature space to the feature subspace which preserves some specified
-#' proprtion of the energy of the data scatter matrix (this is the "var.amnt"
-#' argument in the pca() function); and LambdaInv - a diagonal matrix of the
-#' reciprocal eigenvalues of the data scatter matrix.
+#' = the 1 - alpha quantile of the SPE density. T2_threshold = the 1 - alpha
+#' quantile of the Hotelling's T2 density. projectionMatrix = a projection
+#' matrix from the data feature space to the feature subspace which preserves
+#' some specified proportion of the energy of the data scatter matrix. This
+#' specified energy proportion is user specified through the var.amnt argument
+#' in the pca() function. LambdaInv = a diagonal matrix of the reciprocal
+#' eigenvalues of the data scatter matrix.
 #'
-#' @details This function takes in a pca object returned by the pca.R function
-#' and a threshold level defaulting to 0.001% of the observations (set this low
-#' to reduce false alarms, as described in Kazor et al (2016)). The function
-#' returns a calculated SPE threshold corresponding to the 1 - alpha critical
-#' value, a similar T2 threshold, and the projection and Lambda Inverse (1 /
-#' eigenvalues) matrices passed through from the pca.R function call.
+#' @details This function takes in a pca object returned by the pca() function
+#' and a threshold level defaulting to 0.1% of the observations. The critical
+#' quantile is set this low to reduce false alarms, as described in Kazor et al
+#' (2016). The function then returns a calculated SPE threshold corresponding
+#' to the 1 - alpha critical value, a similar T2 threshold, and the projection
+#' and Lambda Inverse (1 / eigenvalues) matrices passed through from the pca()
+#' function call.
+#'
+#' This internal function is called by faultFilter().
 #'
 #' @export
 #'

### 2017-02-01 R/normal_switch_xts.R
Added rough documentation to the normal data set. Wrote a better description of the data generation process in the vignette.

@@ -1,0 +1,18 @@
+#'  Process Data under Normal Conditions
+#'
+#' @description Three-feature, three-state process data under normal operating
+#' conditions as example data for different included functions.
+#'
+#' @format An xts data matrix with 10080 rows, corresponding to one week worth
+#' of data recorded at a 1-minute interval, and four columns as defined here:
+#' \describe{
+#'   \item{state}{the state indicator for the multivariate system, with three
+#'   levels}
+#'   \item{x}{x(t) = t + error}
+#'   \item{y}{y(t) = t ^ 2 - 3t + error}
+#'   \item{z}{z(t) = - t ^ 3 + 3t ^ 2 + error}
+#' }
+#' where t is a 10080-entry vector of autocorrelated and non-stationary hidden
+#' process realizations. See the vignette for more details.
+#' @source Simluated in R.
+"normal_switch_xts"

### 2017-02-02 README.Rmd
Reduced running time for examples. Created an empty README.Rmd file, and added the Travis shield.

[![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)

### 2017-02-02 R/mspTrain.R

@@ -75,7 +75,7 @@
 #'
 #' @examples
 #' data("normal_switch_xts")
-#' nTrainObs <- floor(0.2 * nrow(normal_switch_xts))
+#' nTrainObs <- floor(0.4 * nrow(normal_switch_xts))
 #' # The state values are recorded in the first column.
 #'
 #' mspTrain(data = normal_switch_xts[, -1],

### 2017-02-02 R/processMonitor.R

@@ -39,7 +39,7 @@
 #' data("normal_switch_xts")
 #' # Select the data under state 1
 #' data <- normal_switch_xts[normal_switch_xts[,1] == 1]
-#' nTrainObs <- floor(0.2 * nrow(data))
+#' nTrainObs <- floor(0.4 * nrow(data))
 #'
 #' # Remove the now unnecesary state column
 #' featureCols <- data[,-1]

### 2017-02-02 README.Rmd
Updated link in Travis shield in README

@@
-[![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)
+[![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?token=ZzKTz9X2qQxWeqCPkaKq&branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)

### 2017-02-02 README.Rmd
Fixed incorrect lag code in vignette. Still need to fix this in mspTrain. Commented mspMonitor.

@@
+# Multi-State Adaptive-Dynamic Process Monitoring
+
 [![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?token=ZzKTz9X2qQxWeqCPkaKq&branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)
+
+## Overview
+We create this package, `mvMonitor`, from the foundation laid by Kazor et al (2016).
+The `mvMonitor` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.
+
+## Installation
+Make sure you have the latest version of the `devtools` package, and pull the package from GitHub.
+Remember, if you can read this file, you are one of the few people who have access to this package.
+In addition, you can also run the following:
+```{r packLoad_GitHub}
+devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
+```
+where you create the value of "tokenHere" by generating a personal access token (PAT) at https://github.com/settings/tokens and copying the quoted string to this argument.
+
+## Examples

### 2017-02-02 R/mspMonitor.R

@@ -5,7 +5,8 @@
 #'
 #' @param observations an n * p xts matrix. For real-time monitoring via a
 #' script within a batch file, n = 1, so this must be a matrix of a single
-#' row.
+#' row. If lags were included at the training step, then these observations
+#' will also have lagged features.
 #' @param labelVector an n * 1 integer vector of class memberships
 #' @param trainingSummary the TrainingSpecs list returned by the mspTrain()
 #' function. This list contains --for each class-- the SPE and T2 thresholds,
@@ -36,6 +37,27 @@
 #' @export
 #'
 #' @examples
+#' data("normal_switch_xts")
+#' # The state values are recorded in the first column.
+#' n <- nrow(normal_switch_xts)
+#' nTrainObs <- floor(0.4 * n)
+#'
+#' # Calculate the training summary, but save five observations for monitoring.
+#' trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
+#'                             labelVector = normal_switch_xts[1:(n - 5), 1],
+#'                             trainObs = nTrainObs,
+#'                             lagsIncluded = 1)
+#'
+#' # While training, we included 1 lag (the default), so we will also lag the
+#' # observations we will test.
+#' testObs <- normal_switch_xts[(n - 6):n, -1]
+#' testObs <- stats::lag(testObs, 0:1)
+#' testObs <- testObs[-1, ]
+#' testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
+#'
+#' mspMonitor(observations = testObs[, -1],
+#'            labelVector = testObs[, 1],
+#'            trainingSummary = trainResults_ls$TrainingSpecs)
 mspMonitor <- function(observations,
                        labelVector,
                        trainingSummary,

### 2017-02-02 R/mspWarning.R
Added mspWarning() example. Rebuilt the vignette .html and PDF files to account for the edits from the past two days. These edits do not include Dr. Hering's comments.

@@ -26,9 +26,35 @@
 #'
 #' @export
 #'
-#'
 #' @examples
-mspWarning <- function(mspMonitor_object, faultsToTriggerAlarm = 3){
+#' data("normal_switch_xts")
+#' # The state values are recorded in the first column.
+#' n <- nrow(normal_switch_xts)
+#' nTrainObs <- floor(0.4 * n)
+#'
+#' # Calculate the training summary, but save five observations for monitoring.
+#' trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
+#'                             labelVector = normal_switch_xts[1:(n - 5), 1],
+#'                             trainObs = nTrainObs,
+#'                             lagsIncluded = 1)
+#'
+#' # While training, we included 1 lag (the default), so we will also lag the
+#' # observations we will test.
+#' testObs <- normal_switch_xts[(n - 6):n, -1]
+#' testObs <- stats::lag(testObs, 0:1)
+#' testObs <- testObs[-1, ]
+#' testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
+#'
+#' # Run the monitoring function.
+#' dataAndFlags <- mspMonitor(observations = testObs[, -1],
+#'                            labelVector = testObs[, 1],
+#'                            trainingSummary = trainResults_ls$TrainingSpecs)
+#'
+#' # Alarm check the last row of the matrix returned by the mspMonitor function
+#' mspWarning(dataAndFlags)
+mspWarning <- function(mspMonitor_object,
+                       faultsToTriggerAlarm = 3){
+
   data_xts <- mspMonitor_object
   n <- nrow(data_xts)
 

### 2017-02-02 README.Rmd
Example added to README. Documentation first round complete.

@@
 ## Examples
+These are the examples shown in the help files for hte mspTrain(), mspMonitor(), and mspWarning() functions.
+```{r mspExamples}
+data("normal_switch_xts")
+# The state values are recorded in the first column.
+n <- nrow(normal_switch_xts)
+nTrainObs <- floor(0.4 * n)
+
+# Calculate the training summary, but save five observations for monitoring.
+trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
+                            labelVector = normal_switch_xts[1:(n - 5), 1],
+                            trainObs = nTrainObs,
+                            lagsIncluded = 1)
+
+trainResults_ls
+
+# While training, we included 1 lag (the default), so we will also lag the
+# observations we will test.
+testObs <- normal_switch_xts[(n - 6):n, -1]
+testObs <- stats::lag(testObs, 0:1)
+testObs <- testObs[-1, ]
+testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
+testObs
+
+# Run the monitoring function.
+dataAndFlags <- mspMonitor(observations = testObs[, -1],
+                           labelVector = testObs[, 1],
+                           trainingSummary = trainResults_ls$TrainingSpecs)
+
+dataAndFlags
+
+# Alarm check the last row of the matrix returned by the mspMonitor function
+mspWarning(dataAndFlags)
+```

### 2017-02-03 README.Rmd
Changed the lagsIncluded functionality in mspTrain(), the README, and the vignette. Updated the function description to account for these changes. Completed Dr. Hering's edits on mspMonitor(), mspTrain(), and mspWarning().

@@
                             trainObs = nTrainObs,
-                            lagsIncluded = 1)
+                            lagsIncluded = c(0,1))
 

### 2017-02-03 R/mspMonitor.R

@@ -1,34 +1,48 @@
 #' Real-Time Process Monitoring Function
 #'
 #' @description Monitor and flag (if necessary) incoming multivariate process
-#' observations.
+#'   observations.
 #'
-#' @param observations an n * p xts matrix. For real-time monitoring via a
-#' script within a batch file, n = 1, so this must be a matrix of a single
-#' row. If lags were included at the training step, then these observations
-#' will also have lagged features.
-#' @param labelVector an n * 1 integer vector of class memberships
+#' @param observations an n x p xts matrix. For real-time monitoring via a
+#'   script within a batch file, n = 1, so this must be a 1 x p matrix. If lags
+#'   were included at the training step, then these observations will also have
+#'   lagged features.
+#' @param labelVector an n x 1 integer vector of class memberships
 #' @param trainingSummary the TrainingSpecs list returned by the mspTrain()
-#' function. This list contains --for each class-- the SPE and T2 thresholds,
-#' as well the projection matrix.
+#'   function. This list contains---for each class---the SPE and T2 thresholds,
+#'   as well the projection matrix.
 #' @param ... Lazy dots for additional internal arguments
 #'
-#' @return An n * (p + 5) xts matrix, where the last five columns are the
-#' monitoring statistics and corresponding fault flags, and an empty alarm
-#' column
+#' @return An n x (p + 5) xts matrix, where the last five columns are:
+#'   \itemize{
+#'     \item{SPE -- }{the SPE statistic value for each observation
+#'       in "observations"}
+#'     \item{SPE_Flag -- }{a vector of SPE indicators recording 0 if the test
+#'       statistic is less than or equal to the critical value passed through
+#'       from the threshold object}
+#'     \item{T2 -- }{the T2 statistic value for each observation in
+#'       "observations"}
+#'     \item{T2_Flag -- }{a vector of T2 fault indicators, defined like
+#'       SPE_Flag}
+#'     \item{Alarm -- }{a column indicating if there have been three flags in a
+#'       row for either the SPE or T2 monitoring statistics or both. Alarm
+#'       states are as follows: 0 = no alarm, 1 = Hotelling's T2 alarm, 2 =
+#'       Squared Prediction Error alarm, and 3 = both alarms.}
+#'   }
 #'
-#' @details This function is designed to be ran at specific time intervals
-#' (every 10 seconds, 30 seconds, 1 minute, 5 minutes, 10 minutes, etc), from a
[…]

### 2017-02-03 R/mspTrain.R

@@ -1,70 +1,109 @@
 #' Multi-State Adaptive-Dynamic Process Training
 #'
 #' @description This function performs Multi-State Adaptive-Dynamic PCA on a
-#' data set with time-stamped observations.
+#'   data set with time-stamped observations.
 #'
 #' @param data An xts data matrix
-#' @param labelVector Class label vector (as logical or finite numeric)
+#' @param labelVector Class labels as a logical (two states only) or finite
+#'   numeric (two or more states) vector with length equal to the number of rows
+#'   in "data". For data with only one state, this will be a vector of 1s.
 #' @param trainObs The number of observations upon which to train the algorithm
 #' @param updateFreq The algorithm update frequency (defaulting to half as many
-#' observations as the training frequency)
-#' @param Dynamic Should the PCA algorithm include lagged variables? Defaults
-#' to TRUE
-#' @param lagsIncluded If Dynamic = TRUE, how many lags should be included?
-#' Defaults to 1.
-#' @param faultsToTriggerAlarm The number of sequential faults needed to
-#' trigger an alarm
+#'   observations as the training frequency)
+#' @param Dynamic Specify if the PCA algorithm should include lagged variables.
+#'   Defaults to TRUE.
+#' @param lagsIncluded A vector of lags to include. If Dynamic = TRUE, specify
+#'   which lags to include. Defaults to c(0, 1), signifying that the Dynamic
+#'   process observations will include current observations and observations
+#'   from one time step previous. See "Details" for more information.
+#' @param faultsToTriggerAlarm The number of sequential faults needed to trigger
+#'   an alarm. Defaults to 3
 #' @param ... Lazy dots for additional internal arguments
 #'
-#' @return A list of the following components: FaultChecks = an xts data matrix
-#' containing the SPE monitoring statistic and corresponding logical flagging
-#' indicator, the Hotelling's T2 monitoring statitisic and corresponding logical
-#' flagging indicator, and the Alarm indicator. Non_Alarmed_Obs = an xts data
-#' matrix of all the non-Alarmed observations. Alarms = and an xts data matrix
-#' of the features and specific alarms for Alarmed observations, where the alarm
-#' code is as follows: 0 = no alarm, 1 = Hotelling's T2 alarm, 2 = Squared
-#' Prediction Error alarm, and 3 = both alarms. TrainingSpecs = a list of k
-#' lists, one for each class, with each list containing the specific threshold
-#' object returned by the internal threshold() function for that class. See this
[…]

### 2017-02-03 R/mspWarning.R

@@ -1,26 +1,30 @@
 #' Process Alarms
 #'
 #' @description Trigger an alarm, if necessary, for incoming multivariate
-#' process observations.
+#'   process observations.
 #'
 #' @param mspMonitor_object An xts matrix returned by the mspMonitor() function
 #' @param faultsToTriggerAlarm Specifies how many sequential faults will cause
-#' an alarm to trigger. Defaults to 3.
+#'   an alarm to trigger. Defaults to 3.
 #'
 #' @return An xts matrix of the same dimensions as mspMonitor_object, with a
-#' recorded negative or positive and type-specific alarm status
+#'   recorded negative or positive and type-specific alarm status. Alarm codes
+#'   are: 0 = no alarm, 1 = Hotelling's T2 alarm, 2 = Squared Prediction Error
+#'   alarm, and 3 = both alarms.
 #'
 #' @details This function and the mspMonitor() function are designed to be ran
-#' via a script within a batch. The file flow is as follows: at each time
-#' interval, run the mspMonitor() function on the daily observation matrix to
-#' add a flag status to the most recent incoming observation in the matrix, and
-#' return this new xts matrix. Then, pass this updated daily observation matrix
-#' to the mspWarning() function, which will check if the process has recorded
-#' three or more sequential monitoring statistic flags in a row. Of note, since
-#' these functions are expected to be repeatedly ran in real time, this
-#' function will only check for an alarm within the last row of the xts matrix.
-#' To check multiple rows for an alarm state, please use the mspTrain function,
-#' which was designed to check multiple past observations.
+#'   via a scheduled task through Windows "Task Scheduler" or Macintosh OX
+#'   "launchd" application suites. The file flow is as follows: at each time
+#'   interval, run the mspMonitor() function on the matrix of daily observations
+#'   to add a flag status to the most recent incoming observation in the matrix,
+#'   and return this new xts matrix. Then, pass this updated daily observation
+#'   matrix to the mspWarning() function, which will check if the process has
+#'   recorded three or more sequential monitoring statistic flags in a row. Of
+#'   note, because these functions are expected to be repeatedly called in real
+#'   time, this function will only check for an alarm within the last row of the
+#'   xts matrix. To check multiple rows for an alarm state, please use the
+#'   mspTrain() function, which was designed to check multiple past
+#'   observations.
 #'
 #' This function requires an xts matrix returned by the mspMonitor() function.
 #'
[…]

### 2017-02-03 R/fault3B_xts.R
Fixed list presentation for the fault data files. Completed Dr. Hering's edits for the NOC data file.

@@ -10,21 +10,21 @@
 #'   fault is a signal dampening in the underlying determining t vector for the
 #'   "z" feature. The fault starts at row 8500, and the four columns under the
 #'   fault state are defined here:
-#' \describe{
-#'   \item{state}{the state indicator for the multivariate system, with three
+#' \itemize{
+#'   \item{state : }{the state indicator for the multivariate system, with three
 #'   levels}
-#'   \item{x}{x(t) = t + error}
-#'   \item{y}{y(t) = t ^ 2 - 3t + error}
-#'   \item{z}{z(t_*) = - (t_*) ^ 3 + 3(t_*) ^ 2 + error}
+#'   \item{x : }{x(t) = t + error}
+#'   \item{y : }{y(t) = t ^ 2 - 3t + error}
+#'   \item{z : }{z(t_*) = - (t_*) ^ 3 + 3(t_*) ^ 2 + error}
 #' }
 #' where t_* = log|t|, and t is a 10080-entry vector of autocorrelated and non-
 #' stationary hidden process realizations. The states alternate each hour and
 #' are defined as follows:
-#' \describe{
-#'   \item{State1}{As presented}
-#'   \item{State2}{Rotated by (yaw = 0, pitch = 90, roll = 30) and scaled by
+#' \itemize{
+#'   \item{State1 -- }{As presented}
+#'   \item{State2 -- }{Rotated by (yaw = 0, pitch = 90, roll = 30) and scaled by
 #'   (1 * x, 0.5 * y , 2 * z).}
-#'   \item{State3}{Rotated by (yaw = 90, pitch = 0, roll = -30) and scaled by
+#'   \item{State3 -- }{Rotated by (yaw = 90, pitch = 0, roll = -30) and scaled by
 #'   (0.25 * x, 0.1 * y , 0.75 * z).}
 #' }
 #' See the vignette for more details.

### 2017-02-03 R/nineDay_xts.R
Added data from K. Newhart. Edited the oneDay and nineDay files. The source data is a ten day file an a 12 hour file, but the 12 hour file is from the start of the training interval, so it is useless to test with. The new oneDay file is the last day of the original tenDay file, and we will use it to test the package. We thus trimmed the last daty from the training data, and saved it as nineDay.

@@ -1,0 +1,10 @@
+#'  Real Process Data for Training
+#'
+#' @description Data from the SM-MBR Bioreactor system over nine days. This data
+#'   will be used for training the mvMonitoring package.
+#'
+#' @format An xts matrix of 1,293 rows and 36 features recorded over
+#'   2017-01-17 at 00:10 to 2017-01-26 at 00:00.
+#'
+#' @source Kathryn Newhart
+"nineDay"

### 2017-02-03 R/oneDay_xts.R

@@ -1,0 +1,10 @@
+#'  Real Process Data for Testing
+#'
+#' @description Data from the SM-MBR Bioreactor system over 24 hours. This data
+#'   will be used for testing the mvMonitoring package.
+#'
+#' @format An xts matrix of 144 rows and 36 features recorded over
+#'   2017-01-26 at 00:10 to 2017-01-27 at 00:00.
+#'
+#' @source Kathryn Newhart
+"oneDay"

### 2017-02-03 R/mspTrain.R
Data cleaning of the testing and training data sets given to us by K. Newhart. We removed NA rows, and the 29th column, as this column is entirely 0 for days at a time. We also added a vector check to mspTrain.

@@ -139,6 +139,9 @@ mspTrain <- function(data,
   data <- xts(data[-(1:max(lagsIncluded)),])
 
   classes <- unique(labelVector)
+  if(is.vector(labelVector)){
+    labelVector <- matrix(labelVector, ncol = 1)
+  }
   classData <- cbind(labelVector[-(1:max(lagsIncluded)),], data)
   data_ls <- lapply(1:length(classes), function(i){
     data_df <- classData[classData[,1] == classes[i],]

### 2017-02-03 R/nineDay_xts.R

@@ -3,8 +3,8 @@
 #' @description Data from the SM-MBR Bioreactor system over nine days. This data
 #'   will be used for training the mvMonitoring package.
 #'
-#' @format An xts matrix of 1,293 rows and 36 features recorded over
+#' @format An xts matrix of 1,155 rows and 35 features recorded over
 #'   2017-01-17 at 00:10 to 2017-01-26 at 00:00.
 #'
 #' @source Kathryn Newhart
-"nineDay"
+"nineDay_clean"

### 2017-02-03 R/oneDay_xts.R

@@ -3,8 +3,8 @@
 #' @description Data from the SM-MBR Bioreactor system over 24 hours. This data
 #'   will be used for testing the mvMonitoring package.
 #'
-#' @format An xts matrix of 144 rows and 36 features recorded over
+#' @format An xts matrix of 144 rows and 35 features recorded over
 #'   2017-01-26 at 00:10 to 2017-01-27 at 00:00.
 #'
 #' @source Kathryn Newhart
-"oneDay"
+"oneDay_clean"

### 2017-02-03 R/mspMonitor.R
Added real data analysis section to the vignette, and added a vector check to mspMonitor().

@@ -84,6 +84,10 @@ mspMonitor <- function(observations,
     observations <- matrix(observations, nrow = 1)
     warning("Observation not an xts object.", immediate. = TRUE)
   }
+
+  if(is.vector(labelVector)){
+    labelVector <- matrix(labelVector, ncol = 1)
+  }
   classData <- cbind(labelVector, observations)
 
   # Apply the fault detection function to each row, accounting for the chance

### 2017-02-03 README.Rmd
Fixed stats::lag, zoo::zoo, and xts::xts data interaction. Without the explicit package calls, the lags are interpreted backwards. Added an escape clause to faultFilter to ensure that the number of test rows is at least the number of consecutive flags to trigger an alarm. Further, I completely re-ran all the real data import, cleaning, and analysis code from the vignette. We are still seeing all alarms for the real data. I'd like to get a lot more training observations to test with before I dig back in to the code.

--- 2017-02-02 README.Rmd
@@
                             trainObs = nTrainObs,
-                            lagsIncluded = 1)
+                            lagsIncluded = c(0, -1))
 
@@
 testObs <- normal_switch_xts[(n - 6):n, -1]
-testObs <- stats::lag(testObs, 0:1)
-testObs <- testObs[-1, ]
+testObs <- stats::lag(zoo::zoo(testObs), 0:-1)
+testObs <- xts::xts(testObs[-1,])
 testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)

### 2017-02-03 R/faultFilter.R

@@ -114,6 +114,7 @@ faultFilter <- function(trainData,
   # This bit will find the observations which have not been flagged by either
   # statistic. However, we need to find and report the alarmed observations as
   # well. We first add a column for SPE and T2 alarm status.
+
   faultObj <- cbind(faultObj, rep(0, nrow(faultObj)))
   colnames(faultObj)[5] <- "Alarm"
   # nonFlaggedObs <- faultObj[faultObj[,2] == FALSE & faultObj[,4] == FALSE, ]
@@ -122,14 +123,16 @@ faultFilter <- function(trainData,
   # 3 (the default value of faultsToTriggerAlarm) flagged observations in a row
   alarmCheck <- rep(1, faultsToTriggerAlarm)
   # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
-  for(i in faultsToTriggerAlarm:nrow(faultObj)){
-    x1 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i, 4])
-    if(identical(x1, alarmCheck)){
-      faultObj[i,5] <- 1
-    }
-    x2 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i, 2])
-    if(identical(x2, alarmCheck)){
-      faultObj[i,5] <- faultObj[i,5] + 2
+  if(nrow(faultObj) >= faultsToTriggerAlarm){
+    for(i in faultsToTriggerAlarm:nrow(faultObj)){
+      x1 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i, 4])
+      if(identical(x1, alarmCheck)){
+        faultObj[i,5] <- 1
+      }
+      x2 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i, 2])
+      if(identical(x2, alarmCheck)){
+        faultObj[i,5] <- faultObj[i,5] + 2
+      }
     }
   }
   # We seperate out the non-alarmed observations, and we keep as many as we

### 2017-02-03 R/mspMonitor.R

@@ -60,13 +60,13 @@
 #' trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
 #'                             labelVector = normal_switch_xts[1:(n - 5), 1],
 #'                             trainObs = nTrainObs,
-#'                             lagsIncluded = c(0,1))
+#'                             lagsIncluded = c(0, -1))
 #'
 #' # While training, we included 1 lag (the default), so we will also lag the
 #' # observations we will test.
 #' testObs <- normal_switch_xts[(n - 6):n, -1]
-#' testObs <- stats::lag(testObs, 0:1)
-#' testObs <- testObs[-1, ]
+#' testObs <- stats::lag(zoo::zoo(testObs), 0:-1)
+#' testObs <- xts::xts(testObs[-1,])
 #' testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
 #'
 #' mspMonitor(observations = testObs[, -1],

### 2017-02-03 R/mspTrain.R

@@ -13,7 +13,7 @@
 #' @param Dynamic Specify if the PCA algorithm should include lagged variables.
 #'   Defaults to TRUE.
 #' @param lagsIncluded A vector of lags to include. If Dynamic = TRUE, specify
-#'   which lags to include. Defaults to c(0, 1), signifying that the Dynamic
+#'   which lags to include. Defaults to c(0, -1), signifying that the Dynamic
 #'   process observations will include current observations and observations
 #'   from one time step previous. See "Details" for more information.
 #' @param faultsToTriggerAlarm The number of sequential faults needed to trigger
@@ -72,17 +72,17 @@
 #'   alarm-positive observations are then removed from the data set and held in
 #'   a separate xts matrix for inspection.
 #'
-#'   Concering the lagsIncluded variable: the argument lagsIncluded = c(0,1)
+#'   Concering the lagsIncluded variable: the argument lagsIncluded = c(0,-1)
 #'   will column concatenate the current data with the same data from one
 #'   discrete time step back. This will necesarily remove the first row of the
 #'   data matrix, as we will have NA values under the lagged features. The
-#'   argument lagsIncluded = 0:2 will column concatenate the current
+#'   argument lagsIncluded = 0:-2 will column concatenate the current
 #'   observations with the observations from one step previous and the
 #'   observations from two steps previous, which will necessarily requirethe
 #'   removal of the first two rows of the data matrix. To include only certain
-#'   lags with the current data, specify lagsIncluded = c(0, lag_1, lag_2, ... ,
-#'   lag_K). This induce NA values in the first max(lag_k) rows, for k = 1, ...
-#'   , K, and these rows will be removed from consideration.
+#'   lags with the current data, specify lagsIncluded = c(0, -lag_1, -lag_2, ...
+#'   , -lag_K). This induce NA values in the first max(abs(-lag_k)) rows, for k
+#'   = 1, ... , K, and these rows will be removed from consideration.
 #'
 #'   Of note when considering performance: the example has 10080 rows on three
 #'   features alternating between three states, and trains on 20 percent of the
@@ -111,6 +111,7 @@
 #' @importFrom lazyeval lazy_dots
 #' @importFrom lazyeval lazy_eval
 #' @importFrom zoo zoo
+#' @importFrom xts xts
 #' @importFrom stats lag
 #'
[…]

### 2017-02-03 R/mspWarning.R

@@ -40,13 +40,13 @@
 #' trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
 #'                             labelVector = normal_switch_xts[1:(n - 5), 1],
 #'                             trainObs = nTrainObs,
-#'                             lagsIncluded = c(0,1))
+#'                             lagsIncluded = c(0, -1))
 #'
 #' # While training, we included 1 lag (the default), so we will also lag the
 #' # observations we will test.
 #' testObs <- normal_switch_xts[(n - 6):n, -1]
-#' testObs <- stats::lag(testObs, 0:1)
-#' testObs <- testObs[-1, ]
+#' testObs <- stats::lag(zoo::zoo(testObs), 0:-1)
+#' testObs <- xts::xts(testObs[-1,])
 #' testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
 #'
 #' # Run the monitoring function.

### 2017-02-03 R/processMonitor.R

@@ -73,6 +73,8 @@ processMonitor <- function(data,
 
   ls <- lazy_dots(...)
 
+  # browser()
+
   faultObj_ls <- do.call(faultFilter,
                 args = c(list(trainData = data[1:trainObs,],
                               testData = data[(trainObs + 1):nrow(data), ],
@@ -98,10 +100,11 @@ processMonitor <- function(data,
     # is what the date/ means for xts objects (date/ means that date and all
     # after it, this is why we remove the first row).
     testData <- data[paste0(testTime, "/")]
-    if(nrow(testData) == 1) break
+    testData <- testData[-1,]
+    if(nrow(testData) == 0) break
     faultObj_ls <- do.call(faultFilter,
                            args = c(list(trainData = trainData,
-                                         testData = testData[-1,],
+                                         testData = testData,
                                          updateFreq = updateFreq,
                                          faultsToTriggerAlarm = faultsToTriggerAlarm),
                                     lazy_eval(ls)))

### 2017-02-03 R/tenDay_xts.R

@@ -1,10 +1,10 @@
 #'  Real Process Data for Training
 #'
-#' @description Data from the SM-MBR Bioreactor system over nine days. This data
+#' @description Data from the SM-MBR Bioreactor system over ten days. This data
 #'   will be used for training the mvMonitoring package.
 #'
 #' @format An xts matrix of 1,155 rows and 35 features recorded over
 #'   2017-01-17 at 00:10 to 2017-01-26 at 00:00.
 #'
 #' @source Kathryn Newhart
-"nineDay_clean"
+"tenDay_clean"

### 2017-02-03 R/oneDay_xts.R
Corrected oneDay and tenDay data files, and updated the help PDF.

@@ -1,10 +1,10 @@
 #'  Real Process Data for Testing
 #'
-#' @description Data from the SM-MBR Bioreactor system over 24 hours. This data
+#' @description Data from the SM-MBR Bioreactor system over 12 hours. This data
 #'   will be used for testing the mvMonitoring package.
 #'
-#' @format An xts matrix of 144 rows and 35 features recorded over
-#'   2017-01-26 at 00:10 to 2017-01-27 at 00:00.
+#' @format An xts matrix of 75 rows and 35 features recorded over
+#'   2017-01-27 at 00:10 to 2017-01-27 at 12:30.
 #'
 #' @source Kathryn Newhart
 "oneDay_clean"

### 2017-02-03 R/tenDay_xts.R

@@ -3,8 +3,8 @@
 #' @description Data from the SM-MBR Bioreactor system over ten days. This data
 #'   will be used for training the mvMonitoring package.
 #'
-#' @format An xts matrix of 1,155 rows and 35 features recorded over
-#'   2017-01-17 at 00:10 to 2017-01-26 at 00:00.
+#' @format An xts matrix of 1,299 rows and 35 features recorded over
+#'   2017-01-17 at 00:10 to 2017-01-27 at 00:00.
 #'
 #' @source Kathryn Newhart
 "tenDay_clean"

### 2017-02-16 R/rotationMatrix.R
Updated the rotate3D() function to take in a list of angles. Corrected the AR structure in the t vector for data generation.

@@ -26,6 +26,13 @@
 #' normal_switch_xts[,-1] %*% rotate3D(yaw = -10, pitch = 0, roll = 15)
 rotate3D <- function(yaw, pitch, roll){
 
+  if(is.list(yaw)){
+    yaw_ls <- yaw
+    yaw <- yaw_ls[[1]]
+    pitch <- yaw_ls[[2]]
+    roll <- yaw_ls[[3]]
+  }
+
   thetaX <- roll * pi / 180
   thetaY <- pitch * pi / 180
   thetaZ <- yaw * pi / 180

### 2017-02-17 R/mspMonitor.R
Fixed lags issue. stats::lag() calls different internal functions based on the class of the object, so we hard coded all lag functions to be lag.xts, and we included a halt command if the data structure is not xts. We also updated the help files and the namespace (as we don't need the zoo() function, but do need is.xts()).

@@ -49,6 +49,7 @@
 #' the xts matrix necessary for the mspWarning() function.
 #'
 #' @export
+#' @importFrom xts lag.xts
 #'
 #' @examples
 #' data("normal_switch_xts")
@@ -65,8 +66,8 @@
 #' # While training, we included 1 lag (the default), so we will also lag the
 #' # observations we will test.
 #' testObs <- normal_switch_xts[(n - 6):n, -1]
-#' testObs <- stats::lag(zoo::zoo(testObs), 0:-1)
-#' testObs <- xts::xts(testObs[-1,])
+#' testObs <- xts:::lag.xts(testObs, 0:1)
+#' testObs <- testObs[-1,]
 #' testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
 #'
 #' mspMonitor(observations = testObs[, -1],

### 2017-02-17 R/mspTrain.R

@@ -20,35 +20,24 @@
 #'   an alarm. Defaults to 3
 #' @param ... Lazy dots for additional internal arguments
 #'
-#' @return A list with the following components:
-#'   \itemize{
-#'     \item{FaultChecks -- }{an xts flagging matrix with the same number of rows as
-#'       "data". This flag matrix has the following five columns:
-#'         \itemize{
-#'           \item{SPE -- }{the SPE statistic value for each observation in
-#'             "data"}
-#'           \item{SPE_Flag -- }{a vector of SPE indicators recording 0 if the
-#'             test statistic is less than or equal to the critical value
-#'             passed through from the threshold object}
-#'           \item{T2 -- }{the T2 statistic value for each observation in
-#'             "data"}
-#'           \item{T2_Flag -- }{a vector of T2 fault indicators, defined like
-#'             SPE_Flag}
-#'           \item{Alarm -- }{a column indicating if there have been three flags
-#'             in a row for either the SPE or T2 monitoring statistics or both.
-#'             Alarm states are as follows: 0 = no alarm, 1 = Hotelling's T2
-#'             alarm, 2 = Squared Prediction Error alarm, and 3 = both alarms.}
-#'         }
-#'       }
-#'     \item{Non_Alarmed_Obs -- }{an xts data matrix of all the non-alarmed
-#'       observations}
-#'     \item{Alarms -- }{an xts data matrix of the features and specific alarms
-#'       for Alarmed observations with the alarm codes are listed above}
-#'     \item{TrainingSpecs -- }{a list of k lists, one for each class, with each
-#'       list containing the specific threshold object returned by the internal
-#'       threshold() function for that class. See the threshold() function's
-#'       help file for more details.}
-#'   }
+#' @return A list with the following components: \itemize{ \item{FaultChecks --
+#'   }{an xts flagging matrix with the same number of rows as "data". This flag
+#'   matrix has the following five columns: \itemize{ \item{SPE -- }{the SPE
+#'   statistic value for each observation in "data"} \item{SPE_Flag -- }{a
+#'   vector of SPE indicators recording 0 if the test statistic is less than or
+#'   equal to the critical value passed through from the threshold object}
+#'   \item{T2 -- }{the T2 statistic value for each observation in "data"}
+#'   \item{T2_Flag -- }{a vector of T2 fault indicators, defined like SPE_Flag}
[…]

### 2017-02-17 R/mspWarning.R

@@ -29,6 +29,7 @@
 #' This function requires an xts matrix returned by the mspMonitor() function.
 #'
 #' @export
+#' @importFrom xts lag.xts
 #'
 #' @examples
 #' data("normal_switch_xts")
@@ -45,8 +46,8 @@
 #' # While training, we included 1 lag (the default), so we will also lag the
 #' # observations we will test.
 #' testObs <- normal_switch_xts[(n - 6):n, -1]
-#' testObs <- stats::lag(zoo::zoo(testObs), 0:-1)
-#' testObs <- xts::xts(testObs[-1,])
+#' testObs <- xts:::lag.xts(testObs, 0:1)
+#' testObs <- testObs[-1,]
 #' testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
 #'
 #' # Run the monitoring function.

### 2017-02-21 R/threshold.R
Apparently, the SPE function is VERY sensitive to the change in the var.amnt parameter (defaults to 95%). At 0.95, the threshold is around 1.2-1.4. The closer this parameter is to 1, the lower the SPE threshold (overfitting?). This causes the abnormally high false alarm rate for state 2. However, when I drop var.amnt even to 94%, the threshold increases drastically (to between 18 and 20); and if I increase var.amnt to 99%, the threshold drops to about 0.6-0.7. I need to speak with Dr. Hering about this.

@@ -58,8 +58,7 @@ threshold.pca <- function(pca_object, alpha = 0.001, ...){
   SPE.np.dens <- density(spe,
                          bw = "SJ", # Sheather Jones
                          kernel = "gaussian",
-                         from = 0
-                         )
+                         from = 0)
 
   # BMS::quantile.density
   SPE.lim.np <- quantile.density(SPE.np.dens, 1 - alpha)

### 2017-02-21 R/faultFilter.R
BUG FIXED: The training summary object returned by the mspTrain() function did not return the class mean vectors or precision matrices. Therefore, the mspMonitor() function could not properly centre and scale the incoming test obs.

@@ -100,6 +100,11 @@ faultFilter <- function(trainData,
   scaledTest <- xts(scaledTest, order.by = index(testData))
   colnames(scaledTest) <- colnames(testData)
 
+  # We also need the training information to contain the mean and precision, so
+  # that new observations can be centred and scaled based on the training info.
+  thresholdObj$muTrain <- muTrain
+  thresholdObj$RootPrecisTrain <- precisRootMat
+
   # We now apply the faultDetect function down each row of the scaled test data
   # set. We then return it to its form as an xts matrix.
   faultObj <- lapply(1:nrow(scaledTest), function(i){

### 2017-02-21 R/mspMonitor.R

@@ -96,8 +96,15 @@ mspMonitor <- function(observations,
   # Apply the fault detection function to each row, accounting for the chance
   # that rows come from different classes
   dataAndFaults <- lapply(1:nrow(classData), function(i){
-    faultObj <- faultDetect(threshold_object = trainingSummary[[classData[i,1]]],
-                            observation = classData[i, -1])
+    # Subset out the appropriate training information for that observation
+    train_ls <- trainingSummary[[classData[i,1]]]
+    # Centre and scale the observation
+    centredObs <- as.matrix(classData[i, -1] - train_ls$muTrain)
+    scaledObs <- centredObs %*% train_ls$RootPrecisTrain
+    # Now apply fault detection
+    faultObj <- faultDetect(threshold_object = train_ls,
+                            observation = scaledObs)
+    # Bind the flagging info to the original observation
     cbind(classData[i,], faultObj)
   })
   obsAndFlags <- do.call(rbind, dataAndFaults)

### 2017-02-21 R/mspTrain.R
Tested fault identification under Faults 1A-3B. Fault 3A seems to give us trouble, but we alarm the other faults quite quickly. Perhaps the drift in this fault is too slow?
Also, I added the class label column to the Non_Alarmed_Obs xts matrix returned by the msptTrain() function.

@@ -174,6 +174,8 @@ mspTrain <- function(data,
     monitorResults[[i]]$Non_Alarmed_Obs
   })
   Non_Alarmed_Obs <- do.call(rbind, Non_Alarmed_Obs)
+  Non_Alarmed_Obs <- cbind(classData[index(Non_Alarmed_Obs), 1],
+                           Non_Alarmed_Obs)
 
   # Alarmed observations and corresponding alarm codes data matrix
   Alarms <- lapply(classes, function(i){

### 2017-03-12 R/mspProcessData.R
Added "All" faults option, adpcaTest, msadpcaTest, and "altState" information to mspProcessData(). This alows us to generate one data matrix with the true states and false states for testing. When we have true single-state data, we test MSAD by randomly assigning a state in the "altState" column. For multi-state data, we test AD by assigning the same state to the "altState" column. So we don't get confused, the true state information is still in the "state" column.
Also, I fixed a documentation error in the mspWarning function. The alarm codes were backwards.

@@ -5,7 +5,7 @@
 #'   operating conditions or under fault conditions.
 #'
 #' @param faults A character vector of faults chosen. Options are "NOC", "A1",
-#'   "B1", "A2", "B2", "A3", or "B3". See details for more information.
+#'   "B1", "A2", "B2", "A3", "B3", or "All". See details for more information.
 #' @param faultStartIndex An integer specifying the index at which the faults
 #'   will start.
 #' @param startTime a POSIXct object specifying the day and time for the
@@ -22,24 +22,61 @@
 #'   pitch = 0, and roll = -30.
 #' @param scales3 Change the principal scales for State 3. Defaults to 0.25,
 #'   0.1, and 0.75.
+#' @param adpcaTest If "multiState" is TRUE, incorrectly label all the states
+#'   the same. This should only be used to test AD-PCA performance under a true
+#'   multi-state model. Defaults to FALSE.
+#' @param msadpcaTest If "multiState" is FALSE, incorrectly label all the states
+#'   at random. This should only be used to test MSAD-PCA performance under a
+#'   true single-state model. Defaults to FALSE.
 #' @param ... Lazy dots for internal arguments
 #'
 #' @return A list of data frames named with the names of the given faults with
-#'   the following information: \itemize{ \item{dateTime -- }{A POSIXct column
-#'   of times starting at the user-defined `startTime` argument, length given by
-#'   the `period` argument, and spacing given by the `increment` argument. For
-#'   example, if the starting value is "2016-01-10", period is 10080, and the
-#'   incrementation is in minutes, then this sequence will be one week's worth
-#'   of observations recorded every minute from midnight on the tenth of
-#'   January.} \item{state -- }{An integer column of all 1's (when the
-#'   `multiState` argument is FALSE), or a column of the state values (1, 2 or
-#'   3).} \item{x -- }{A double column of generated values for the first
-#'   feature.} \item{y -- }{A double column of generated values for the second
-#'   feature.} \item{z -- }{A double column of generated values for the third
-#'   feature.}}
+#'   the following information: \itemize{
+#'     \item{dateTime -- }{A POSIXct column of times starting at the user-
+#'       defined `startTime` argument, length given by the `period` argument,
+#'       and spacing given by the `increment` argument. For example, if the
+#'       starting value is "2016-01-10", period is 10080, and the incrementation
+#'       is in minutes, then this sequence will be one week's worth of
[…]

### 2017-03-12 R/mspWarning.R

@@ -9,7 +9,7 @@
 #'
 #' @return An xts matrix of the same dimensions as mspMonitor_object, with a
 #'   recorded negative or positive and type-specific alarm status. Alarm codes
-#'   are: 0 = no alarm, 1 = Hotelling's T2 alarm, 2 = Squared Prediction Error
+#'   are: 0 = no alarm, 1 = Squared Prediction Error alarm, 2 = Hotelling's T2
 #'   alarm, and 3 = both alarms.
 #'
 #' @details This function and the mspMonitor() function are designed to be ran

### 2017-03-12 R/faultSwitch.R
Fixed minor documenation issues in faultSwitch() and mspProcessData().

@@ -5,7 +5,8 @@
 #'
 #' @param df A data frame returned by the processNOCdata() function.
 #' @param fault A character string. Options are "NOC", "A1", "B1", "A2", "B2",
-#'   "A3", or "B3". See "details" of mspProcessData() for more information.
+#'   "A3", "B3", or "All". See "details" of mspProcessData() for more
+#'   information.
 #' @param faultStartIndex An integer specifying the index at which the faults
 #'   will start.
 #' @param period The observation cycle length. Defaults to one week's worth of

### 2017-03-12 R/mspProcessData.R

@@ -48,6 +48,8 @@
 #'     \item{y -- }{A double column of generated values for the second feature.}
 #'     \item{z -- }{A double column of generated values for the third feature.}
 #'     }
+#'   For details on how these features are defined, see the "details" of the
+#'   processNOCdata() function.
 #'
 #' @details For details on how the faults are induced, see the "details" of the
 #'   faultSwitch() function. This function also includes AD-PCA versus MSAD-PCA

### 2017-03-14 R/mspWarning.R
Added working MSAD simulation. We haven't yet finished the AD simulation.

@@ -9,7 +9,7 @@
 #'
 #' @return An xts matrix of the same dimensions as mspMonitor_object, with a
 #'   recorded negative or positive and type-specific alarm status. Alarm codes
-#'   are: 0 = no alarm, 1 = Squared Prediction Error alarm, 2 = Hotelling's T2
+#'   are: 0 = no alarm, 1 = Hotelling's T2 alarm, 2 = Squared Prediction Error
 #'   alarm, and 3 = both alarms.
 #'
 #' @details This function and the mspMonitor() function are designed to be ran

### 2017-03-15 inst/mspSummary.R
Vignette updated to include single-state sim. mspSummary() helper function file updated to include analysis of the single-state data. Move computation to the Mac for parallel support.

@@ -1,3 +1,8 @@
+# This file exists to generation the simulation tabulated results for detection
+# times and the histograms for false alarm rates
+
+######  Multi-State Simulation  ###############################################
+
 # Read in the latest simulation data
 library(readr)
 library(tidyverse)
@@ -82,3 +87,50 @@ FA_rates2$MSAD_SPE %>%
   hist(xlim = c(0, 0.06), main = "MSAD SPE False Alarm Rates")
 FA_rates2$AD_T2 %>%
   hist(xlim = c(0, 0.06), main = "AD T2 False Alarm Rates")
+
+######  Single-State Simulation  ##############################################
+###  Detection Times  ###
+# Read Detection Times Data
+
+# Fault 1A
+ss_detectionTimes %>%
+  filter(Faults == "A1") %>%
+  select(-Faults) %>%
+  sapply(mspSummary)
+
+# Fault 1B
+ss_detectionTimes %>%
+  filter(Faults == "B1") %>%
+  select(-Faults) %>%
+  sapply(mspSummary)
+
+# Fault 2A
+ss_detectionTimes %>%
+  filter(Faults == "A2") %>%
+  select(-Faults) %>%
+  sapply(mspSummary)
+
+# Fault 1B
+ss_detectionTimes %>%
+  filter(Faults == "B2") %>%
+  select(-Faults) %>%
+  sapply(mspSummary)
+
+# Fault 3A
+ss_detectionTimes %>%
+  filter(Faults == "A3") %>%
+  select(-Faults) %>%
+  sapply(mspSummary)
+
+# Fault 3B
+ss_detectionTimes %>%
+  filter(Faults == "B3") %>%
+  select(-Faults) %>%
+  sapply(mspSummary)
+
+###  False Alarm Rates  ###
+# Read in False Alarm Rates Data
+ss_FA_rates[,1] %>% hist(xlim = c(0, 0.02), main = "MSAD SPE False Alarm Rates")
+ss_FA_rates[,3] %>% hist(xlim = c(0, 0.02), main = "AD SPE False Alarm Rates")
+ss_FA_rates[,2] %>% hist(xlim = c(0.05, 0.2), main = "MSAD T2 False Alarm Rates")
+ss_FA_rates[,4] %>% hist(xlim = c(0.05, 0.2), main = "AD T2 False Alarm Rates")

### 2017-03-16 inst/mspSummary.R
Full round 1 simulation complete.

@@ -110,7 +110,7 @@ ss_detectionTimes %>%
   select(-Faults) %>%
   sapply(mspSummary)
 
-# Fault 1B
+# Fault 2B
 ss_detectionTimes %>%
   filter(Faults == "B2") %>%
   select(-Faults) %>%
@@ -120,7 +120,7 @@ ss_detectionTimes %>%
 ss_detectionTimes %>%
   filter(Faults == "A3") %>%
   select(-Faults) %>%
-  sapply(mspSummary)
+  sapply(mspSummary) %>% round(3)
 
 # Fault 3B
 ss_detectionTimes %>%
@@ -130,7 +130,7 @@ ss_detectionTimes %>%
 
 ###  False Alarm Rates  ###
 # Read in False Alarm Rates Data
-ss_FA_rates[,1] %>% hist(xlim = c(0, 0.02), main = "MSAD SPE False Alarm Rates")
-ss_FA_rates[,3] %>% hist(xlim = c(0, 0.02), main = "AD SPE False Alarm Rates")
+ss_FA_rates[,1] %>% hist(xlim = c(0, 0.03), main = "MSAD SPE False Alarm Rates")
+ss_FA_rates[,3] %>% hist(xlim = c(0, 0.03), main = "AD SPE False Alarm Rates")
 ss_FA_rates[,2] %>% hist(xlim = c(0.05, 0.2), main = "MSAD T2 False Alarm Rates")
 ss_FA_rates[,4] %>% hist(xlim = c(0.05, 0.2), main = "AD T2 False Alarm Rates")

### 2017-03-19 R/faultFilter.R
Alarm labels were backwards for the vignette and mspWarning() functions. We can't save the simulated data because some of the time to detection lines were correct, but the corresponding false alarm rates were not, or vice versa. I also added two label comments to faultFilter().
Also, I reflowed the function description in mspTrain(). It had been word wrapped even though it's a bulleted list.

@@ -130,10 +130,12 @@ faultFilter <- function(trainData,
   # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
   if(nrow(faultObj) >= faultsToTriggerAlarm){
     for(i in faultsToTriggerAlarm:nrow(faultObj)){
+      # T2
       x1 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i, 4])
       if(identical(x1, alarmCheck)){
         faultObj[i,5] <- 1
       }
+      # SPE
       x2 <- as.vector(faultObj[(i - faultsToTriggerAlarm + 1):i, 2])
       if(identical(x2, alarmCheck)){
         faultObj[i,5] <- faultObj[i,5] + 2

### 2017-03-19 R/mspTrain.R

@@ -20,24 +20,31 @@
 #'   an alarm. Defaults to 3
 #' @param ... Lazy dots for additional internal arguments
 #'
-#' @return A list with the following components: \itemize{ \item{FaultChecks --
-#'   }{an xts flagging matrix with the same number of rows as "data". This flag
-#'   matrix has the following five columns: \itemize{ \item{SPE -- }{the SPE
-#'   statistic value for each observation in "data"} \item{SPE_Flag -- }{a
-#'   vector of SPE indicators recording 0 if the test statistic is less than or
-#'   equal to the critical value passed through from the threshold object}
-#'   \item{T2 -- }{the T2 statistic value for each observation in "data"}
-#'   \item{T2_Flag -- }{a vector of T2 fault indicators, defined like SPE_Flag}
-#'   \item{Alarm -- }{a column indicating if there have been three flags in a
-#'   row for either the SPE or T2 monitoring statistics or both. Alarm states
-#'   are as follows: 0 = no alarm, 1 = Hotelling's T2 alarm, 2 = Squared
-#'   Prediction Error alarm, and 3 = both alarms.} } } \item{Non_Alarmed_Obs --
-#'   }{an xts data matrix of all the non-alarmed observations} \item{Alarms --
-#'   }{an xts data matrix of the features and specific alarms for Alarmed
-#'   observations with the alarm codes are listed above} \item{TrainingSpecs --
-#'   }{a list of k lists, one for each class, with each list containing the
-#'   specific threshold object returned by the internal threshold() function for
-#'   that class. See the threshold() function's help file for more details.} }
+#' @return A list with the following components: \itemize{
+#'   \item{FaultChecks -- }{an xts flagging matrix with the same number of rows
+#'     as "data". This flag matrix has the following five columns: \itemize{
+#'       \item{SPE -- }{the SPE statistic value for each observation in "data"}
+#'       \item{SPE_Flag -- }{a vector of SPE indicators recording 0 if the test
+#'         statistic is less than or equal to the critical value passed through
+#'         from the threshold object}
+#'       \item{T2 -- }{the T2 statistic value for each observation in "data"}
+#'       \item{T2_Flag -- }{a vector of T2 fault indicators, defined like
+#'         SPE_Flag}
+#'       \item{Alarm -- }{a column indicating if there have been three flags in
+#'         a row for either the SPE or T2 monitoring statistics or both. Alarm
+#'         states are as follows: 0 = no alarm, 1 = Hotelling's T2 alarm,
[…]

### 2017-03-19 R/mspWarning.R

@@ -78,15 +78,15 @@ mspWarning <- function(mspMonitor_object,
       # that specific observation have not been checked.
       data_xts[n, "Alarm"] <- 0
 
-      # We now check the last few SPE flags
-      x1 <- as.vector(data_xts[(n - faultsToTriggerAlarm + 1):n, "SPE_Flag"])
+      # We now check the last few T2 flags
+      x1 <- as.vector(data_xts[(n - faultsToTriggerAlarm + 1):n, "T2_Flag"])
       if(identical(x1, alarmCheck)){
         data_xts[n, "Alarm"] <- 1
       }
 
-      # And we also check the last few T2 flags. We will increment the Alarm
+      # And we also check the last few SPE flags. We will increment the Alarm
       #state based on SPE flag status, T2 flag status, or both
-      x2 <- as.vector(data_xts[(n - faultsToTriggerAlarm + 1):n, "T2_Flag"])
+      x2 <- as.vector(data_xts[(n - faultsToTriggerAlarm + 1):n, "SPE_Flag"])
       if(identical(x2, alarmCheck)){
         data_xts[n, "Alarm"] <- data_xts[n, "Alarm"] + 2
       }

### 2017-03-21 inst/mspSummary.R
Added cluster apply code for Windows implementation.

@@ -45,37 +45,37 @@ mspSummary <- function(vec,
 
 
 # Fault 1A
-detection_times2 %>%
+ms_detectionTimes3 %>%
   filter(Faults == "A1") %>%
   select(-Faults) %>%
   sapply(mspSummary)
 
 # Fault 1B
-detection_times2 %>%
+ms_detectionTimes3 %>%
   filter(Faults == "B1") %>%
   select(-Faults) %>%
   sapply(mspSummary)
 
 # Fault 2A
-detection_times2 %>%
+ms_detectionTimes3 %>%
   filter(Faults == "A2") %>%
   select(-Faults) %>%
   sapply(mspSummary)
 
-# Fault 1B
-detection_times2 %>%
+# Fault 2B
+ms_detectionTimes3 %>%
   filter(Faults == "B2") %>%
   select(-Faults) %>%
   sapply(mspSummary)
 
 # Fault 3A
-detection_times2 %>%
+ms_detectionTimes3 %>%
   filter(Faults == "A3") %>%
   select(-Faults) %>%
   sapply(mspSummary)
 
 # Fault 3B
-detection_times2 %>%
+ms_detectionTimes3 %>%
   filter(Faults == "B3") %>%
   select(-Faults) %>%
   sapply(mspSummary)
@@ -83,9 +83,9 @@ detection_times2 %>%
 
 ###  False Alarm Rates  ###
 FA_rates2 <- read_csv("~/Box Sync/Consulting/Dr. Hering/MV_Process_Control/MVSPC/Simulation_Data/false_alarm_rates_1000_20170314.csv")
-FA_rates2$MSAD_SPE %>%
+ms_FA_rates3$MSAD_SPE %>%
   hist(xlim = c(0, 0.06), main = "MSAD SPE False Alarm Rates")
-FA_rates2$AD_T2 %>%
+ms_FA_rates3$AD_T2 %>%
   hist(xlim = c(0, 0.06), main = "AD T2 False Alarm Rates")
 
 ######  Single-State Simulation  ##############################################

### 2017-03-22 R/faultSwitch.R
Fixed bug in simulation where the inner lapply() rolls over the non-NOC elements, not the "all but the first element" elements. Also updated Fault 3A so that the drify multiplier ranges from 1 to 6 instead of 1 to 3.

@@ -71,8 +71,8 @@
 #'       \item{y : }{y(t_*) = (t_*) ^ 2 - 3t_* + error}
 #'       \item{z : }{z(t_*) = -(t_*) ^ 3 + 3(t_*) ^ 2 + error}
 #'     }
-#'     where t_* = 3 x t x (period - s) / (2 x period) and s is the observation
-#'     index.
+#'     where t_* = 5 x t x (period - s) / (period - faultStartIndex) and s is
+#'     the observation index.
 #'   }
 #'   \item{B3 -- }{The fault is a signal amplificaton in the determining latent
 #'     t vector for the "z" feature only. The fault starts at "faultStartIndex",
@@ -139,7 +139,7 @@ faultSwitch <- function(df, fault,
 
   # Fault 3A
   fault3A <- function(df, faultStartIndex, period){
-    amplify_vec <- 2 * (1:period - faultStartIndex) /
+    amplify_vec <- 5 * (1:period - faultStartIndex) /
       (period - faultStartIndex) + 1
     amplify_vec[amplify_vec < 1] <- 1
     df %>%

### 2017-03-27 README.Rmd
Update README.Rmd
Added a random draw from mspProcessData(), and updated the god-awful lag bit.

@@
 ## Overview
-We create this package, `mvMonitor`, from the foundation laid by Kazor et al (2016).
+We create this package, `mvMonitoring`, from the foundation laid by Kazor et al (2016).
 The `mvMonitor` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.
@@
 ## Examples
-These are the examples shown in the help files for hte mspTrain(), mspMonitor(), and mspWarning() functions.
+These are the examples shown in the help files for the mspTrain(), mspMonitor(), and mspWarning() functions.
 ```{r mspExamples}
-data("normal_switch_xts")
+normal_switch_xts <- mspProcessData(faults = "NOC", faultStartIndex = 8500)
 # The state values are recorded in the first column.
@@
 testObs <- normal_switch_xts[(n - 6):n, -1]
-testObs <- stats::lag(zoo::zoo(testObs), 0:-1)
-testObs <- xts::xts(testObs[-1,])
+testObs <- xts:::lag.xts(testObs, 0:1)
+testObs <- testObs[-1,]
 testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)

### 2017-03-28 inst/mspGraphsGrid.R
Removed background from the legend.

@@ -53,7 +53,8 @@ mspGraphsGrid <- function(data_xts){
     theme(panel.grid = element_blank(),
           axis.title.y = element_blank(),
           plot.title = element_text(hjust = 0.5),
-          legend.position = c(0.12, 0.85)) + # legend.justification = c(1,0),
+          legend.position = c(0.12, 0.85),
+          legend.background = element_blank()) + # legend.justification = c(1,0),
     guides(color = guide_legend(override.aes = list(size = 2))) +
     ggtitle("Feature X") +
     geom_vline(xintercept = as.numeric(faultStart), size = 1)

### 2017-03-28 R/faultSwitch.R
Finished Fault XC documentation. Hopefully, this makes Travis happy.

@@ -4,8 +4,8 @@
 #'   the infected data frame.
 #'
 #' @param df A data frame returned by the processNOCdata() function.
-#' @param fault A character string. Options are "NOC", "A1", "B1", "A2", "B2",
-#'   "A3", "B3", or "All". See "details" of mspProcessData() for more
+#' @param fault A character string. Options are "NOC", "A1", "B1", "C1", "A2",
+#'   "B2", "C2", "A3", "B3", or "C3". See "details" of mspProcessData() for more
 #'   information.
 #' @param faultStartIndex An integer specifying the index at which the faults
 #'   will start.
@@ -14,6 +14,8 @@
 #' @param shift The fault parameter for faults "A1" and "B1" corresponding to
 #'   the positive shock value added to features. Defaults to 2. See "details" of
 #'   mspProcessData() for more information.
+#' @param postStateSplit Should we induce faults before or after state-splitting?
+#'   Defaults to FALSE. Make this argument TRUE for faults 1C, 2C, 3C.
 #'
 #' @return A data frame with the same structure as df, but with faults induced
 #'   across all observations. The mspProcessData() function then subsets the
@@ -46,6 +48,14 @@
 #'       \item{z : }{z(t) = -t ^ 3 + 3t ^ 2 + error}
 #'     }
 #'   }
+#'   \item{C1 -- }{A matrix as defined in A1, but with x, y, and z feature
+#'     columns defined as follows: \itemize{
+#'       \item{x : }{x(t) = t + shift / 4 + error}
+#'       \item{y : }{y(t) = t ^ 2 - 3t + error}
+#'       \item{z : }{z(t) = -t ^ 3 + 3t ^ 2 + shift / 4 + error}
+#'     }
+#'     This shift is applied only in State 3.
+#'   }
 #'   \item{A2 -- }{The fault is a drift on each feature by
 #'     (s - faultStartIndex / 10 ^ 3, where s is the observation index. The
 #'     fault starts at "faultStartIndex", and the x, y, and z feature columns
@@ -63,6 +73,14 @@
 #'       \item{y : }{y(t) = t ^ 2 - 3t + drift + error}
 #'       \item{z : }{z(t) = -t ^ 3 + 3t ^ 2 + drift + error}
 #'     }
+#'   }
+#'   \item{C2 -- }{The fault is a negative drift on the "y" feature by 1.5 *
[…]

### 2017-03-28 R/mspProcessData.R

@@ -5,7 +5,8 @@
 #'   operating conditions or under fault conditions.
 #'
 #' @param faults A character vector of faults chosen. Options are "NOC", "A1",
-#'   "B1", "A2", "B2", "A3", "B3", or "All". See details for more information.
+#'   "B1", "C1", "A2", "B2", "C2", "A3", "B3", "C3", or "All". See details for
+#'   more information.
 #' @param faultStartIndex An integer specifying the index at which the faults
 #'   will start.
 #' @param period The observation cycle length. Defaults to one week's worth of

### 2017-04-26 R/faultFilter.R
Mostly done with the new and improved vignette for Melissa J. Still have to show the code example for mspMonitor() and mspWarning(). Also created the mvMonitoring documentation file (as per p.51 of Hadley's packages book "documenting packages").
Also, added some documentation in faultFilter(). We added the SPE and T2 math equations.

@@ -14,27 +14,42 @@
 #'
 #' @return A list of class "fault_ls" with the following:
 #'   \itemize{
-#'     \item{faultObj -- }{an xts flagging matrix with the same number of rows as
+#'     \item{faultObj -- }{An xts flagging matrix with the same number of rows as
 #'       "testData". This flag matrix has the following five columns:
 #'         \itemize{
-#'           \item{SPE -- }{the SPE statistic value for each observation in
-#'             "testData"}
-#'           \item{SPE_Flag -- }{a vector of SPE indicators recording 0 if the
+#'           \item{SPE -- }{The SPE statistic value for each observation in
+#'             "testData". This statistic is defined as
+#'             \deqn{
+#'               SPE_i = (\textbf{X}_i - \textbf{Y}_i * \textbf{P}^T) *
+#'                (\textbf{X}_i - \textbf{Y}_i * \textbf{P}^T)^T,
+#'             }
+#'             where \eqn{\textbf{X}_i} is the \eqn{i^{th}} observation vector,
+#'             \eqn{\textbf{Y}_i} is the reduced-feature projection of the
+#'             observation \eqn{\textbf{X}_i}, and \eqn{\textbf{P}} is the
+#'             projection matrix such that \eqn{\textbf{X}_i\textbf{P} =
+#'             \textbf{Y}_i}.}
+#'           \item{SPE_Flag -- }{A vector of SPE indicators recording 0 if the
 #'             test statistic is less than or equal to the critical value
-#'             passed through from the threshold object}
-#'           \item{T2 -- }{the T2 statistic value for each observation in
-#'             "testData"}
-#'           \item{T2_Flag -- }{a vector of T2 fault indicators, defined like
-#'             SPE_Flag}
-#'           \item{Alarm -- }{a column indicating if there have been three flags
+#'             passed through from the threshold object.}
+#'           \item{T2 -- }{The T2 statistic value for each observation in
+#'             "testData". This statistic is defined as
+#'             \deqn{
+#'                T^2_i = \textbf{Y}_i * \textbf{D}^{-1} * \textbf{Y}_i^T,
+#'             }
+#'             where \eqn{\textbf{Y}_i = \textbf{X}_i\textbf{P}} is the reduced-
+#'             feature projection of the observation \eqn{\textbf{X}_i}, and
+#'             \eqn{\textbf{D}} is the diagonal matrix of eigenvalues.}
+#'           \item{T2_Flag -- }{A vector of T2 fault indicators, defined like
[…]

### 2017-04-26 vignettes/MVSPC-Workflow.R

@@ -1,0 +1,28 @@
+## ---- message = FALSE, warning = FALSE-----------------------------------
+library(tidyverse)
+library(mvMonitoring)
+fault2A_xts <- mspProcessData(faults = "A2",
+                              period = 7 * 24 * 60,
+                              faultStartIndex = 8500,
+                              startTime = "2015-05-16 10:00:00 CST")
+
+str(fault2A_xts)
+
+## ------------------------------------------------------------------------
+train2A_xts <- fault2A_xts[1:10020,]
+# This function will run in 13 seconds on the author's machine.
+train2A_ls <- mspTrain(data = train2A_xts[,-1],
+                       labelVector = train2A_xts[,1],
+                       trainObs = 3 * 24 * 60,
+                       updateFreq = 1 * 24 * 60,
+                       Dynamic = TRUE,
+                       lagsIncluded = 0:1,
+                       faultsToTriggerAlarm = 5)
+
+## ---- fig.show='hold'----------------------------------------------------
+plot(1:10)
+plot(10:1)
+
+## ---- echo=FALSE, results='asis'-----------------------------------------
+knitr::kable(head(mtcars, 10))
+

### 2017-07-04 README.Rmd

@@
 ## Examples
-These are the examples shown in the help files for the mspTrain(), mspMonitor(), and mspWarning() functions.
+These are the examples shown in the help files for the mspProcessData(), mspTrain(), mspMonitor(), and mspWarning() functions.
 ```{r mspExamples}
-normal_switch_xts <- mspProcessData(faults = "NOC", faultStartIndex = 8500)
+# Generate one week's worth of normal operating (NOC) data recorded at the one-
+# minute level
+noc_xts <- mspProcessData(faults = "NOC")
 # The state values are recorded in the first column.
-n <- nrow(normal_switch_xts)
-nTrainObs <- floor(0.4 * n)
+n <- nrow(noc_xts)
 
 # Calculate the training summary, but save five observations for monitoring.
-trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
-                            labelVector = normal_switch_xts[1:(n - 5), 1],
-                            trainObs = nTrainObs,
-                            lagsIncluded = c(0, -1))
-
-trainResults_ls
+# This function will treat the first 3 days as in control (IC), and then update
+# the training window each day.
+trainResults_ls <- mspTrain(data = noc_xts[1:(n - 5), -1],
+                            labelVector = noc_xts[1:(n - 5), 1],
+                            trainObs = 4320)
 
@@
 # observations we will test.
-testObs <- normal_switch_xts[(n - 6):n, -1]
+testObs <- noc_xts[(n - 6):n, -1]
 testObs <- xts:::lag.xts(testObs, 0:1)
 testObs <- testObs[-1,]
-testObs <- cbind(normal_switch_xts[(n - 5):n, 1], testObs)
-testObs
+testObs <- cbind(noc_xts[(n - 5):n, 1], testObs)
 
@@
 
-dataAndFlags
-
 # Alarm check the last row of the matrix returned by the mspMonitor function

### 2017-07-04 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Created a LaTeX vignette folder. In the LaTeX vignette, I am building the package 'mvMonitoring' with devtools::build(), so if the LaTeX vignette is in the proper vignettes folder, it will recursively attempt to build itself. This is bad.

\documentclass{report}
\usepackage{amsmath, amssymb}
\usepackage{hyperref}
\usepackage{enumerate}

\begin{document}

\chapter{Multivariate Statistical Process Control with \texttt{mvMonitoring}}

This document serves to introduce engineers to the workflow necessary to follow in order to analyze multivariate process monitoring data via the \texttt{mvMonitoring} package.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  Introduction  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction} \label{sec:intro}

This is the accompanying package to the research published by \cite{kazor_comparison_2016} and the previous chapter. The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component. This package can be downloaded from GitHub by running the following:
%   <<r packLoad_GitHub, eval = FALSE>>=
%   devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
% @
\noindent where you create the value of ``tokenHere'' by generating a personal access token (PAT) at \url{https://github.com/settings/tokens} and copying the quoted string to this argument.

\subsection{Why use \texttt{mvMonitoring}?}
The \texttt{mvMonitoring} package can be used to detect outliers in a correlated multivariate process with non-linear, non-stationary, or autocorrelated feature behavior. These process outliers are often indicative of system fault. The common  and naive approach to multivariate process monitoring is to use expert opinion to identify a few important features to monitor visually, and raise an alarm if these features travel outside pre-defined normal operating boundaries.

However, this split univariate approach fails to account for the correlated nature of the process features, so some engineers have taken to monitoring the system as a single correlated multivariate process rather than a collection of independent univariate processes. In the literature review of the motivating papers, the authors cite how this approach has benefited the science of process monitoring as a whole. Unfortunately, this approach has its own shortcomings -- namely, monitoring a multivariate process in its original feature space can lead to exorbitant computational costs. To this end, \emph{principal components analysis} (PCA) and its many modifications have been employed to reduce the computation necessary to monitor a multivariate process as a whole. This package is an implementation of one such PCA modification.

\subsection{Multi- or Single-State AD-PCA}
AD-PCA is \emph{adaptive-dynamic} PCA, which accounts for non-linearity, non-stationarity, and autocorrelation in the multivariate process, and this modification is thoroughly discussed in \cite{kazor_comparison_2016} as well as in the previous chapter. As an additional component to this model, we now consider that the process to monitor may have multiple known system states. Thus, \emph{multi-state} monitoring is a modification to PCA which accounts for multiple process states and models them separately. States can be any mutually exclusive blocking factor, and states do not necessarily follow a strict order. Then, Multi-State AD-PCA (MSAD-PCA) allows process engineers to account for a few very different process states. Specifically, this modification should be used when features under different process states have different means, correlations, variances, or some combination of these three.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  mspProcessData  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Simulating Data with \texttt{mspProcessData}}
This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations. We follow the seminal work of \cite{dong_batch_1996} for generation of the foundational stationary and independent features.

\subsection{Latent Feature Creation}
So that the simulated features have non-zero correlations, Dong and McAvoy created their three features all as polynomial functions of a single latent variable $t(s)$, where $s = 1, \ldots, \omega$ is the observational index of the process.

\subsubsection{Autocorrelated and Non-Stationary Error}
The \texttt{mspProcesData} function induces autocorrelation in $t$ through its errors, $\varepsilon_s$, where
\[
  \varepsilon_1 \sim \mathcal{N}\left(\frac{1}{2}(a + b)(1 - \phi), \frac{b - a}{12} (1 - \phi ^ 2)\right),
\]
where $a = 0.01$ and $b = 2$. Now, we define the first-order autoregressive process on $\varepsilon_s$ by
\[
  \varepsilon_s = \varphi\varepsilon_{s - 1} + (1 - \varphi)\varepsilon,
\]
where $\varepsilon$ is as defined in the previous expression and the autocorrelation component $\phi = 0.75$. The mean and variance multipliers are the mean and variance of a random variable from the $\mathcal{U}_{[a,b]}$ distribution.

\subsubsection{The Non-Linear Latent Process}
This $t$ vector will be sinusoidal with period $\omega = 7 * 24 * 60$ (signifying a weekly period in  minute-level observations). We then synthesize a $t$ with
\[
  t^*_s = -\cos\left( \frac{2\pi}{\omega} s \right) + \epsilon_s,
\]
and scale $t^*$ to
\[
  t = \frac{(b - a)(t^*_s - \text{min}(t^*_s))}{\text{max}(t^*_s) - \text{min}(t^*_s)} + a.
\]
Finally then, the $t$ vector will lie entirely in $[a,b]$.

\subsection{Single-State and Multi-State Features}

\subsubsection{Single State Features}
First \texttt{mspProcessData} simulates three features, with each feature operating under $k$ different states. Let $\langle x_k(t), y_k(t), z_k(t) \rangle$ be the notation for State $k$. These are the three features under State 1 (normal operating conditions, or \emph{NOC}) as three functions of $t$:
\begin{align}
\textbf{x}(\textbf{t}) &\equiv \textbf{t} + \boldsymbol\varepsilon_1, \\
\textbf{y}(\textbf{t}) &\equiv \textbf{t} ^ 2 - 3 * \textbf{t} + \boldsymbol\varepsilon_2, \\
\textbf{z}(\textbf{t}) &\equiv -\textbf{t} ^ 3 + 3 * \textbf{t} ^ 2 + \boldsymbol\varepsilon_3,
\end{align}
where $\varepsilon_i \sim N(0, 0.01)$. The \texttt{mspProcessData} function calls the internal \texttt{processNOCdata} function to generate single-state observations under NOC.

\subsubsection{Multi-State Features}
The multi-state feature expression is induced by rotation and scaling of certain sets of observations. To induce a three-state, hourly switching process (the default), the \texttt{mspProcessData} function will create a label column that switches from ``1'' to ``2'' to ``3'' every hour. State ``1'' will be the features generated under the single-state assumption, while State ``2'' and State ``3'' are generated as follows. These states will be scaled rotations of the current $\langle x,y,z \rangle$ set. The second state is yaw, pitch, and roll rotated by (0, 90, 30) degrees, and the scales are multiplied by (1, 0.5, 2). The third state is yaw, pitch, and roll rotated by (90, 0, -30) degrees, and the scales are multiplied by (0.25, 0.1, 0.75).
\begin{enumerate}
\item $\mathcal{S}_1$: $\textbf{X}(t_s) := \langle x(t_s), y(t_s), z(t_s)\rangle$.

\item $\mathcal{S}_2$: $\textbf{X}(t_s) := \langle x(t_s), y(t_s), z(t_s)\rangle \cdot \textbf{P}_1\boldsymbol\Lambda_1$, where
\[
  \textbf{P}_1 = \begin{bmatrix}
  0    &  0.50 & -0.87 \\
  0    &  0.87 &  0.50 \\
  1    &  0    &  0
  \end{bmatrix}
\]
is the orthogonal rotation matrix for a yaw, pitch and roll degree change of $\langle 0^{\circ}, 90^{\circ}, 30^{\circ} \rangle$, and $\boldsymbol\Lambda_1 = \text{diag}(1, 0.5, 2)$ is a diagonal scaling matrix.

\item $\mathcal{S}_3$: $\textbf{X}(t_s) := \langle x(t_s), y(t_s), z(t_s)\rangle \cdot \textbf{P}_2\boldsymbol\Lambda_2$, where
\[
  \textbf{P}_2 = \begin{bmatrix}
  0    &  0.87 & -0.50 \\
  -1    &  0    &  0    \\
  0    &  0.50 &  0.87
  \end{bmatrix}
\]
is the orthogonal rotation matrix for a yaw, pitch and roll degree change of $\langle 90^{\circ}, 0^{\circ}, -30^{\circ} \rangle$, and $\boldsymbol\Lambda_2 = \text{diag}(0.25, 0.1, 0.75)$ is a diagonal scaling matrix.
\end{enumerate}

These rotation matrices $\textbf{P}_1$ and $\textbf{P}_2$ turn the states in three-dimensional space so that the states are at right angles to each other in at least one dimension, and the scaling matrices $\boldsymbol\Lambda_1$ and $\boldsymbol\Lambda_2$ inflate or deflate the process variances along each principal component. The \texttt{mspProcessData} function calls the internal function \texttt{dataStateSwitch} which splits the observations by state and applies the state-specific rotation and scaling through the internal \texttt{rotateScale3D} function.

\subsection{Synthetic Fault Induction}
Faults can be introduced to single- or multi-state data via the \texttt{mspProcessData} function. The default fault start index is 8500, or roughly 84\% through the 10,080 observation cycle. These faults are added through the internal \texttt{faultSwitch} function.
\begin{enumerate}
\item Fault 1A is a positive shift to all three features before state rotation: $\textbf{X}^*(t_s) = \textbf{X}(t_s) + 2,\ s \ge 8500$.
%
\item Fault 1B is a positive shift to the $x$ feature before state rotation: $x^*(t_s) = x(t_s) + 2,\ s \ge 8500$.
%
\item Fault 1C is a positive shift to the $x$ and $z$ features in State 3 only and *after* state rotation: $x^*(t_s) = x(t_s) + 2,\ z^*(t_s) = z(t_s) + 2,\ s \ge 8500$.
%
\item Fault 2A is a positive drift across all the process monitoring features before state rotation: $\textbf{X}^*(t_s) = \textbf{X}(t_s) + (s - 8500)\times 10^{-3}$, $s > 8500$.
%
\item Fault 2B is a positive drift across the $y$ and $z$ process monitoring features before state rotation: $y^*(t_s) = y(t_s) + (s - 8500)\times 10^{-3},\ z^*(t_s) = z(t_s) + (s - 8500)\times 10^{-3}$, $s > 8500$.
%
\item Fault 2C is a negative drift in the $y$ process monitoring feature in State 2 only and \emph{after} state rotation: $y^*(t_s) = y(t_s) - 1.5 \times \frac{s - 8500}{10080 - 8500}$, for $s > 8500$.
%
\item Fault 3A is an amplification of the underlying latent variable $t$ for all features. The maximum latent drift of this fault will be 5 + 1: $\textbf{X}^*(t_s) = \textbf{X}(t_s^*),\ s > 8500$, where $t_s^* = \left[\frac{5(s - 8500)}{\omega - 8500} + 1\right]t_s$.
%
\item Fault 3B is a mutation of the underlying latent variable $t$ for the $z$ feature: $z^*(t_s) = z(\log t_s^*)$, $s \ge 8500$. This fault will dampen the underlying latent effect for $z$ if $t_s > 1$ and amplify this effect if $t_s < 1$.
%
\item Fault 3C is a polynomial mutation of the error for the $y$ feature in State 2 only and \emph{after} state rotation: $y^*(t_s) = y(t_s) + 2 * \textbf{e}_3(s) - 0.25$, for $s > 8500$.
\end{enumerate}

\subsection{Putting it all together\ldots}
The \texttt{mspProcessData} function can generate weeks' worth of non-linear, non-stationary, autocorrelated, multi-state, multivariate process data useful to test new process monitoring techniques. Users can generate observations under NOC to measure false alarm rates, or induce one of nine pre-built faults to test detection time and consistency with repeated Monte Carlo sampling. We expect this function will generate interesting data useful enough to compare new and improved process monitoring techniques with existing methods.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  mspTrain  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Training with \texttt{mspTrain}}

The \texttt{mspTrain} function will generate projection matrices and test statistic thresholds from test data matrices.

\subsection{The \texttt{xts} Data Matrix}
An \texttt{xts} data matrix is first and foremost a matrix, \emph{not} a data frame. For users very familiar with data frame manipulation (with \texttt{dplyr} for instance), the slight but profound differences between manipulating matrices and data frames become quickly apparent. Because of the class requirements for matrices, \emph{all} features must be integer or double objects. The \texttt{mspTrain} function cannot train on character information.

The \texttt{xts} object class stands for \emph{extendible time series} and comes from the package \texttt{xts}, which is itself built on the package \texttt{zoo}. The date and time information (necessarily as \texttt{POSIX} objects) are stored as the row indices of \texttt{xts} matrices. We recommend the package \texttt{lubridate} for manipulating \texttt{POSIX} objects.

\subsection{The Class Vector}
When implementing single-state AD-PCA, this class vector simply needs to be a numeric column of the same value -- for instance, 1. However, for MSAD-PCA, the class vector should be an integer vector of class membership. The \texttt{mspTrain} function will split the observations by the class label, apply single-state AD-PCA to each class, then return the class-specific projection matrices and thresholds. Because of this split-apply-combine strategy, users must ensure that one or more classes are not too ``rare'' -- that is, the class-specific sample size should be sufficiently large to allow for stable covariance matrix inversion. For $p$ features (including lags), covariance inversion requires a class sample size greater than $p ^ 2 / 2$. Because of this, pay close attention to model parsimony -- do not block the observations on a factor unless the factor significantly affects the observations' mean vector or covariance matrix.

\subsection{Adaptive and Dynamic Modeling}
Because of the non-linear, non-stationary, and autocorrelated nature of some process monitoring applications, the \texttt{mspTrain} function allows users to include lags of all feature variables and also to update the training window over time. Including lags of the features in the data matrix can significantly reduce the negative effects of autocorrelation. Re-estimating the projection matrix and test statistic thresholds at pre-specified time intervals reduces the negative effects of non-linearity and non-stationarity in the observations.

The idea is to divide a non-linear and non-stationary process along some boundaries (every day, for instance), and then the process becomes locally linear and stationary within the window. As time progresses, the oldest observations are ``forgotten'' and the newest observations are ``learned'', which causes the projection and NOC thresholds to update over time.

\subsection{Model Training}
After the observations have been split by class, the \texttt{mspTrain} function will call the internal function \texttt{processMonitor}, which in turn calls the internal function \texttt{faultFilter}. This function will calculate a linear projection matrix of the data by taking the PCA of the training data matrix. The observations will then be projected linearly into a reduced-feature subspace which preserves a chosen proportion of the energy of the training data, where the energy of a matrix is the relative sum of eigenvalues of that matrix. The default proportion is 90\%. This projection is calculated by the internal \texttt{pca} function.

Furthermore, non-parametric threshold values are calculated for the two process monitoring statistics -- \emph{Squared Prediction Error} and \emph{Hotelling's} $T^2$. These monitoring statistics are described in the motivating paper. These threshold values are found in the internal \texttt{threshold} function, and passed through the function pipe to be returned by \texttt{mspTrain}. The $\alpha$-level of the nonparametric threshold is controlled by the user, and its default value is 0.001.

Finally, the \texttt{mspTrain} function will remove any observation which would cause an alarm from the training data set. The alarm free observations will be returned in one \texttt{xts} matrix, while the alarmed observations will be returned by another. When training your process monitor, pay attention to the observations flagged as alarms. The proportion of observations flagged as faults may be higher than the $\alpha$-level specified, so some tuning may be necessary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  mspMonitor and mspWarning  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Monitor and Issue Alarms with \texttt{mspMonitor} and \texttt{mspWarning}}

After training the model with \texttt{mspTrain}, the projection matrices and non-parametric monitoring statistic thresholds can be used to flag incoming observations. This function can check every observation in a test matrix (useful when analyzing past data), but was instead designed to test a single incoming observation at a time via a script or batch file. To this end, the \texttt{mspMonitor} function projects a single observation with the class projection matrices returned by \texttt{mspTrain} and checks the observation's \emph{SPE} and $T^2$ statistics against the thresholds returned by \texttt{mspTrain}. The \texttt{mspMonitor} will then append the monitoring statistic values and indicators to the end of the observation row. Indicator values will be returned as a ``1'' if the values of these statistics exceed normal thresholds. This new appended observation will be passed to the \texttt{mspWarning} function.

If an observation returned by the \texttt{mspMonitor} function has positive statistic indicator values for either the SPE or $T^2$ monitoring statistics, then the \texttt{mspWarning} function will query the last set $r$ observations for other flags. If all $r$ observations are positive for anomalies, then the \texttt{mspWarning} function will issue an alarm. This $r$ is the parameter \texttt{faultsToTriggerAlarm}, and it defaults to 5. However, this default value depends heavily on the scale of the data: for continuous observations aggregated and recorded every five seconds, the number of sequential faults necessary to trigger an alarm should be very high, perhaps even 20 or more. For observations aggregated to the 10-minute-scale, only three sequential faults may be necessary.

In future updates of this package, this function will also have an option to issue an alarm if a critical mass of non-sequential alarms is reached in a set period of observations. This modification may be necessary if the observation level becomes more fine than the 1-minute-level. Additionally, this function will also be equipped to take in a cell phone number and service provider and issue an alarm via SMS through email.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%  Example Workflow  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Example Simulation Workflow}

This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package. This package depends on a few other packages, but most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
<<r load_mvMonitoring>>=
library(devtools)
# install.packages("BMS") # If necessary
build("C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring")
library(mvMonitoring)
@

\subsection{Generating Synthetic Data}
First begin by generating multi-state data from a fault scenario. This code will yield observations under Fault 2A, as described the Synthetic Fault Induction section. We choose the default options for the period length (7 days * 24 hours * 60 minutes = 10,080 observations), the starting index of the fault (8500 out of 10080), and the time stamp for beginning the data is 16 May of 2016 at 10:00AM (my wedding anniversary). As we can see from the \texttt{str()} function, we have an \texttt{xts} matrix with 10080 rows and four columns (the state indicator and the three features).

<<r generate_Data>>=
fault1A_xts <- mspProcessData(faults = "A1",
                              period = 7 * 24 * 60,
                              faultStartIndex = 8500,
                              startTime = "2015-05-16 10:00:00 CST")
str(fault1A_xts)
@

\subsection{Train the Fault Detection Threshold}
Now that these observations are generated and stored in memory, the \texttt{mspTrain} function can train the MSAD-PCA model. The last 1620 observations (27 hours' worth) will be saved for testing. The \texttt{mspTrain} function takes in the training data set partitioned between the observation and the label column. If this function errors, make sure the label column is not included in the data matrix -- this will cause a singularity in the data. The function will
\begin{enumerate}
\item Train on the first three days' worth of observations, as set by \texttt{trainObs}.
%
\item Scan the fourth day for anomalies, as set by \texttt{updateFreq}.
%
\item Remove any alarmed observations.
%
\item ``Forget'' the first day's observations.
%
\item ``Learn'' the non-alarmed observations from the fourth day.
%
\item Retrain and repeat until the end of the data matrix
\end{enumerate}

Furthermore, the \texttt{Dynamic = TRUE} option means that the \texttt{mspTrain} function will include the lags specified by the \texttt{lagsIncluded} argument. Finally, the number of sequential anomalous observations necessary to raise an alarm is set at 5 by the \texttt{faultsToTriggerAlarm} argument. These last three arguments are set to their defaults.
<<r train>>=
train1A_xts <- fault1A_xts[1:8461,]
# This function will run in 13 seconds on the author's machine.
train1A_ls <- mspTrain(data = train1A_xts[,-1],
                       labelVector = train1A_xts[,1],
                       trainObs = 3 * 24 * 60,
                       updateFreq = 1 * 24 * 60,
                       Dynamic = TRUE,
                       lagsIncluded = 0:1,
                       faultsToTriggerAlarm = 5)
@
The \texttt{mspTrain} function returns a list of four objects:
\begin{enumerate}
\item \texttt{FaultChecks}: An \texttt{xts} matrix of monitoring statistics and associated indicators for all observations after the burn-in of \texttt{trainObs}. It will have 10080 - \texttt{trainObs} number of rows and five columns:
	\begin{enumerate}
	\item \texttt{SPE}: the SPE statistic for each observation.
    %
    \item \texttt{SPE\_Flag}: an indicator showing if the SPE statistic for that observation is beyond the calculated threshold; 0 is normal, 1 is flagged.
    %
    \item \texttt{T2}: the $T^2$ statistic for each observation.
    %
    \item \texttt{T2\_Flag}: an indicator showing if the $T^2$ statistic for that observation is beyond the calculated threshold; 0 is normal, 1 is flagged.
    %
    \item \texttt{Alarm}: an indicator showing if the observation is in a sequence of flagged observations; 0 is normal, 1 is alarmed.
	\end{enumerate}
%
\item \texttt{Non\_Alarmed\_Obs}: An \texttt{xts} matrix will all observations with an alarm code of 0 from \texttt{FaultChecks}. Of note, this matrix contains the data, while the \texttt{FaultChecks} matrix only contains the monitoring statistics and indicators.
%
\item \texttt{Alarms}: An \texttt{xts} matrix of all the observations removed from the training data matrix.
%
\item \texttt{TrainingSpecs}: a list with length equal to the number of classes -- in this case 3. For each class, this list contains a list of six objects:
	\begin{enumerate}
	\item \texttt{SPE\_Threshold}: a named numeric scalar of the $1 - \alpha$ percentile of the non-parametric estimate of the SPE statistic density.
    %
    \item \texttt{T2\_Threshold}: a named numeric scalar of the $1 - \alpha$ percentile of the non-parametric estimate of the $T^2$ statistic density.
    %
    \item \texttt{projectionMatrix}: The $p \times q$ matrix of eigenvectors necessary to project a $p$-dimensional observation to $q$ dimensions. This is necessary to reduce the dimension of any test observation, and is used in calculating the SPE statistic for test observations.
    %
    \item \texttt{LambdaInv}: The inverse of the diagonal $q \times q$ matrix of eigenvalues. This matrix is used to calculate the $T^2$ statistic for test observations.
    %
    \item \texttt{muTrain}: The mean vector of the training observations. This is used to center the test observations on the training mean.
    %
    \item \texttt{RootPrecisTrain}: The $p \times p$ diagonal matrix of the inverse square roots of the feature variances. This is used to scale the test observations into the training scale.
	\end{enumerate}
\end{enumerate}

\subsection{Test New Observations for Anomalies}
The training data summary was given by \texttt{mspTrain}, so this information can now be used to monitor incoming observations for system faults.

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
% ```{r, message = FALSE}
% library(xts)
% test1A_xts <- fault1A_xts[8460:8520, -1]
% lagTest1A_xts <- lag.xts(test1A_xts, 0:1)
% lagTest1A_xts <- cbind(fault1A_xts[8461:8520,1],
%                        lagTest1A_xts[-1,])
% head(lagTest1A_xts)
% ```

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
% ```{r}
% monitor1A_xts <- mspMonitor(observations = lagTest1A_xts[,-1],
%                             labelVector = lagTest1A_xts[,1],
%                             trainingSummary = train1A_ls$TrainingSpecs)
% head(monitor1A_xts)
% ```

\subsection{Warn Operators During Alarms}
Note that all `Alarm` codes in the monitor matrix above are recorded with \texttt{NA} values. This is because the \texttt{mspMonitor} function does not check the sequential flag conditions of the monitor matrix. This is the responsibility of the \texttt{mspWarning} function. Because the \texttt{mspWarning} function is designed to test one incoming observation at a time through a script or batch file, the following example is designed to mimic the behavior of the \texttt{mspWarning} function as each new observation comes online.
% ```{r}
% alarm1A_xts <- monitor1A_xts
% for(i in 1:nrow(alarm1A_xts)){
%   if(i < (5 + 1)){
%     alarm1A_xts[1:i,] <- mspWarning(alarm1A_xts[1:i,])
%   }else{
%     alarm1A_xts[(i - 5):i,] <- mspWarning(alarm1A_xts[(i - 5):i,])
%   }
% }
% ```
The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
% ```{r}
% plot(alarm1A_xts[, ncol(alarm1A_xts)],
%      main = "Alarm Codes for Test Data")
% ```
The alarm codes are
\begin{enumerate}
\item ``0'': No alarm.
\item ``1'': Hotelling's $T^2$ alarm.
\item ``2'': Squared Prediction Error alarm.
\item ``3'': Both alarms.
\end{enumerate}

% Package Implementation in Practice
% Kathryn B. Newhart will send me a brief discussion of how she has implemented this package in wastewater treatment monitoring at a facility in Golden, CO.

\end{document}

### 2017-07-04 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Created a LaTeX vignette folder. In the LaTeX vignette, I am building the package 'mvMonitoring' with devtools::build(), so if the LaTeX vignette is in the proper vignettes folder, it will recursively attempt to build itself. This is bad.

--- 2017-07-04 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
@@
-\documentclass{report}
+\documentclass{report}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage{amsmath, amssymb}
@@
 \usepackage{enumerate}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 The exception is \texttt{BMS}.
-<<r load_mvMonitoring>>=
-library(devtools)
-# install.packages("BMS") # If necessary
-build("C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring")
-library(mvMonitoring)
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{library}\hlstd{(devtools)}
+\end{alltt}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'devtools' was built under R version 3.4.1}}\begin{alltt}
+\hlcom{# install.packages("BMS") # If necessary}
+\hlkwd{build}\hlstd{(}\hlstr{"C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring"}\hlstd{)}
+\end{alltt}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# "{}C:/PROGRA\textasciitilde{}1/R/R-34\textasciitilde{}1.0/bin/x64/R"{} --no-site-file --no-environ --no-save\ \ \textbackslash{}\\\#\#\ \  --no-restore --quiet CMD build\ \ \textbackslash{}\\\#\#\ \  "{}C:\textbackslash{}Users\textbackslash{}gabriel\_odom\textbackslash{}Documents\textbackslash{}GitHub\textbackslash{}mvMonitoring\textbackslash{}mvMonitoring"{}\ \ \textbackslash{}\\\#\#\ \  --no-resave-data --no-manual}}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# }}\begin{verbatim}
+## [1] "C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring_0.1.0.tar.gz"
+\end{verbatim}
+\begin{alltt}
+\hlkwd{library}\hlstd{(mvMonitoring)}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
 
@@
 
-<<r generate_Data>>=
-fault1A_xts <- mspProcessData(faults = "A1",
-                              period = 7 * 24 * 60,
-                              faultStartIndex = 8500,
-                              startTime = "2015-05-16 10:00:00 CST")
-str(fault1A_xts)
-@
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{fault1A_xts} \hlkwb{<-} \hlkwd{mspProcessData}\hlstd{(}\hlkwc{faults} \hlstd{=} \hlstr{"A1"}\hlstd{,}
+                              \hlkwc{period} \hlstd{=} \hlnum{7} \hlopt{*} \hlnum{24} \hlopt{*} \hlnum{60}\hlstd{,}
+                              \hlkwc{faultStartIndex} \hlstd{=} \hlnum{8500}\hlstd{,}
+                              \hlkwc{startTime} \hlstd{=} \hlstr{"2015-05-16 10:00:00 CST"}\hlstd{)}
+\hlkwd{str}\hlstd{(fault1A_xts)}
+\end{alltt}
+\begin{verbatim}
+## An 'xts' object on 2015-05-16 10:00:00/2015-05-23 09:59:00 containing:
+##   Data: num [1:10080, 1:4] 1 1 1 1 1 1 1 1 1 1 ...
+##  - attr(*, "dimnames")=List of 2
+##   ..$ : NULL
+##   ..$ : chr [1:4] "state" "x" "y" "z"
+##   Indexed by objects of class: [POSIXct,POSIXt] TZ: 
+##   xts Attributes:  
+##  NULL
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 These last three arguments are set to their defaults.
-<<r train>>=
-train1A_xts <- fault1A_xts[1:8461,]
-# This function will run in 13 seconds on the author's machine.
-train1A_ls <- mspTrain(data = train1A_xts[,-1],
-                       labelVector = train1A_xts[,1],
-                       trainObs = 3 * 24 * 60,
-                       updateFreq = 1 * 24 * 60,
-                       Dynamic = TRUE,
-                       lagsIncluded = 0:1,
-                       faultsToTriggerAlarm = 5)
-@
+% ```{r}
+% train1A_xts <- fault1A_xts[1:8461,]
+% # This function will run in 13 seconds on the author's machine.
+% train1A_ls <- mspTrain(data = train1A_xts[,-1],
+%                        labelVector = train1A_xts[,1],
+%                        trainObs = 3 * 24 * 60,
+%                        updateFreq = 1 * 24 * 60,
+%                        Dynamic = TRUE,
+%                        lagsIncluded = 0:1,
+%                        faultsToTriggerAlarm = 5)
+% ```
 The \texttt{mspTrain} function returns a list of four objects:

### 2017-07-04 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
LaTeX file complete.

@@
 library(devtools)
+library(xts)
 # install.packages("BMS") # If necessary
@@
                        faultsToTriggerAlarm = 5)
+str(train1A_ls)
 @
@@
 Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
-% ```{r, message = FALSE}
-% library(xts)
-% test1A_xts <- fault1A_xts[8460:8520, -1]
-% lagTest1A_xts <- lag.xts(test1A_xts, 0:1)
-% lagTest1A_xts <- cbind(fault1A_xts[8461:8520,1],
-%                        lagTest1A_xts[-1,])
-% head(lagTest1A_xts)
-% ```
+<<r lagging_Test>>=
+test1A_xts <- fault1A_xts[8460:8520, -1]
+lagTest1A_xts <- lag.xts(test1A_xts, 0:1)
+lagTest1A_xts <- cbind(fault1A_xts[8461:8520,1],
+                       lagTest1A_xts[-1,])
+head(lagTest1A_xts)
+@
 
@@
 Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
-% ```{r}
-% monitor1A_xts <- mspMonitor(observations = lagTest1A_xts[,-1],
-%                             labelVector = lagTest1A_xts[,1],
-%                             trainingSummary = train1A_ls$TrainingSpecs)
-% head(monitor1A_xts)
-% ```
+<<r monitor>>=
+monitor1A_xts <- mspMonitor(observations = lagTest1A_xts[,-1],
+                            labelVector = lagTest1A_xts[,1],
+                            trainingSummary = train1A_ls$TrainingSpecs)
+head(monitor1A_xts)
+@
 
@@
 Because the \texttt{mspWarning} function is designed to test one incoming observation at a time through a script or batch file, the following example is designed to mimic the behavior of the \texttt{mspWarning} function as each new observation comes online.
-% ```{r}
-% alarm1A_xts <- monitor1A_xts
-% for(i in 1:nrow(alarm1A_xts)){
-%   if(i < (5 + 1)){
-%     alarm1A_xts[1:i,] <- mspWarning(alarm1A_xts[1:i,])
-%   }else{
-%     alarm1A_xts[(i - 5):i,] <- mspWarning(alarm1A_xts[(i - 5):i,])
-%   }
-% }
-% ```
+<<r warnings>>=
+alarm1A_xts <- monitor1A_xts
+for(i in 1:nrow(alarm1A_xts)){
+  if(i < (5 + 1)){
+    alarm1A_xts[1:i,] <- mspWarning(alarm1A_xts[1:i,])
+  }else{
+    alarm1A_xts[(i - 5):i,] <- mspWarning(alarm1A_xts[(i - 5):i,])
+  }
+}
+@
 The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
-% ```{r}
-% plot(alarm1A_xts[, ncol(alarm1A_xts)],
-%      main = "Alarm Codes for Test Data")
-% ```
+<<r warning_Plot>>=
+plot(alarm1A_xts[, ncol(alarm1A_xts)],
+     main = "Alarm Codes for Test Data")
+@
 The alarm codes are
@@
 \end{enumerate}
-
+As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.
 % Package Implementation in Practice

### 2017-07-04 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
LaTeX file complete.

@@
 {\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'devtools' was built under R version 3.4.1}}\begin{alltt}
+\hlkwd{library}\hlstd{(xts)}
+\end{alltt}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'xts' was built under R version 3.4.1}}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: zoo}}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# \\\#\# Attaching package: 'zoo'}}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# The following objects are masked from 'package:base':\\\#\# \\\#\#\ \ \ \  as.Date, as.Date.numeric}}\begin{alltt}
 \hlcom{# install.packages("BMS") # If necessary}
@@
 These last three arguments are set to their defaults.
-% ```{r}
-% train1A_xts <- fault1A_xts[1:8461,]
-% # This function will run in 13 seconds on the author's machine.
-% train1A_ls <- mspTrain(data = train1A_xts[,-1],
-%                        labelVector = train1A_xts[,1],
-%                        trainObs = 3 * 24 * 60,
-%                        updateFreq = 1 * 24 * 60,
-%                        Dynamic = TRUE,
-%                        lagsIncluded = 0:1,
-%                        faultsToTriggerAlarm = 5)
-% ```
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{train1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{1}\hlopt{:}\hlnum{8461}\hlstd{,]}
+\hlcom{# This function will run in 13 seconds on the author's machine.}
+\hlstd{train1A_ls} \hlkwb{<-} \hlkwd{mspTrain}\hlstd{(}\hlkwc{data} \hlstd{= train1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
+                       \hlkwc{labelVector} \hlstd{= train1A_xts[,}\hlnum{1}\hlstd{],}
+                       \hlkwc{trainObs} \hlstd{=} \hlnum{3} \hlopt{*} \hlnum{24} \hlopt{*} \hlnum{60}\hlstd{,}
+                       \hlkwc{updateFreq} \hlstd{=} \hlnum{1} \hlopt{*} \hlnum{24} \hlopt{*} \hlnum{60}\hlstd{,}
+                       \hlkwc{Dynamic} \hlstd{=} \hlnum{TRUE}\hlstd{,}
+                       \hlkwc{lagsIncluded} \hlstd{=} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{,}
+                       \hlkwc{faultsToTriggerAlarm} \hlstd{=} \hlnum{5}\hlstd{)}
+\hlkwd{str}\hlstd{(train1A_ls)}
+\end{alltt}
+\begin{verbatim}
+## List of 4
+##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
+##   Data: num [1:4142, 1:5] 0.364 0.425 0.821 1.004 0.864 ...
+##  - attr(*, "dimnames")=List of 2
+##   ..$ : NULL
+##   ..$ : chr [1:5] "SPE" "SPE_Flag" "T2" "T2_Flag" ...
+##   Indexed by objects of class: [POSIXct,POSIXt] TZ: 
+##   xts Attributes:  
+##  NULL
+##  $ Non_Alarmed_Obs:An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
+##   Data: num [1:4142, 1:7] 2 3 1 1 1 1 1 1 1 1 ...
+##  - attr(*, "dimnames")=List of 2
+##   ..$ : NULL
+##   ..$ : chr [1:7] "state" "x" "y" "z" ...
+##   Indexed by objects of class: [POSIXct,POSIXt] TZ: 
+##   xts Attributes:  
+##  NULL
+##  $ Alarms         :An 'xts' object of zero-width
+##  $ TrainingSpecs  :List of 3
+##   ..$ 1:List of 6
+##   .. ..$ SPE_threshold   : Named num 4.7
+##   .. .. ..- attr(*, "names")= chr "99.9%"
+##   .. ..$ T2_threshold    : Named num 59.7
+##   .. .. ..- attr(*, "names")= chr "99.9%"
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.424 -0.384 0.437 0.433 -0.308 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.206 0 0 1.513
+##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.09 2.96 1.37 -2.05 ...
+##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.54 0 0 0 0 ...
+##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
+##   ..$ 2:List of 6
+##   .. ..$ SPE_threshold   : Named num 1.35
+##   .. .. ..- attr(*, "names")= chr "99.9%"
+##   .. ..$ T2_threshold    : Named num 76.8
+##   .. .. ..- attr(*, "names")= chr "99.9%"
+##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4995 -0.0334 0.4931 -0.5255 -0.1688 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.72 ...
+##   .. ..$ muTrain         : Named num [1:6] 2.977 -0.566 -4.498 2.951 -0.591 ...
+##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.07 0 0 0 0 ...
+##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
+##   ..$ 3:List of 6
+##   .. ..$ SPE_threshold   : Named num 5.85
+##   .. .. ..- attr(*, "names")= chr "99.9%"
+##   .. ..$ T2_threshold    : Named num 80.7
+##   .. .. ..- attr(*, "names")= chr "99.9%"
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.396 0.454 0.454 -0.153 0.461 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.276 0 0 0.499
+##   .. ..$ muTrain         : Named num [1:6] 0.528 0.272 1.44 0.568 0.258 ...
+##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.4 0 0 0 0 ...
+##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 The \texttt{mspTrain} function returns a list of four objects:
@@
 Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
-% ```{r, message = FALSE}
-% library(xts)
-% test1A_xts <- fault1A_xts[8460:8520, -1]
-% lagTest1A_xts <- lag.xts(test1A_xts, 0:1)
-% lagTest1A_xts <- cbind(fault1A_xts[8461:8520,1],
-%                        lagTest1A_xts[-1,])
-% head(lagTest1A_xts)
-% ```
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
+\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
+\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
+                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
+\hlkwd{head}\hlstd{(lagTest1A_xts)}
+\end{alltt}
+\begin{verbatim}
+##                     state         x         y        z       x.1
+## 2015-05-22 07:00:00     1 0.7465717 -1.582803 1.141042 0.3817970
+## 2015-05-22 07:01:00     1 0.8064225 -1.564885 1.226738 0.7465717
+## 2015-05-22 07:02:00     1 0.7621322 -1.603962 1.150504 0.8064225
+## 2015-05-22 07:03:00     1 0.7995411 -1.785750 1.149927 0.7621322
+## 2015-05-22 07:04:00     1 0.8638972 -1.822695 1.116856 0.7995411
+## 2015-05-22 07:05:00     1 0.7735952 -1.505855 1.139623 0.8638972
+##                            y.1       z.1
+## 2015-05-22 07:00:00  0.1052954 0.3582939
+## 2015-05-22 07:01:00 -1.5828027 1.1410421
+## 2015-05-22 07:02:00 -1.5648852 1.2267384
+## 2015-05-22 07:03:00 -1.6039621 1.1505043
+## 2015-05-22 07:04:00 -1.7857497 1.1499272
+## 2015-05-22 07:05:00 -1.8226952 1.1168557
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
-% ```{r}
-% monitor1A_xts <- mspMonitor(observations = lagTest1A_xts[,-1],
-%                             labelVector = lagTest1A_xts[,1],
-%                             trainingSummary = train1A_ls$TrainingSpecs)
-% head(monitor1A_xts)
-% ```
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
+                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
+                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
+\hlkwd{head}\hlstd{(monitor1A_xts)}
+\end{alltt}
+\begin{verbatim}
+##                             x         y        z       x.1        y.1
+## 2015-05-22 07:00:00 0.7465717 -1.582803 1.141042 0.3817970  0.1052954
+## 2015-05-22 07:01:00 0.8064225 -1.564885 1.226738 0.7465717 -1.5828027
+## 2015-05-22 07:02:00 0.7621322 -1.603962 1.150504 0.8064225 -1.5648852
+## 2015-05-22 07:03:00 0.7995411 -1.785750 1.149927 0.7621322 -1.6039621
+## 2015-05-22 07:04:00 0.8638972 -1.822695 1.116856 0.7995411 -1.7857497
+## 2015-05-22 07:05:00 0.7735952 -1.505855 1.139623 0.8638972 -1.8226952
+##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
+## 2015-05-22 07:00:00 0.3582939 0.3441627        0 29.445080       0    NA
+## 2015-05-22 07:01:00 1.1410421 0.3811468        0  3.329163       0    NA
+## 2015-05-22 07:02:00 1.2267384 0.2937754        0  3.222249       0    NA
+## 2015-05-22 07:03:00 1.1505043 0.1424375        0  2.810259       0    NA
+## 2015-05-22 07:04:00 1.1499272 0.2947956        0  2.630555       0    NA
+## 2015-05-22 07:05:00 1.1168557 0.8742699        0  3.708552       0    NA
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
 
@@
 Because the \texttt{mspWarning} function is designed to test one incoming observation at a time through a script or batch file, the following example is designed to mimic the behavior of the \texttt{mspWarning} function as each new observation comes online.
-% ```{r}
-% alarm1A_xts <- monitor1A_xts
-% for(i in 1:nrow(alarm1A_xts)){
-%   if(i < (5 + 1)){
-%     alarm1A_xts[1:i,] <- mspWarning(alarm1A_xts[1:i,])
-%   }else{
-%     alarm1A_xts[(i - 5):i,] <- mspWarning(alarm1A_xts[(i - 5):i,])
-%   }
-% }
-% ```
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{alarm1A_xts} \hlkwb{<-} \hlstd{monitor1A_xts}
+\hlkwa{for}\hlstd{(i} \hlkwa{in} \hlnum{1}\hlopt{:}\hlkwd{nrow}\hlstd{(alarm1A_xts))\{}
+  \hlkwa{if}\hlstd{(i} \hlopt{<} \hlstd{(}\hlnum{5} \hlopt{+} \hlnum{1}\hlstd{))\{}
+    \hlstd{alarm1A_xts[}\hlnum{1}\hlopt{:}\hlstd{i,]} \hlkwb{<-} \hlkwd{mspWarning}\hlstd{(alarm1A_xts[}\hlnum{1}\hlopt{:}\hlstd{i,])}
+  \hlstd{\}}\hlkwa{else}\hlstd{\{}
+    \hlstd{alarm1A_xts[(i} \hlopt{-} \hlnum{5}\hlstd{)}\hlopt{:}\hlstd{i,]} \hlkwb{<-} \hlkwd{mspWarning}\hlstd{(alarm1A_xts[(i} \hlopt{-} \hlnum{5}\hlstd{)}\hlopt{:}\hlstd{i,])}
+  \hlstd{\}}
+\hlstd{\}}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
 The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
-% ```{r}
-% plot(alarm1A_xts[, ncol(alarm1A_xts)],
-%      main = "Alarm Codes for Test Data")
-% ```
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{plot}\hlstd{(alarm1A_xts[,} \hlkwd{ncol}\hlstd{(alarm1A_xts)],}
+     \hlkwc{main} \hlstd{=} \hlstr{"Alarm Codes for Test Data"}\hlstd{)}
+\end{alltt}
+\end{kframe}
+\includegraphics[width=\maxwidth]{figure/r_warning_Plot-1}
+
+\end{knitrout}
 The alarm codes are

### 2017-07-07 README.Rmd
Updated Simulation_Vignette.Rmd because I hadn't looked at it in a while. This is to prepare for the pkgdown website build.

@@
 In addition, you can also run the following:
-```{r packLoad_GitHub}
+```{r packLoad_GitHub, eval=FALSE}
 devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
@@
 where you create the value of "tokenHere" by generating a personal access token (PAT) at https://github.com/settings/tokens and copying the quoted string to this argument.
+Load the library after installation by
+```{r packLoad}
+library(mvMonitoring)
+```
 

### 2017-07-07 docs/articles/MVSPC-Workflow.Rmd
Updated Simulation_Vignette.Rmd because I hadn't looked at it in a while. This is to prepare for the pkgdown website build.

---
title: "Multivariate Statistical Process Control with mvMonitoring"
author: "Gabriel Odom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This document serves to introduce engineers to the workflow necessary to follow in order to analyze multivariate process monitoring data via the `mvMonitoring` package.

<br>
<br>

# Introduction

This is the accompanying package to the research published by
[Kazor et al (2016)](https://link.springer.com/article/10.1007/s00477-016-1246-2) and forthcoming paper by [Odom et al (2017)](https://www.overleaf.com/read/vbfbjsywtkvv#/26878504/) (manuscript in progress). The `mvMonitoring` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.

## Why use `mvMonitoring`

The `mvMonitoring` package can be used to detect outliers in a correlated multivariate process with non-linear, non-stationary, or autocorrelated feature behavior. These process outliers are often indicative of system fault. The common  and naive approach to multivariate process monitoring is to use expert opinion to identify a few important features to monitor visually, and raise an alarm if these features travel outside pre-defined normal operating boundaries.

However, this split univariate approach fails to account for the correlated nature of the process features, so some engineers have taken to monitoring the system as a single correlated multivariate process rather than a collection of independent univaraite processes. In the literature review of the motivating papers, the authors cite how this approach has benefitted the science of process monitoring as a whole. Unfortunately, this approach has its own shortcomings -- namely, montioring a multivariate process in its original feature space can lead to exorbitant computational costs.

To this end, *principal components analysis* (PCA) and its many modifications have been employed to reduce the computation necessary to monitor a multivariate process as a whole. This package is an implementation of one such PCA modification.

## Multi- or Single-State AD-PCA

AD-PCA is *adaptive-dynamic* PCA, which accounts for non-linearity, non-stationarity, and autocorrelation in the multivariate process, and this modification is thoroghly discussed in Kazor et al (2016).

Multi-State Monitoring
  : a modification of PCA which accounts for multiple process states and models them seperately. States can be any mutually exclusive blocking factor, and states do not necessarily follow a strict order.

Multi-State AD-PCA (MSAD-PCA) allows process engineers to account for a few very different process states. Specifically, this modification should be used when features under different process states have different means, correlations, or variances.

<br>
<br>

# The `msp` Functions

These are brief descriptions of the external functions useful for multivariate statistical process monitoring via MSAD- or AD-PCA.

## Simulating Data with `mspProcessData`
This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations. We follow the seminal work of [Dong and McAvoy (1996)](http://onlinelibrary.wiley.com/doi/10.1002/aic.690420810/abstract) for generation of the foundational stationary and independent features.

### Latent Feature Creation
So that the simulated features have non-zero correlations, Dong and McAvoy created their three features all as polynomial functions of a single latent variable $t(s)$, where $s = 1, \ldots, \omega$ is the observational index of the process.

#### Autocorrelated and Non-Stationary Error
The `mspProcesData` function induces autocorrelation in $t$ through its errors, $\varepsilon_s$, where
\[
\varepsilon_1 \sim \mathcal{N}\left(\frac{1}{2}(a + b)(1 - \phi), \frac{b - a}{12} (1 - \phi ^ 2)\right),
\]
where $a = 0.01$ and $b = 2$. Now, we define the first-order autoregressive process on $\varepsilon_s$ by
\[
\varepsilon_s = \varphi\varepsilon_{s - 1} + (1 - \varphi)\varepsilon,
\]
where $\varepsilon$ is as defined in the previous expression and the autocorrelation component $\phi = 0.75$. The mean and variance multipliers are the mean and variance of a random variable from the $\mathcal{U}_{[a,b]}$ distribution.

#### The Non-Linear Latent Process
This $t$ vector will be sinusoidal with period $\omega = 7 * 24 * 60$ (signifying a weekly period in  minute-level observations). We then synthesize a $t$ with
\[
t^*_s = -\cos\left( \frac{2\pi}{\omega} s \right) + \epsilon_s,
\]
and scale $t^*$ to
\[
t = \frac{(b - a)(t^*_s - \text{min}(t^*_s))}{\text{max}(t^*_s) - \text{min}(t^*_s)} + a.
\]
Finally then, the $t$ vector will lie entirely in $[a,b]$.

### Single-State and Multi-State Features

#### Single State Features

First `mspProcessData` simulates three features, with each feaure operating under $k$ different states. Let $<x_k(t), y_k(t), z_k(t)>$ be the notation for State $k$. These are the three features under State 1 (normal operating conditions, or *NOC*) as three functions of $t$:
\begin{align}
  \textbf{x}(\textbf{t}) &\equiv \textbf{t} + \boldsymbol\varepsilon_1, \\
  \textbf{y}(\textbf{t}) &\equiv \textbf{t} ^ 2 - 3 * \textbf{t} + \boldsymbol\varepsilon_2, \\
  \textbf{z}(\textbf{t}) &\equiv -\textbf{t} ^ 3 + 3 * \textbf{t} ^ 2 + \boldsymbol\varepsilon_3,
\end{align}
where $\varepsilon_i \sim N(0, 0.01)$. The `mspProcessData` function calls the internal `processNOCdata` function to generate single-state observations under normal operating conditions (NOC).

#### Multi-State Features

The multi-state feature expression is induced by rotation and scaling of certain sets of observations. To induce a three-state, hourly switching process (the default), the `mspProcessData` function will create a label column that switches from "1" to "2" to "3" every hour. State "1" will be the features generated under the single-state assumption, while State "2" and State "3" are generated as follows. These states will be scaled rotations of the current $<x,y,z>$ set. The second state is yaw, pitch, and roll rotated by (0, 90, 30) degrees, and the scales are multiplied by (1, 0.5, 2). The third state is yaw, pitch, and roll rotated by (90, 0, -30) degrees, and the scales are multiplied by (0.25, 0.1, 0.75).

- $\mathcal{S}_1$: $\textbf{X}(t_s) := \langle x(t_s), y(t_s), z(t_s)\rangle$.

- $\mathcal{S}_2$: $\textbf{X}(t_s) := \langle x(t_s), y(t_s), z(t_s)\rangle \cdot \textbf{P}_1\boldsymbol\Lambda_1$, where
	\[
	\textbf{P}_1 = \begin{bmatrix}
	 0    &  0.50 & -0.87 \\
	 0    &  0.87 &  0.50 \\
	 1    &  0    &  0   
	\end{bmatrix}
	\]
is the orthogonal rotation matrix for a yaw, pitch and roll degree change of $\langle 0^{\circ}, 90^{\circ}, 30^{\circ} \rangle$, and $\boldsymbol\Lambda_1 = \text{diag}(1, 0.5, 2)$ is a diagonal scaling matrix.

- $\mathcal{S}_3$: $\textbf{X}(t_s) := \langle x(t_s), y(t_s), z(t_s)\rangle \cdot \textbf{P}_2\boldsymbol\Lambda_2$, where
	\[
	\textbf{P}_2 = \begin{bmatrix}
	 0    &  0.87 & -0.50 \\
	-1    &  0    &  0    \\
	 0    &  0.50 &  0.87
	\end{bmatrix}
	\]
is the orthogonal rotation matrix for a yaw, pitch and roll degree change of $\langle 90^{\circ}, 0^{\circ}, -30^{\circ} \rangle$, and $\boldsymbol\Lambda_2 = \text{diag}(0.25, 0.1, 0.75)$ is a diagonal scaling matrix.

These rotation matrices $\textbf{P}_1$ and $\textbf{P}_2$ turn the states in three-dimensional space so that the states are at right angles to each other in at least one dimension, and the scaling matrices $\boldsymbol\Lambda_1$ and $\boldsymbol\Lambda_2$ inflate or deflate the process variances along each principal component. The `mspProcessData` function calls the internal function `dataStateSwitch` which splits the observations by state and applies the state-specific rotation and scaling through the internal `rotateScale3D` function.

### Synthetic Fault Induction

Faults can be introduced to single- or multi-state data via the `mspProcessData` function. The default fault strt index is 8500, or roughly 84\% through the 10,080 observation cycle. These faults are added through the internal `faultSwitch` function.

- Fault 1A is a positive shift to all three features before state rotation: $\textbf{X}^*(t_s) = \textbf{X}(t_s) + 2,\ s \ge 8500$.

- Fault 1B is a positive shift to the $x$ feature before state rotation: $x^*(t_s) = x(t_s) + 2,\ s \ge 8500$.

- Fault 1C is a positive shift to the $x$ and $z$ features in State 3 only and *after* state rotation: $x^*(t_s) = x(t_s) + 2,\ z^*(t_s) = z(t_s) + 2,\ s \ge 8500$.

- Fault 2A is a positive drift across all the process monitoring features before state rotation: $\textbf{X}^*(t_s) = \textbf{X}(t_s) + (s - 8500)\times 10^{-3}$, $s > 8500$.

- Fault 2B is a positive drift across the $y$ and $z$ process monitoring features before state rotation: $y^*(t_s) = y(t_s) + (s - 8500)\times 10^{-3},\ z^*(t_s) = z(t_s) + (s - 8500)\times 10^{-3}$, $s > 8500$.

- Fault 2C is a negative drift in the $y$ process monitoring feature in State 2 only and *after* state rotation: $y^*(t_s) = y(t_s) - 1.5 \times \frac{s - 8500}{10080 - 8500}$, for $s > 8500$.

- Fault 3A is an amplification of the underlying latent variable $t$ for all features. The maximum latent drift of this fault will be 5 + 1: $\textbf{X}^*(t_s) = \textbf{X}(t_s^*),\ s > 8500$, where $t_s^* = \left[\frac{5(s - 8500)}{\omega - 8500} + 1\right]t_s$.

- Fault 3B is a mutation of the underlying latent variable $t$ for the $z$ feature: $z^*(t_s) = z(\log t_s^*)$, $s \ge 8500$. This fault will dampen the underlying latent effect for $z$ if $t_s > 1$ and amplify this effect if $t_s < 1$.

- Fault 3C is a polynomial mutation of the error for the $y$ feature in State 2 only and *after* state rotation: $y^*(t_s) = y(t_s) + 2 * \textbf{e}_3(s) - 0.25$, for $s > 8500$.

### Putting it all together...
The `mspProcessData` function can generate weeks' worth of non-linear, non-stationary, autocorrelated, multi-state, multivariate process data useful to test new process monitoring techniques. Users can generate observations under NOC to measure false alarm rates, or induce one of nine pre-built faults to test detection time and consistency with repeated Monte Carlo sampling. We expect this function will generate interesting data useful enough to compare new and improved process monitoring techniques with existing methods.

## Training with `mspTrain`

The `mspTrain` function will generate projection matrices and test statistic thresholds from test data matrices.

### The `xts` Data Matrix

An `xts` data matrix is first and foremost a matrix, *not* a data frame. For users very familiar with data frame manipulation (with `dplyr` for instance), the slight but profound differences between manipulating matrices and data frames become quickly apparent. Because of the class requirements for matrices, *all* features must be integer or double objects. The `mspTrain` function cannot train on character information.

The `xts` object class stands for *extendible time series* and comes from the package `xts`, which is itself built on the package `zoo`. The date and time information (necessarily as `POSIX` objects) are stored as the row indices of `xts` matrices. We recommend the package `lubridate` for manipulating `POSIX` objects.

### The Class Vector

When implementing single-state AD-PCA, this class vector simply needs to be a numeric column of the same value. However, for MSAD-PCA, the class vector should be an integer vector of class membership. The `mspTrain` function will split the observations by the class label, apply single-state AD-PCA to each class, then return the class-specific projection matrices and thresholds. Because of this split-apply-combine strategy, users must ensure that one or more classes are not too "rare" -- that is, the class-specific sample size should be sufficiently large to allow for stable covariance matrix inversion. For $p$ features (inlcuding lags), covariance inversion requires a class sample size greater than $p ^ 2 / 2$. Because of this, pay close attention to model parsimony -- don't block the observations on a factor unless the factor significantly affects the observations' mean vector or covariance matrix.

### Adaptive and Dynamic Modelling

Because of the non-linear, non-stationary, and autocorrelated nature of some process monitoring applications, the `mspTrain` function allows users to include lags of all feature variables and also to update the training window over time. Including lags of the features in the data matrix can significantly reduce the negative effects of autocorrelation. Re-estimating the projection matrix and test statistic thresholds at pre-specified time intervals reduces the negative effects of non-linearity and non-stationarity in the observations.

The idea is to divide a non-linear and non-stationary process along some boundaries (every day, for instance), and then the process becomes locally linear and stationary within the window. As time progresses, the oldest observations are "forgotten" and the newest observations are "learned", which causes the projection and NOC thresholds to update over time.

### Model Training

After the observations have been split by class, the `mspTrain` function will call the internal function `processMonitor`, which in turn calls the internal function `faultFilter`. This function will calculate a linear projection matrix of the data by taking the PCA of the training data matrix. The observations will then be projected linearly into a reduced-feature subspace which preserves a chosen proportion of the energy of the training data, where the energy of a matrix is the sum of eigenvalues of that matrix. The default proportion is 90\%. This projection is calculated by the internal `pca` function.

Furthermore, non-parametric threshold values are calculated for the two process monitoring statistics -- *Squared Prediction Error* and *Hotelling's $T^2$*. These monitoring statistics are described in the motivating paper. These threshold values are found in the internal `threshold` function, and passed through the function pipe to be returned by `mspTrain`. The $\alpha$-level of the nonparametric threshold is controlled by the user, and its default value is 0.001.

Finally, the `mspTrain` function will remove any observation which would cause an alarm from the training data set. The alarm free observations will be returned in one `xts` matrix, while the alarmed observations will be returned by another. When training your process monitor, pay attention to the observations flagged as alarms. The proportion of observations flagged as faults may be higher than the $\alpha$-level specified, so some tuning may be necessary.

## Monitoring Incoming Observations with `mspMonitor`

After training the model with `mspTrain`, the projection matrices and non-parametric monitoring statistic thresholds can be used to flag incoming observations. This function can check every observation in a test matrix (useful when analyzing past data), but was instead designed to test a single incoming observation at a time via a script or batch file. To this end, the `mspMonitor` function projects a single observation with the class projection matrices returned by `mspTrain` and checks the observation's SPE and $T^2$ statistics against the thresholds returned by `mspTrain`. The `mspMonitor` will then append the monitoring statistic values, and indicators if these values exceed normal thresholds, to the end of the observation row. This new appended observation will be passed to the `mspWarning` function.

## Issue a Warning with `mspWarning`

If an observation returned by the `mspMonitor` function has positive statistic indicator values for either the SPE or $T^2$ monitoring statistics, then the `mspWarning` function will query the last set $r$ observations for other flags. If all $r$ observations are positive for anomalies, then the `mspWarning` function will issue an alarm. This is the parameter "faultsToTriggerAlarm", and it defaults to 5. However, this default value depends heavily on the scale of the data: for continuous observations aggregated and recorded every five seconds, the number of sequential faults necessary to trigger an alarm should be very high, perhaps even 50 or more. For observations aggregated to the 10-minute-scale, only three sequential faults may be necessary.

In future updates of this package, this function will also have an option to issue an alarm if a critical mass of non-sequential alarms is reached in a set period of observations. This modification may be necessary if the observation level becomes more fine than the 1-minute-level. Additionally, this function will also be equipped to take in a cell phone number and service provider and issue an alarm via SMS through email.

<br>
<br>

# Example Simulation Workflow

This section provides a fully-commented code walkthrough for the main `msp` functions in the `mvMonitoring` package.

## Generating Synthetic Data
First begin by generating multi-state data from a fault scenario. This code will yield observations under Fault 2A, as described the Synthetic Fault Induction section. We choose the default options for the period length (7 days \* 24 hours \* 60 minutes = 10,080 observations), the starting index of the fault (8500 out of 10080), and the time stamp for beggining the data is 16 May of 2016 at 10:00AM (my wedding anniversary). As we can see from the `str()` function, we have an `xts` matrix with 10080 rows and four columns (the state indicator and the three features).
```{r, message = FALSE}
library(mvMonitoring)
fault1A_xts <- mspProcessData(faults = "A1",
                              period = 7 * 24 * 60,
                              faultStartIndex = 8500,
                              startTime = "2015-05-16 10:00:00 CST")

str(fault1A_xts)
```

## Train the Fault Detection Threshold
Now that these observations are generated and stored in memory, the `mspTrain` function can train the MSAD-PCA model. The last 1620 observations (27 hours' worth) will be saved for testing. The `mspTrain` function takes in the training data set partitioned between the observation and the label column. If this function errors, make sure the label column is not included in the data matrix -- this will cause a singularity in the data. The function will
1. Train on the first three days' worth of observations, as set by `trainObs`.
1. Scan the fourth day for anomalies, as set by `updateFreq`.
1. Remove any alarmed observations.
1. "Forget" the first day's observations.
1. "Learn" the non-alarmed observations from the fourth day.
1. Retrain and repeat until the end of the data matrix

Furthermore, the `Dynamic = TRUE` option means that the `mspTrain` function will include the lags specified by the `lagsIncluded` argument. Finally, the number of sequential anomalous observations necessary to raise an alarm is set at 5 by the `faultsToTriggerAlarm` argument. These last three arguments are set to their defaults.
```{r}
train1A_xts <- fault1A_xts[1:8461,]
# This function will run in 13 seconds on the author's machine.
train1A_ls <- mspTrain(data = train1A_xts[,-1],
                       labelVector = train1A_xts[,1],
                       trainObs = 3 * 24 * 60,
                       updateFreq = 1 * 24 * 60,
                       Dynamic = TRUE,
                       lagsIncluded = 0:1,
                       faultsToTriggerAlarm = 5)
```
The `mspTrain` function returns a list of four objects:

 - `FaultChecks`: An `xts` matrix of monitoring statistics and associated indicators for all observations after the burn-in of `trainObs`. It will have 10080 - `trainObs` number of rows and five columns:
     * `SPE`: the SPE statistic for each observation.
     * `SPE_Flag`: an indicator showing if the SPE statistic for that observation is beyond the calculated threshold; 0 is normal, 1 is flagged.
     * `T2`: the $T^2$ statistic for each observation.
     * `T2_Flag`: an indicator showing if the $T^2$ statistic for that observation is beyond the calculated threshold; 0 is normal, 1 is flagged.
     * `Alarm`: an indicator showing if the observation is in a sequence of flagged observations; 0 is normal, 1 is alarmed.
 - `Non_Alarmed_Obs`: An `xts` matrix will all observations with an alarm code of 0 from `FaultChecks`. Of note, this matrix contains the data, while the `FaultChecks` matrix only contains the monitoring statistics and indicators.
 - `Alarms`: An `xts` matrix of all the observations removed from the training data matrix.
 - `TrainingSpecs`: a list with length equal to the number of classes -- in this case 3. For each class, this list contains a list of six objects:
     * `SPE_Threshold`: a named numeric scalar of the 1 - $\alpha$ percentile of the non-parametric estimate of the SPE statistic density.
     * `T2_Threshold`: a named numeric scalar of the 1 - $\alpha$ percentile of the non-parametric estimate of the $T^2$ statistic density.
     * `projectionMatrix`: The $p \times q$ matrix of eigenvectors necessary to project a $p$-dimensional observation to $q$ dimensions. This is necessary to reduce the dimension of any test observation, and is used in calculating the SPE statistic for test observations.
     * `LambdaInv`: The inverse of the diagonal $q \times q$ matrix of eigenvalues. This matrix is used to calculate the $T^2$ statistic for test observations.
     * `muTrain`: The mean vector of the training observations. This is used to center the test observations on the training mean.
     * `RootPrecisTrain`: The $p \times p$ diagonal matrix of the inverse square roots of the feature variances. This is used to scale the test observations into the training scale.

## Test New Observations for Anomalies
The training data summary was given by `mspTrain`, so this information can now be used to monitor incoming observations for system faults.

### Adding Lagged Features
First, concatenate the last given observation from the training set as "row 0" of the test data set. This will enable `mspMonitor` to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
```{r, message = FALSE}
library(xts)
test1A_xts <- fault1A_xts[8460:8520, -1]
lagTest1A_xts <- lag.xts(test1A_xts, 0:1)
lagTest1A_xts <- cbind(fault1A_xts[8461:8520,1],
                       lagTest1A_xts[-1,])
head(lagTest1A_xts)
```

### Monitoring the Test Data
With the lagged test observations in the working environment, the `mspMonitor` function can be applied. This function (similarly to `mspTrain`) takes in the label information as a separate argument from the input data. Further, the `mspMonitor` function takes in the `TrainingSpecs` object returned in the results list from `mspTrain`. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
```{r}
monitor1A_xts <- mspMonitor(observations = lagTest1A_xts[,-1],
                            labelVector = lagTest1A_xts[,1],
                            trainingSummary = train1A_ls$TrainingSpecs)
head(monitor1A_xts)
```

## Warn Operators during Alarms
Note that all `Alarm` codes in the monitor matrix above are recorded with `NA` values. This is because the `mspMonitor` function does not check the sequential flag conditions of the monitor matrix. This is the responsibility of the `mspWarning` function. Because the `mspWarning` function is designed to test one incoming observation at a time through a script or batch file, the following example is designed to mimic the behavior of the `mspWarning` function as each new observation comes online.
```{r}
alarm1A_xts <- monitor1A_xts
for(i in 1:nrow(alarm1A_xts)){
  if(i < (5 + 1)){
    alarm1A_xts[1:i,] <- mspWarning(alarm1A_xts[1:i,])
  }else{
    alarm1A_xts[(i - 5):i,] <- mspWarning(alarm1A_xts[(i - 5):i,])
  }
}
```
The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
```{r}
plot(alarm1A_xts[, ncol(alarm1A_xts)],
     main = "Alarm Codes for Test Data")
```
 The alarm codes are

- "0": No alarm.
- "1": Hotelling's $T^2$ alarm.
- "2": Squared Prediction Error alarm.
- "3": Both alarms.

<br>
<br>

# Package Implementation in Practice
Kathryn B. Newhart will send me a brief discussion of how she has implemented this package in wastewater treatment monitoring at a facility in Golden, CO.

### 2017-07-07 docs/articles/Simulation_Vignette.Rmd
Updated Simulation_Vignette.Rmd because I hadn't looked at it in a while. This is to prepare for the pkgdown website build.

---
title: "MSAD-PCA Walkthrough"
author: "Gabriel Odom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MSAD-PCA Walkthrough}
  %\VignetteEngine{rmarkdown::render}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# # To build the documentation PDF, use
# if(.Platform$OS.type == "windows"){
#   # PC - still hella buggy
# system("R CMD Rd2pdf C:\Users\gabriel_odom\Documents\GitHub\mvMonitoring\mvMonitoring")
# }else{
#   # Mac
# system("R CMD Rd2pdf /Users/gabrielodom/Documents/GitHub/mvMonitoring")
# }
```

## Multi-State Adaptive-Dynamic PCA Simulation

We create this package, `mvMonitoring`, from the foundation laid by Kazor et al (2016). The `mvMonitoring` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.

### The Interval Vector
We begin by simulating an autocorrelated interval-step vector $t$. This vector $t$ has induced autocorrelation in its errors, $\varepsilon$, where these autocorrelated errors have initial values and independent components given by \[ \varepsilon \sim \mathcal{N}\left(\frac{1}{2}(a + b)(1 - \phi), \frac{b - a}{12} (1 - \phi ^ 2)\right), \] where $\epsilon_1$ is a random draw from this distribution, $a = 0.01$, $b = 2$, and the autocorrelation component $\phi = 0.75$. The mean and variance multipliers are the mean and variance of a random variable from the $\mathcal{U}_{[a,b]}$ distribution. The full autocorrelated error structure is then \[ \epsilon_s = \phi\epsilon_{s - 1} + (1 - \phi)\varepsilon.
\]
This $t$ vector will be sinusoidal with period $\omega = 7 * 24 * 60$ (signifying a weekly period in  minute-level observations). We then synthesize a $t$ with $t^*_1 = -\cos\left(\frac{2\pi}{\omega}\right) + \epsilon_1$, and \[ t^*_s = -\cos\left(\frac{2\pi}{\omega}\right) + \epsilon_s.
\]
The final $t$ vector is the $t^*$ vector scaled to lie entirely in $[a,b]$.
```{r t_vec_initialized}
omega <- 60 * 24 * 7
phi <- 0.75
a <- 0.01; b <- 2
mean_t_err <- 0.5 * (a + b) # mean of Uniform(0.01,2)
var_t_err <- (b - a) / 12 # variance of Uniform(0.01,2)

# Create an autocorrelated vector of errors for the random variable t
t_err <- vector(length = omega)
# Initialise the errors so that the overall mean and variance match the sim of
# Kazor et al.
t_err[1] <- rnorm(n = 1,
                  mean = mean_t_err * (1 - phi),
                  sd = sqrt(var_t_err * (1 - phi ^ 2)))
for(s in 2:omega){
  t_err[s] <- phi * t_err[(s - 1)] +
    (1 - phi) * rnorm(n = 1,
                      mean = mean_t_err * (1 - phi),
                      sd = sqrt(var_t_err * (1 - phi ^ 2)))
}

# Now for the vector itself
s <- 1:omega
t_star <- -cos(2 * pi * s / omega) + t_err

# Now we scale the ts to match the ts from the Unif(0.01,2)
t_star_adj <- ((b - a) * (t_star - min(t_star))) /
  (max(t_star) - min(t_star)) + a
```
Now that we have created the underlying autocorrelated and non-stationary process vector $t$, we perform some simple confirmatory graphing techniques.

```{r t_vec_graphs, echo = FALSE}
plot(t_star_adj,
     type = "l",
     main = "Plot of t Scaled to [0.1,2]",
     xlab = "t")
pacf(t_star,
     main = "Partial ACF for the Series t")
```
As we can see, $t$ is autocorrelated and non-stationary with mean `r mean(t_star)` and variance `r var(t_star)`.

###  Features and State Features
We will simulate three features, with each feaure operating under $k$ different states. We will use $<x(t), y(t), z(t)>$ instead of the $<x_1(t), x_2(t), x_3(t)>$ notation used in Kazor et al. This will assist us when we introduce feature states. Our state notation will be $<x_k(t), y_k(t), z_k(t)>$ for State $k$.

We create the three features under State 1 (normal operating conditions, or \emph{NOC}) as three functions of $t$:
\begin{align}
\textbf{x}(\textbf{t}) &\equiv \textbf{t} + \boldsymbol\varepsilon_1, \\
\textbf{y}(\textbf{t}) &\equiv \textbf{t} ^ 2 - 3 * \textbf{t} + \boldsymbol\varepsilon_2, \\
\textbf{z}(\textbf{t}) &\equiv -\textbf{t} ^ 3 + 3 * \textbf{t} ^ 2 + \boldsymbol\varepsilon_3, \end{align}
where $\varepsilon_i \sim N(0, 0.01)$.

```{r state_1_init}
library(scatterplot3d)
library(magrittr)
library(tidyverse)
library(mvMonitoring)

normal_df <- data.frame(t = t_star_adj,
                        err1 = rnorm(n = omega, sd = sqrt(0.01)),
                        err2 = rnorm(n = omega, sd = sqrt(0.01)),
                        err3 = rnorm(n = omega, sd = sqrt(0.01)))

###  State 1  ###
normal_df %<>% mutate(x = t + err1,
                     y = t ^ 2 - 3 * t + err2,
                     z = -t ^ 3 + 3 * t ^ 2 + err3)

orig_state_mat <- normal_df %>%
                    select(x,y,z) %>%
                    as.matrix
```
Let's take a look at our 3D scatterplot:
```{r state1_scatter}
scatterplot3d(x = normal_df$x,
              y = normal_df$y,
              z = normal_df$x,
              angle = 15,
              highlight.3d = TRUE)
```

Now we can create data for our other two states. These states will be scaled rotations of the current $<x,y,z>$ set. Thus, we need the `mvMonitoring::rotateScale3D()` function from the `Rotation_Playground.R` file. The first state is yaw, pitch, and roll rotated by (0, 90, 30) degrees, and the scales are multiplied by (1, 0.5, 2).
```{r state_2_init}
###  State 2  ###
state2_angles <- list(yaw = 0,
                      pitch = 90,
                      roll = 30)
state2_scales <- c(1,0.5,2)
state2_mat <- orig_state_mat %*% 
  rotateScale3D(rot_angles = state2_angles,
                scale_factors = state2_scales)
```
We can see the effects of the rotation and scaling.
```{r state_2_scatter}
scatterplot3d(state2_mat)
```
The second state is yaw, pitch, and roll rotated by (90, 0, -30) degrees, and the scales are multiplied by (0.25, 0.1, 0.75).
```{r state_3_init}
###  State 3  ###
state3_angles <- list(yaw = 90,
                      pitch = 0,
                      roll = -30)
state3_scales <- c(0.25,0.1,0.75)
state3_mat <- orig_state_mat %*% mvMonitoring::rotateScale3D(rot_angles = state3_angles,
                                               scale_factors = state3_scales)
```
We can see the difference that State 3 creates.
```{r state_3_scatter}
scatterplot3d(state3_mat)
```

Now, let's combine all these state observations into one data frame, which we will then subset based on the state indicator.
```{r combine_state_data}
###  Combination and Cleaning  ###
# Now concatenate these vectors
normal_df$xState2 <- state2_mat[,1]
normal_df$yState2 <- state2_mat[,2]
normal_df$zState2 <- state2_mat[,3]
normal_df$xState3 <- state3_mat[,1]
normal_df$yState3 <- state3_mat[,2]
normal_df$zState3 <- state3_mat[,3]

# Add a State label column
normal_df %<>%
  mutate(state = rep(rep(c(1, 2, 3), each = 60), (24 / 3) * 7))

# Add a date-time column
normal_df %<>%
  mutate(dateTime = seq.POSIXt(from = as.POSIXct("2016-11-27 00:00:00 CST"),
                               by = "min", length.out = 10080))

###  Hourly Switching Process  ###
state1_df <- normal_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
state2_df <- normal_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
state3_df <- normal_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
normal_switch_df <- bind_rows(state1_df, state2_df, state3_df) %>%
  arrange(dateTime)
```

Let's take a look at the individual states, and their combined product.
```{r state_scatterplots}

normal_switch_df %>%
  filter(state == 1) %>%
  select(x, y, z) %>%
  scatterplot3d(xlim = c(-2, 3),
                ylim = c(-3, 1),
                zlim = c(-1, 5))

normal_switch_df %>%
  filter(state == 2) %>%
  select(x, y, z) %>%
  scatterplot3d(xlim = c(-2, 3),
                ylim = c(-3, 1),
                zlim = c(-1, 5))

normal_switch_df %>%
  filter(state == 3) %>%
  select(x, y, z) %>%
  scatterplot3d(xlim = c(-2, 3),
                ylim = c(-3, 1),
                zlim = c(-1, 5))

normal_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d(xlim = c(-2, 3),
                ylim = c(-3, 1),
                zlim = c(-1, 5))
```

###  Fault Introduction
We now create the faults for individual states and all states. We will introduce these faults 1000 time units after the end of training (to evauluate false positive rates). The first fault is to add 2 to each $<\textbf{x}(\textbf{t}), \textbf{y}(\textbf{t}), \textbf{z}(\textbf{t})>$.
```{r fault1A_intro}
faultStart <- 8500

###  Fault 1A  ###
# Shift each <x, y, z> by 2
shift <- 2
fault1A_df <- normal_df %>%
  select(dateTime, state, t, x, y, z) %>%
  mutate(x = x + shift,
         y = y + shift,
         z = z + shift)
fault1A_mat <- fault1A_df %>% select(x,y,z) %>% as.matrix

# State 2
fault1A_S2_mat <- fault1A_mat %*% mvMonitoring::rotateScale3D(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault1A_S2_mat)

# State 3
fault1A_S3_mat <- fault1A_mat %*% mvMonitoring::rotateScale3D(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault1A_S3_mat)

# Now concatenate these vectors
fault1A_df$xState2 <- fault1A_S2_mat[,1]
fault1A_df$yState2 <- fault1A_S2_mat[,2]
fault1A_df$zState2 <- fault1A_S2_mat[,3]
fault1A_df$xState3 <- fault1A_S3_mat[,1]
fault1A_df$yState3 <- fault1A_S3_mat[,2]
fault1A_df$zState3 <- fault1A_S3_mat[,3]

# Hourly switching process
fault1A_state1_df <- fault1A_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault1A_state2_df <- fault1A_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault1A_state3_df <- fault1A_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault1A_switch_df <- bind_rows(fault1A_state1_df,
                               fault1A_state2_df,
                               fault1A_state3_df) %>%
  arrange(dateTime)
```
Now, let's take a look at our process after introducing fault 1A.
```{r fault1A_scatter}
fault1A_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()
```
The second fault (Fault 1B) is to add 2 to feature $<\textbf{x}(\textbf{t})>$ only.
```{r fault1B_intro}
###  Fault 1B  ###
# Shift each x by 2
fault1B_df <- normal_df %>%
  select(dateTime, state, t, x, y, z) %>%
  mutate(x = x + shift)
fault1B_mat <- fault1B_df %>% select(x,y,z) %>% as.matrix

# State 2
fault1B_S2_mat <- fault1B_mat %*% mvMonitoring::rotateScale3D(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault1B_S2_mat)

# State 3
fault1B_S3_mat <- fault1B_mat %*% mvMonitoring::rotateScale3D(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault1B_S3_mat)

# Now concatenate these vectors
fault1B_df$xState2 <- fault1B_S2_mat[,1]
fault1B_df$yState2 <- fault1B_S2_mat[,2]
fault1B_df$zState2 <- fault1B_S2_mat[,3]
fault1B_df$xState3 <- fault1B_S3_mat[,1]
fault1B_df$yState3 <- fault1B_S3_mat[,2]
fault1B_df$zState3 <- fault1B_S3_mat[,3]

# Hourly switching process
fault1B_state1_df <- fault1B_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault1B_state2_df <- fault1B_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault1B_state3_df <- fault1B_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault1B_switch_df <- bind_rows(fault1B_state1_df,
                               fault1B_state2_df,
                               fault1B_state3_df) %>%
  arrange(dateTime)
```
We now look at the effect of Fault 1B on the scatterplot of the process.
```{r fault1B_scatter}
fault1B_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()
```

The third fault we introduce (Fault 2A) is a drift in each feature by $10 ^ {-3} * (\text{step} - 8500)$.
```{r fault2A_intro}
###  Fault 2A  ###
# Drift each <x, y, z> by (step - faultStart) / 10 ^ 3
drift_vec <- (1:omega - faultStart) / 10 ^ 3
drift_vec[drift_vec < 0] <- 0
fault2A_df <- normal_df %>%
  select(dateTime, state, t, x, y, z) %>%
  mutate(x = x + drift_vec,
         y = y + drift_vec,
         z = z + drift_vec)
fault2A_mat <- fault2A_df %>% select(x,y,z) %>% as.matrix

# State 2
fault2A_S2_mat <- fault2A_mat %*% mvMonitoring::rotateScale3D(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
# scatterplot3d(fault2A_S2_mat)

# State 3
fault2A_S3_mat <- fault2A_mat %*% mvMonitoring::rotateScale3D(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
# scatterplot3d(fault2A_S3_mat)

# Now concatenate these vectors
fault2A_df$xState2 <- fault2A_S2_mat[,1]
fault2A_df$yState2 <- fault2A_S2_mat[,2]
fault2A_df$zState2 <- fault2A_S2_mat[,3]
fault2A_df$xState3 <- fault2A_S3_mat[,1]
fault2A_df$yState3 <- fault2A_S3_mat[,2]
fault2A_df$zState3 <- fault2A_S3_mat[,3]

# Hourly switching process
fault2A_state1_df <- fault2A_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault2A_state2_df <- fault2A_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault2A_state3_df <- fault2A_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault2A_switch_df <- bind_rows(fault2A_state1_df,
                               fault2A_state2_df,
                               fault2A_state3_df) %>%
  arrange(dateTime)
```
Now we look at the scatterplot under this drift fault.
```{r fault2A_scatter}
fault2A_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()
```

The fourth fault we introduce (Fault 2B) is a drift in features $\textbf{y}$ and $\textbf{z}$ by $10 ^ {-3} * (\text{step} - 8500)$.
```{r fault2B_intro}
###  Fault 2B  ###
# Drift each <y, z> by (step - faultStart) / 10 ^ 3
fault2B_df <- normal_df %>%
  select(dateTime, state, t, x, y, z) %>%
  mutate(y = y + drift_vec,
         z = z + drift_vec)
fault2B_mat <- fault2B_df %>% select(x,y,z) %>% as.matrix

# State 2
fault2B_S2_mat <- fault2B_mat %*% mvMonitoring::rotateScale3D(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault2B_S2_mat)

# State 3
fault2B_S3_mat <- fault2B_mat %*% mvMonitoring::rotateScale3D(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault2B_S3_mat)

# Now concatenate these vectors
fault2B_df$xState2 <- fault2B_S2_mat[,1]
fault2B_df$yState2 <- fault2B_S2_mat[,2]
fault2B_df$zState2 <- fault2B_S2_mat[,3]
fault2B_df$xState3 <- fault2B_S3_mat[,1]
fault2B_df$yState3 <- fault2B_S3_mat[,2]
fault2B_df$zState3 <- fault2B_S3_mat[,3]

# Hourly switching process
fault2B_state1_df <- fault2B_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault2B_state2_df <- fault2B_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault2B_state3_df <- fault2B_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault2B_switch_df <- bind_rows(fault2B_state1_df,
                               fault2B_state2_df,
                               fault2B_state3_df) %>%
  arrange(dateTime)
```
We now inspect the effect of Fault 2B.
```{r fault2B_scatter}
fault2B_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()
```

Our fifth fault (Fault 3A) is to amplify the underlying $\textbf{t}$ signal vector as $\frac{3}{2 * 10080} * (10080 - \text{step}) * \textbf{t}$.
```{r fault3A_intro}
###  Fault 3A  ###
# Amplify t for each <x, y, z> by 3 * (omega - step) * t / (2 * omega)
amplify_vec <- 2 * (1:omega - faultStart) / (omega - faultStart) + 1
amplify_vec[amplify_vec < 1] <- 1
fault3A_df <- normal_df %>%
  select(dateTime, state, t, err1, err2, err3) %>%
  mutate(t = amplify_vec * t) %>%
  mutate(x = t + err1,
         y = t ^ 2 - 3 * t + err2,
         z = -t ^ 3 + 3 * t ^ 2 + err3)
fault3A_mat <- fault3A_df %>% select(x,y,z) %>% as.matrix

# State 2
fault3A_S2_mat <- fault3A_mat %*% mvMonitoring::rotateScale3D(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
scatterplot3d(fault3A_S2_mat)

# State 3
fault3A_S3_mat <- fault3A_mat %*% mvMonitoring::rotateScale3D(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
scatterplot3d(fault3A_S3_mat)

# Now concatenate these vectors
fault3A_df$xState2 <- fault3A_S2_mat[,1]
fault3A_df$yState2 <- fault3A_S2_mat[,2]
fault3A_df$zState2 <- fault3A_S2_mat[,3]
fault3A_df$xState3 <- fault3A_S3_mat[,1]
fault3A_df$yState3 <- fault3A_S3_mat[,2]
fault3A_df$zState3 <- fault3A_S3_mat[,3]

# Hourly switching process
fault3A_state1_df <- fault3A_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault3A_state2_df <- fault3A_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault3A_state3_df <- fault3A_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault3A_switch_df <- bind_rows(fault3A_state1_df,
                               fault3A_state2_df,
                               fault3A_state3_df) %>%
  arrange(dateTime)
```
Now inspect the effect of this fault
```{r fault3A_scatter}
fault3A_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()
```
Our last fault under consideration, Fault 3B, is a dampening fault to $\textbf{t}$ as $\log \textbf{t}$. As $\textbf{t}$ is bdd within $[0.01, 2]$, $\log\textbf{t}\in[-4.61, 0.7]$.
```{r fault3B_intro}
###  Fault 3B  ###
# Dampen t for z by log|t|
t_log <- normal_df$t
t_log[faultStart:omega] <- log(t_log[faultStart:omega])
fault3B_df <- normal_df %>%
  select(dateTime, state, t, err1, err2, err3) %>%
  mutate(t_damp = t_log) %>%
  mutate(x = t + err1,
         y = t ^ 2 - 3 * t + err2,
         z = -t_damp ^ 3 + 3 * t_damp ^ 2 + err3)
fault3B_mat <- fault3B_df %>% select(x,y,z) %>% as.matrix

# State 2
fault3B_S2_mat <- fault3B_mat %*% mvMonitoring::rotateScale3D(rot_angles = state2_angles,
                                                  scale_factors = state2_scales)
# scatterplot3d(fault3B_S2_mat)

# State 3
fault3B_S3_mat <- fault3B_mat %*% mvMonitoring::rotateScale3D(rot_angles = state3_angles,
                                                  scale_factors = state3_scales)
# scatterplot3d(fault3B_S3_mat)

# Now concatenate these vectors
fault3B_df$xState2 <- fault3B_S2_mat[,1]
fault3B_df$yState2 <- fault3B_S2_mat[,2]
fault3B_df$zState2 <- fault3B_S2_mat[,3]
fault3B_df$xState3 <- fault3B_S3_mat[,1]
fault3B_df$yState3 <- fault3B_S3_mat[,2]
fault3B_df$zState3 <- fault3B_S3_mat[,3]

# Hourly switching process
fault3B_state1_df <- fault3B_df %>%
  filter(state == 1) %>%
  select(dateTime, state, x, y, z)
fault3B_state2_df <- fault3B_df %>%
  filter(state == 2) %>%
  select(dateTime, state, x = xState2, y = yState2, z = zState2)
fault3B_state3_df <- fault3B_df %>%
  filter(state == 3) %>%
  select(dateTime, state, x = xState3, y = yState3, z = zState3)
fault3B_switch_df <- bind_rows(fault3B_state1_df,
                               fault3B_state2_df,
                               fault3B_state3_df) %>%
  arrange(dateTime)
```
We inspect the effect of the last fault on our scatterplot.
```{r fault3B_scatter}
fault3B_switch_df %>%
  select(x, y, z) %>%
  scatterplot3d()
```

###  The Seven Data Frames
The normal_df data frame is without fault. We will remove rows 8500 to 10080, and replace these rows with the same rows from each each of the fault data frames. We then store each of these seven `xts` matrices in a list.

Implementation notes: turn all the data frames into `xts` objects for Kazor's function to work, which we believe follows a depreciated version of `zoo`, so we need the `dateTime` column as the rownames of the data frame, not as an index. EDITED NOTE - B. Barnard and I rebuilt Kazor's code as a functional package called `mvMonitoring`. The functions in these packages use `xts` matrices as inputs.
```{r fault_dataframes}
library(xts)
normal_switch_xts <- xts(normal_switch_df[,-1],
                         order.by = normal_switch_df[,1])
# devtools::use_data(normal_switch_xts)

# Fault 1A
normal_w_fault1A_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                              fault1A_switch_df[faultStart:omega,])
fault1A_xts <- xts(normal_w_fault1A_df[,-1], order.by = normal_switch_df[,1])
# devtools::use_data(fault1A_xts)

# Fault 1B
normal_w_fault1B_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault1B_switch_df[faultStart:omega,])
fault1B_xts <- xts(normal_w_fault1B_df[,-1], order.by = normal_switch_df[,1])
# devtools::use_data(fault1B_xts)

# Fault 2A
normal_w_fault2A_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault2A_switch_df[faultStart:omega,])
fault2A_xts <- xts(normal_w_fault2A_df[,-1], order.by = normal_switch_df[,1])
# devtools::use_data(fault2A_xts)

# Fault 2B
normal_w_fault2B_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault2B_switch_df[faultStart:omega,])
fault2B_xts <- xts(normal_w_fault2B_df[,-1], order.by = normal_switch_df[,1])
# devtools::use_data(fault2B_xts)

# Fault 3A
normal_w_fault3A_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault3A_switch_df[faultStart:omega,])
fault3A_xts <- xts(normal_w_fault3A_df[,-1], order.by = normal_switch_df[,1])
# devtools::use_data(fault3A_xts)

# Fault 3B
normal_w_fault3B_df <- bind_rows(normal_switch_df[1:(faultStart - 1),],
                                 fault3B_switch_df[faultStart:omega,])
fault3B_xts <- xts(normal_w_fault3B_df[,-1], order.by = normal_switch_df[,1])
# devtools::use_data(fault3B_xts)
```

Now we clean up the environment, and load the data we've saved.
```{r sweepEnv}
# # uncomment these lines to use the data from the package. Comment them out
# # when generating new data.
# rm(list = ls())
# load("~/Documents/GitHub/mvMonitoring/data/normal_switch_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault1A_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault1B_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault2A_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault2B_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault3A_xts.rda")
# load("~/Documents/GitHub/mvMonitoring/data/fault3B_xts.rda")

faults_ls <- list(normal = normal_switch_xts,
                  fault1A = fault1A_xts,
                  fault1B = fault1B_xts,
                  fault2A = fault2A_xts,
                  fault2B = fault2B_xts,
                  fault3A = fault3A_xts,
                  fault3B = fault3B_xts)
```

### Feature Time-series Plots
Now that we've created and stored these feature, we can use time-series plots to confirm our multi-state vision as well as quickly ascertain the fault behavior.
```{r feature_ts_plots}
# Double check that faults are visible and according to plan:
# faults_ls$fault1A %>% select(x) %>% plot.ts()
# faults_ls$fault1A %>% select(y) %>% plot.ts()
# faults_ls$fault1A %>% select(z) %>% plot.ts()
# faults_ls$fault1B %>% select(x) %>% plot.ts()
# faults_ls$fault1B %>% select(y) %>% plot.ts()
# faults_ls$fault1B %>% select(z) %>% plot.ts()
# faults_ls$fault2A %>% select(x) %>% plot.ts()
# faults_ls$fault2A %>% select(y) %>% plot.ts()
# faults_ls$fault2A %>% select(z) %>% plot.ts()
# faults_ls$fault2B %>% select(x) %>% plot.ts()
# faults_ls$fault2B %>% select(y) %>% plot.ts()
# faults_ls$fault2B %>% select(z) %>% plot.ts()
# faults_ls$fault3A %>% select(x) %>% plot.ts()
# faults_ls$fault3A %>% select(y) %>% plot.ts()
# faults_ls$fault3A %>% select(z) %>% plot.ts()
# faults_ls$fault3B %>% select(x) %>% plot.ts()
# faults_ls$fault3B %>% select(y) %>% plot.ts()
# faults_ls$fault3B %>% select(z) %>% plot.ts()
faults_ls$normal$x %>% plot.xts()
faults_ls$normal$y %>% plot.xts()
faults_ls$normal$z %>% plot.xts()
faults_ls$fault1A$x %>% plot.xts()
faults_ls$fault1A$y %>% plot.xts()
faults_ls$fault1A$z %>% plot.xts()
faults_ls$fault1B$x %>% plot.xts() 
faults_ls$fault1B$y %>% plot.xts()
faults_ls$fault1B$z %>% plot.xts()
faults_ls$fault2A$x %>% plot.xts()
faults_ls$fault2A$y %>% plot.xts()
faults_ls$fault2A$z %>% plot.xts()
faults_ls$fault2B$x %>% plot.xts()
faults_ls$fault2B$y %>% plot.xts()
faults_ls$fault2B$z %>% plot.xts()
faults_ls$fault3A$x %>% plot.xts()
faults_ls$fault3A$y %>% plot.xts()
faults_ls$fault3A$z %>% plot.xts()
faults_ls$fault3B$x %>% plot.xts()
faults_ls$fault3B$y %>% plot.xts()
faults_ls$fault3B$z %>% plot.xts()
```

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspTrain(data = faults_ls$normal[1:8640, 2:4],
                         labelVector = faults_ls$normal[1:8640, 1],
                         trainObs = 5 * 24 * 60,
                         updateFreq = 24 * 60,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 0:2,
                         var.amnt = 0.95)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

# Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
(falseAlarmRate_SPE <- sum(results_ls$FaultChecks[,5] %in% c(2,3)) /
  nrow(results_ls$FaultChecks))
# The SPE false alarm rate hits 0 at alpha = 0.07.
(falseAlarmRate_T2 <- sum(results_ls$FaultChecks[,5] %in% c(1,3)) /
  nrow(results_ls$FaultChecks))
# The T2 false alarm rate hits 0 at alpha = 0.00015, and is at 16% at 0.07. The
# T2 statistic throws too many false alarms for my taste.
# These values were before we split the update observations by a third. These
# false alarm rates increased dramatically (0.19, 0.41), so we increased the
# number of training observations to 4320 (three days worth, up from 2880). The
# false alarm rates dropped back, but not nearly as low (0.0031, 0.0884).

results_ls$TrainingSpecs[[2]]$SPE_threshold
# Apparently, the SPE function is VERY sensitive to the change in the var.amnt
# parameter (defaults to 95%). At 0.95, the threshold is around 1.2-1.4. The
# closer this parameter is to 1, the lower the SPE threshold (overfitting?).
# This causes the abnormally high false alarm rate for state 2. However, when I
# drop var.amnt even to 94%, the threshold increases drastically (to between 18
# and 20); and if I increase var.amnt to 99%, the threshold drops to about
# 0.6-0.7. I need to speak with Dr. Hering about this.

# I think that right around 94% is the cutoff to include or not include one of
# the features, so we have almost a 0-1 loss cutoff there. Features aren't
# continuous, so I'm not sure the best course of action here.
```

## Test the Multi-State Monitoring function
```{r test_msad-pca}
# Create six observations with lags 0:2 included
laggedTestObs <- faults_ls$normal[8639:10080, -1]
laggedTestObs <- lag.xts(laggedTestObs, 0:2)
laggedTestObs <- laggedTestObs[-(1:2),]
laggedTestObs <- cbind(faults_ls$normal[8641:10080, 1], laggedTestObs)
testDataandFlags <- mvMonitoring::mspMonitor(observations = laggedTestObs[,-1],
           labelVector = laggedTestObs[,1],
           trainingSummary = results_ls$TrainingSpecs)
testDataandFlags[1:5,]
```

## Test the Warning function
```{r test-warning}
# This line will test if the function can check the last line at all.
mvMonitoring::mspWarning(testDataandFlags[1,])

# These lines will test each line as if it was just received:
alarmData <- testDataandFlags
for(i in 1:nrow(testDataandFlags)){
  alarmData[1:i,] <- mvMonitoring::mspWarning(alarmData[1:i,])
}

# False Alarms? 
alarmData[,15] %>% sum(na.rm = T)
alarmData[,11:15] %>% head
alarmData[,11:15] %>% tail

# What do the first three hours look like? What did it look like right before?
# Before
faults_ls$normal[8461:8640, 2:4] %>% scatterplot3d()
# After
alarmData[1:180,2:4] %>% scatterplot3d()
# I'm not seeing much difference - even the scales are the same. Let's look
# specifically at state 2:
# Before
faults_ls$normal[8521:8580, 2:4] %>% scatterplot3d()
# After
alarmData[61:120,2:4] %>% scatterplot3d()

# We are seeing a lot of false alarms in state 2 under NOC, but few to no false
# alarms in states 1 an 3
# faults_ls$normal[faults_ls$normal[,1] == 2, 2] %>% plot.xts()
# faults_ls$normal[faults_ls$normal[,1] == 2, 3] %>% plot.xts()
# faults_ls$normal[faults_ls$normal[,1] == 2, 4] %>% plot.xts()
# faults_ls$normal[faults_ls$normal[,1] == 2, 2:4] %>% scatterplot3d()
```

# Real Data
This data was sent to use from Kate Newhart in Golden, CO.

### Import the Data files
First, we import the two data sets. 
```{r realData_import}
library(readr)
if(.Platform$OS.type == "windows"){
  tenDayData_v2 <- read_csv("~/GitHub/mvMonitoring/mvMonitoring/inst/tenDayData_v2.csv", 
  col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
currentDayData_v2 <- read_csv("~/GitHub/mvMonitoring/mvMonitoring/inst/currentDayData_v2.csv", 
  col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
}else{
  tenDayData_v2 <- read_csv("~/Documents/GitHub/mvMonitoring/inst/tenDayData_v2.csv", 
                col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
currentDayData_v2 <- read_csv("~/Documents/GitHub/mvMonitoring/inst/currentDayData_v2.csv",
                col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
}

```
The first data set is of a 10-day period, and the second data set is from a single day. The first columns of each data set are DateTime columns. Now we can do some basic data exploration, and save the data sets as `xts` matrices. Because `readr` imports the data frame as a tibble, we use list subsetting to get at the index column.
```{r readData_EDA}
str(tenDayData_v2, give.attr = FALSE)
tenDay <- xts(tenDayData_v2[, -1], order.by = tenDayData_v2[[1]])
tenDay[nrow(tenDay),]

str(currentDayData_v2, give.attr = FALSE)
oneDay <- xts(currentDayData_v2[, -1], order.by = currentDayData_v2[[1]])
oneDay[1,]
```

### Clean and Save the Data
We see that the `oneDay` data matrix is adjacent to the last observation from the `tenDay` data matrix. Now we check the data matrices for NA values.
```{r newRealTestData}
anyNA(tenDay)
anyNA(oneDay)
```
The ten day data set contains NA values, so we need to deal with these. We also must check for constant or near-constant data vectors. These vectors will cause the eigendecomposition to fail.
```{r rmNA}
# Any constant columns? Columns with the same values can cause singularity issues.
sapply(1:ncol(tenDay), function(i){
  length(unique(tenDay[,i])) < 20
})
# From this, we see that columns 3, 6, 29, and 30 put us at risk of singularity
# issues.
plot.xts(tenDay[,3])
plot.xts(tenDay[,6])
plot.xts(tenDay[,29])
plot.xts(tenDay[,30])
# We necessarily remove column 29, as it is constant for multiple entire updates
tenDay_clean <- tenDay[,-29]
oneDay_clean <- oneDay[,-29]

# Now we remove the rows with NA observations
tenDay_clean <- na.omit(tenDay_clean)
nrow(tenDay) - nrow(tenDay_clean)

# devtools::use_data(oneDay_clean)
# devtools::use_data(tenDay_clean)
```
The clean data frame has 138 fewer observations.

### Training the AD-PCA Model
Now to analyse the training data, and pass the training information in order to test the testing data. Because the data do not come from a process with recorded state variables (or, more specifically, that we do not have such state information), we will give a column of 1s as the labels. Futher, we have ten days' worth of 10-minute-level observations, so we will train on $7 * 24 * 60 / 10 = 1008$ observations (seven days' worth), and update each day ($24 * 60 * 10 = 144$). Further, we will lag the features by one time step. CAVEAT: we're missing one observation: the `tenDay_clean` data matrix had 1299 rows, while our train (864) and returned faultChecks (434) account for 1298 rows. This missing row is the row we lost due to the lag.
```{r trainRealData}
tenDayResults_ls <- mvMonitoring::mspTrain(data = tenDay_clean,
                         labelVector = rep(1, nrow(tenDay_clean)),
                         trainObs = 1008,
                         updateFreq = 144,
                         alpha = 0.001,
                         faultsToTriggerAlarm = 3,
                         lagsIncluded = 0:1,
                         var.amnt = 0.95)
```

### Testing the New Observations
We will test the observations from the `oneDay_clean` data set. We must first lag the test observations. We'll borrow the lags we don't have from the previous day (in `nineDay_clean`).
```{r testRealData}
laggedOneDay <- lag.xts(oneDay_clean, 0:1)
laggedOneDay[1,36:70] <- tenDay_clean[nrow(tenDay_clean),]

realDataandFlags <- mvMonitoring::mspMonitor(observations = laggedOneDay,
           labelVector = rep(1, nrow(laggedOneDay)),
           trainingSummary = tenDayResults_ls$TrainingSpecs)
realDataandFlags[1,]
```
For some reason, that I don't know right now, `mspMonitor` is flagging all of these values as faults, which will trigger alarms for most of the day.
```{r realWarnings}
# These lines will test each line as if it was just received:
realAlarmData <- realDataandFlags
for(i in 1:nrow(realDataandFlags)){
  realAlarmData[1:i,] <- mvMonitoring::mspWarning(realAlarmData[1:i,])
}
tail(realAlarmData)
```
I'm not sure why this is happening. I'll have to dig in to it later. I do notice that both the SPE and T2 statistics are off the charts. The only component affecting them equally is the projection matrix P. We are estimating a 70 ^ 2 matrix using only 432 observations at a time, so this matrix could very well be unstable (we'd need around 2500 observations to stably estimate the scatter matrix).
EDIT: I was not supplying the training mean vector and precision matrix to the monitoring function, which means that the the test observations were not being centred and scaled. This did not make much impact in the simulated data, as the centered and scaled data would not be far off from the original values, except in state 2. This issue is fixed.

# Simulation Setup
We have also collapsed the data generation setup and implementation from this vignette into a function suite. The outward-facing function is called `mspProcessData`, and we now give an example.
```{r mspProcessEg}
simFaults_ls <- mspProcessData(faults = "All",
                               faultStartIndex = 8500,
                               startTime = "2016-11-27 00:00:00 CST")

```
This process data was generated from a true three-state model. Therefore, our comparison for this data is the false alarm rate and time to alarm for the MSAD-PCA method to the AD-PCA method. We perform this comparison by overwriting the `state` column of the data frames with a single value (labelling the observations as if they came from a true single-state model).

## True Multi-State Observations
We first assume that the observations do come from a multi-state process. This means that we will test AD-PCA by incorrectly assuming that all observations come from the same state. We first draw a list of data matrices. Then we look at false alarm rates for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA. We also measure detection time for all faults for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA.
```{r trueMultiState_sim, message = FALSE}
# We get warnings of "no non-missing arguments to min; returning Inf" when
# none of the observations yield alarms. Suppress this with ? "message = FALSE"
# doesn't work.
library(parallel) # use mclapply on Mac, parLapply on Windows
library(tidyverse)
library(xts)
a <- Sys.time()
cl <- makeCluster(getOption("cl.cores", 8))
clusterEvalQ(cl, library(tidyverse))
clusterEvalQ(cl, library(xts))
clusterEvalQ(cl, library(mvMonitoring))
msadResults5_ls <- parLapply(cl = cl, 1:100, function(void){
# msadResults2_ls <- mclapply(1:1000, mc.cores = 8L, function(void){

  ##########   Draw a Random Data Set   ##########
  msadpcaObs_ls <- mspProcessData(faults = c("NOC", "C1", "C2", "C3"), # "All"
                              faultStartIndex = 8500,
                              startTime = "2016-11-27 00:00:00 CST",
                              multiState = TRUE,
                              adpcaTest = TRUE)

  ##########   False Alarm Rates   ##########
  ###  MSAD-PCA: Assume the Correct State  ###
  # False Alarm Rates (NOC Data)
  msadpcaNOC_ls <- mspTrain(data = msadpcaObs_ls$NOC[, 2:4],
                                    labelVector = msadpcaObs_ls$NOC[, 1],
                                    trainObs = 3 * 24 * 60,
                                    updateFreq = 24 * 60,
                                    alpha = 0.001,
                                    lagsIncluded = 0:2)

  # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
  # SPE
  falseAlarmSPE_msad <- sum(msadpcaNOC_ls$FaultChecks[,5] %in% c(2,3)) /
    nrow(msadpcaNOC_ls$FaultChecks)
  # T2
  falseAlarmT2_msad <- sum(msadpcaNOC_ls$FaultChecks[,5] %in% c(1,3)) /
    nrow(msadpcaNOC_ls$FaultChecks)

  ###  AD-PCA: Incorrectly Assume Equal States  ###
  adpcaNOC_ls <- mspTrain(data = msadpcaObs_ls$NOC[, 2:4],
                                  labelVector = msadpcaObs_ls$NOC[, 5],
                                  trainObs = 3 * 24 * 60,
                                  updateFreq = 24 * 60,
                                  alpha = 0.001,
                                  lagsIncluded = 0:2)

  # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
  # SPE
  falseAlarmSPE_ad <- sum(adpcaNOC_ls$FaultChecks[,5] %in% c(2,3)) /
    nrow(adpcaNOC_ls$FaultChecks)
  # T2
  falseAlarmT2_ad <- sum(adpcaNOC_ls$FaultChecks[,5] %in% c(1,3)) /
    nrow(adpcaNOC_ls$FaultChecks)

  ###  Return Data Frame  ###
  FA_rates <- data.frame(MSAD_SPE = falseAlarmSPE_msad,
                         MSAD_T2 = falseAlarmT2_msad,
                         AD_SPE = falseAlarmSPE_ad,
                         AD_T2 = falseAlarmT2_ad)

  ##########   Time to Fault Detection   ##########

  # Train the two models
  msadpca_MS_Results_ls <- mspTrain(data = msadpcaObs_ls$NOC[1:7500, 2:4],
                            labelVector = msadpcaObs_ls$NOC[1:7500, 1],
                            trainObs = 3 * 24 * 60,
                            updateFreq = 24 * 60,
                            alpha = 0.001,
                            lagsIncluded = 0:2)
  adpca_MS_Results_ls <- mspTrain(data = msadpcaObs_ls$NOC[1:7500, 2:4],
                          labelVector = msadpcaObs_ls$NOC[1:7500, 5],
                          trainObs = 3 * 24 * 60,
                          updateFreq = 24 * 60,
                          alpha = 0.001,
                          lagsIncluded = 0:2)

  # Subset out the normal operating data
  faultsSimRes <- lapply(msadpcaObs_ls[names(msadpcaObs_ls) != "NOC"],
                         function(mat){
    # Testing the apply statement
    # mat <- msadpcaObs_ls$C1

    ###  MSAD-PCA: Assume the Correct State  ###
    # Take our testing data
    testObs <- mat[7499:10080, 2:4]
    # lag the test data and cut the NA observations
    testObs <- lag.xts(testObs, 0:2)
    testObs <- testObs[-(1:2),]
    # re-attach the *CORRECT* state label
    msad_MS_TestObs <- cbind(mat[7501:10080, 1], testObs)
    # Run the test data through the Monitor function
    msad_MS_DataandFlags <- mspMonitor(observations = msad_MS_TestObs[,-1],
                                       labelVector = msad_MS_TestObs[,1],
                                       trainingSummary =
                                         msadpca_MS_Results_ls$TrainingSpecs)
    # Check for alarms
    msad_MS_Alarm <- msad_MS_DataandFlags
    for(i in 1:nrow(msad_MS_DataandFlags)){
      msad_MS_Alarm[1:i,] <- mspWarning(msad_MS_Alarm[1:i,])
    }

    ## Time to first alarm
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # Use suppressWarnings() on the min() function. If the which() function
    # returns an integer(0), its minimum is Inf, but it throws a warning. These
    # warnings will fill the console under heavy repitition, so suppress them.
    # SPE
    # All alarms: which(msad_MS_Alarm[1:2580,15] %in% c(2,3))
    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(2,3))
    time2SPE_msad <- suppressWarnings(min(time2SPE_msad))
    # T2
    # All alarms: which(msad_MS_Alarm[1:2580,15] %in% c(1,3))
    time2T2_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(1,3))
    time2T2_msad <- suppressWarnings(min(time2T2_msad))

    ###  AD-PCA: Assume Equal States  ###
    # Attach the *incorrect* state label instead of the correct label
    ad_MS_TestObs <- cbind(mat[7501:10080, 5], testObs)
    # Run the test data through the Monitor function
    ad_MS_DataandFlags <- mspMonitor(observations = ad_MS_TestObs[,-1],
                                     labelVector = ad_MS_TestObs[,1],
                                     trainingSummary =
                                       adpca_MS_Results_ls$TrainingSpecs)
    # Check for alarms
    ad_MS_Alarm <- ad_MS_DataandFlags
    for(i in 1:nrow(msad_MS_DataandFlags)){
      ad_MS_Alarm[1:i,] <- mspWarning(ad_MS_Alarm[1:i,])
    }

    ## Time to first alarm
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # SPE
    # All alarms: which(ad_MS_Alarm[,15] %in% c(2,3))
    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(2,3))
    time2SPE_ad <- suppressWarnings(min(time2SPE_ad))
    # T2
    # All alarms: which(ad_MS_Alarm[,15] %in% c(1,3))
    time2T2_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(1,3))
    time2T2_ad <- suppressWarnings(min(time2T2_ad))

    ###  Return Data Frame  ###
    data.frame(MSAD_SPE = time2SPE_msad,
               MSAD_T2 = time2T2_msad,
               AD_SPE = time2SPE_ad,
               AD_T2 = time2T2_ad)
  }) %>%
    do.call(bind_rows, .) %>% 
    mutate(Faults = names(msadpcaObs_ls[names(msadpcaObs_ls) != "NOC"]))

  ##########   Return a List   ##########
  list(falseAlarmRates = FA_rates,
       time2Detect = faultsSimRes)
})
b <- Sys.time() 
b - a # 91 seconds for each iteration. 15.3 minutes for 10 iterations, 12.1 
# hours for 500 iterations. On parallel Mac, 5.3 minutes for 10 iterations over
# 8 cores, 41.4 minutes for 100 iterations over 8 cores, and 6.7 hours for 1000
# iterations over 8 cores. On parallel Windows, 4.3 minutes for 10 iterations
# over 8 cores, and 5.4 hours for 1000 iterations over 8 cores.
stopCluster(cl)
```
Let's clean up these results.
```{r msadSim_Cleaning}
ms_FA_rates5 <- lapply(1:length(msadResults5_ls), function(i){
  msadResults5_ls[[i]]$falseAlarmRates
}) %>% do.call(bind_rows, .)
write_csv(ms_FA_rates4, path = "false_alarm_rates_ms_1000_20170323.csv")
ms_detectionTimes5 <- lapply(1:length(msadResults5_ls), function(i){
  msadResults5_ls[[i]]$time2Detect
}) %>% do.call(bind_rows, .)
write_csv(ms_detectionTimes4, path = "detection_times_ms_1000_20170323.csv")
```

Now we can look at the results.
```{r msadSim_graphics}
# False Alarm Rates
ms_FA_rates3[,1] %>% hist(xlim = c(0, 0.05), main = "MSAD SPE False Alarm Rates")
ms_FA_rates3[,2] %>% hist(xlim = c(0, 0.05), main = "MSAD T2 False Alarm Rates")
ms_FA_rates3[,3] %>% hist(xlim = c(0, 0.05), main = "AD SPE False Alarm Rates")
ms_FA_rates3[,4] %>% hist(xlim = c(0, 0.05), main = "AD T2 False Alarm Rates")

###  Detection Times  ###
# Fault 1A
ms_detectionTimes3 %>%
  filter(Faults == "A1") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 1B
ms_detectionTimes3 %>%
  filter(Faults == "B1") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 2A
ms_detectionTimes3 %>%
  filter(Faults == "A2") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 2B
ms_detectionTimes3 %>%
  filter(Faults == "B2") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 3A
ms_detectionTimes3 %>%
  filter(Faults == "A3") %>%
  select(-Faults) %>% 
  sapply(summary)

# Fault 3B
ms_detectionTimes3 %>%
  filter(Faults == "B3") %>%
  select(-Faults) %>% 
  sapply(summary)

```

## True Single-State Observations
We first assume that the observations do not come from a multi-state process. This means that we will test MSAD-PCA by incorrectly assuming that observations come from different states: we will assign a state at random to each observation from "1", "2", or "3". We first draw a list of data matrices. Then we look at false alarm rates for multi-state data under normal operating conditions using AD-PCA and MSAD-PCA. We also measure detection time for all faults for single-state data under normal operating conditions using AD-PCA and MSAD-PCA.
```{r trueSingleState_sim, message = FALSE}
library(parallel) # use mclapply on Mac, parLapply on Windows
library(tidyverse)
library(xts)
a <- Sys.time()
cl <- makeCluster(getOption("cl.cores", 8))
clusterEvalQ(cl, library(tidyverse))
clusterEvalQ(cl, library(xts))
clusterEvalQ(cl, library(mvMonitoring))
adResults3_ls <- parLapply(cl = cl, 1:1000, function(void){
# adResults_ls <- mclapply(1:1000, mc.cores = 8L, function(void){
  ##########   Draw a Random Data Set   ##########
  adpcaObs_ls <- mspProcessData(faults = "All",
                              faultStartIndex = 8500,
                              startTime = "2016-11-27 00:00:00 CST",
                              multiState = FALSE,
                              msadpcaTest = TRUE)

  ##########   False Alarm Rates   ##########
  ###  MSAD-PCA: Assume the Incorrect State  ###
  # False Alarm Rates (NOC Data)
  msadpcaNOC_ls <- mspTrain(data = adpcaObs_ls$NOC[, 2:4],
                                    labelVector = adpcaObs_ls$NOC[, 5],
                                    trainObs = 3 * 24 * 60,
                                    updateFreq = 24 * 60,
                                    alpha = 0.001,
                                    lagsIncluded = 0:2)

  # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
  # SPE
  falseAlarmSPE_msad <- sum(msadpcaNOC_ls$FaultChecks[,5] %in% c(2,3)) /
    nrow(msadpcaNOC_ls$FaultChecks)
  # T2
  falseAlarmT2_msad <- sum(msadpcaNOC_ls$FaultChecks[,5] %in% c(1,3)) /
    nrow(msadpcaNOC_ls$FaultChecks)

  ###  AD-PCA: Correctly Assume Equal States  ###
  adpcaNOC_ls <- mspTrain(data = adpcaObs_ls$NOC[, 2:4],
                                  labelVector = adpcaObs_ls$NOC[, 1],
                                  trainObs = 3 * 24 * 60,
                                  updateFreq = 24 * 60,
                                  alpha = 0.001,
                                  lagsIncluded = 0:2)

  # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
  # SPE
  falseAlarmSPE_ad <- sum(adpcaNOC_ls$FaultChecks[,5] %in% c(2,3)) /
    nrow(adpcaNOC_ls$FaultChecks)
  # T2
  falseAlarmT2_ad <- sum(adpcaNOC_ls$FaultChecks[,5] %in% c(1,3)) /
    nrow(adpcaNOC_ls$FaultChecks)

  ###  Return Data Frame  ###
  FA_rates <- data.frame(MSAD_SPE = falseAlarmSPE_msad,
                         MSAD_T2 = falseAlarmT2_msad,
                         AD_SPE = falseAlarmSPE_ad,
                         AD_T2 = falseAlarmT2_ad)

  ##########   Time to Fault Detection   ##########

  # Train the two models
  msadpca_MS_Results_ls <- mspTrain(data = adpcaObs_ls$NOC[1:7500, 2:4],
  # Data is truly single-state, so we point the label vector at the wrong
  # column for the multi-state implementation. The states in column 5 are
  # generated at random
                            labelVector = adpcaObs_ls$NOC[1:7500, 5],
                            trainObs = 3 * 24 * 60,
                            updateFreq = 24 * 60,
                            alpha = 0.001,
                            lagsIncluded = 0:2)
  adpca_MS_Results_ls <- mspTrain(data = adpcaObs_ls$NOC[1:7500, 2:4],
  # Data is truly single-state, so we point the label vector at the correct
  # column for the single-state implementation. The state in column 1 is all
  # the same value
                          labelVector = adpcaObs_ls$NOC[1:7500, 1],
                          trainObs = 3 * 24 * 60,
                          updateFreq = 24 * 60,
                          alpha = 0.001,
                          lagsIncluded = 0:2)

  # Subset out the normal operating data
  faultsSimRes <- lapply(adpcaObs_ls[names(adpcaObs_ls) != "NOC"],
                         function(mat){

    ###  MSAD-PCA: Assume the Incorrect State  ###
    # Take our testing data
    testObs <- mat[7499:10080, 2:4]
    # lag the test data and cut the NA observations
    testObs <- lag.xts(testObs, 0:2)
    testObs <- testObs[-(1:2),]
    # Attach the *incorrect* state label instead of the correct label
    msad_MS_TestObs <- cbind(mat[7501:10080, 5], testObs)
    # Run the test data through the Monitor function
    msad_MS_DataandFlags <- mspMonitor(observations = msad_MS_TestObs[,-1],
                                       labelVector = msad_MS_TestObs[,1],
                                       trainingSummary =
                                         msadpca_MS_Results_ls$TrainingSpecs)
    # Check for alarms
    msad_MS_Alarm <- msad_MS_DataandFlags
    for(i in 1:nrow(msad_MS_DataandFlags)){
      msad_MS_Alarm[1:i,] <- mspWarning(msad_MS_Alarm[1:i,])
    }

    ## Time to first alarm
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # Use suppressWarnings() on the min() function. If the which() function
    # returns an integer(0), its minimum is Inf, but it throws a warning. These
    # warnings will fill the console under heavy repitition, so suppress them.
    # SPE
    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(2,3))
    time2SPE_msad <- suppressWarnings(min(time2SPE_msad))
    # T2
    time2T2_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(1,3))
    time2T2_msad <- suppressWarnings(min(time2T2_msad))

    ###  AD-PCA: Assume Equal States  ###
    # re-attach the *CORRECT* state label
    ad_MS_TestObs <- cbind(mat[7501:10080, 1], testObs)
    # Run the test data through the Monitor function
    ad_MS_DataandFlags <- mspMonitor(observations = ad_MS_TestObs[,-1],
                                     labelVector = ad_MS_TestObs[,1],
                                     trainingSummary =
                                       adpca_MS_Results_ls$TrainingSpecs)
    # Check for alarms
    ad_MS_Alarm <- ad_MS_DataandFlags
    for(i in 1:nrow(ad_MS_DataandFlags)){
      ad_MS_Alarm[1:i,] <- mspWarning(ad_MS_Alarm[1:i,])
    }

    ## Time to first alarm
    # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
    # SPE
    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(2,3))
    time2SPE_ad <- suppressWarnings(min(time2SPE_ad))
    # T2
    time2T2_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(1,3))
    time2T2_ad <- suppressWarnings(min(time2T2_ad))

    ###  Return Data Frame  ###
    data.frame(MSAD_SPE = time2SPE_msad,
               MSAD_T2 = time2T2_msad,
               AD_SPE = time2SPE_ad,
               AD_T2 = time2T2_ad)
  }) %>%
    do.call(bind_rows, .) %>% 
    mutate(Faults = names(adpcaObs_ls[names(adpcaObs_ls) != "NOC"]))

  ##########   Return a List   ##########
  list(falseAlarmRates = FA_rates,
       time2Detect = faultsSimRes)
})
b <- Sys.time() 
b - a # On parallel Mac, 5.9 minutes for 10 iterations over 8 cores and 14.6
# hours for 1000 iterations over 8 cores. On parallel Windows, 4.5 minutes for
# 10 iterations over 8 cores, and 6.0 hours for 1000 iterations over 8 cores.
stopCluster(cl)
```

Let's clean up these results.
```{r adSim_Cleaning}
ss_FA_rates <- lapply(1:length(adResults_ls), function(i){
  adResults3_ls[[i]]$falseAlarmRates
}) %>% do.call(bind_rows, .)
write_csv(ss_FA_rates, path = "false_alarm_rates_ss_1000_20170320.csv")
ss_detectionTimes <- lapply(1:length(adResults_ls), function(i){
  adResults3_ls[[i]]$time2Detect
}) %>% do.call(bind_rows, .)
write_csv(ss_detectionTimes, path = "detection_times_ss_1000_20170320.csv")
```

Now we can look at the results.

### 2017-07-07 docs/articles/MVSPC-Workflow.R

@@ -1,0 +1,48 @@
+## ---- message = FALSE----------------------------------------------------
+library(mvMonitoring)
+fault1A_xts <- mspProcessData(faults = "A1",
+                              period = 7 * 24 * 60,
+                              faultStartIndex = 8500,
+                              startTime = "2015-05-16 10:00:00 CST")
+
+str(fault1A_xts)
+
+## ------------------------------------------------------------------------
+train1A_xts <- fault1A_xts[1:8461,]
+# This function will run in 13 seconds on the author's machine.
+train1A_ls <- mspTrain(data = train1A_xts[,-1],
+                       labelVector = train1A_xts[,1],
+                       trainObs = 3 * 24 * 60,
+                       updateFreq = 1 * 24 * 60,
+                       Dynamic = TRUE,
+                       lagsIncluded = 0:1,
+                       faultsToTriggerAlarm = 5)
+
+## ---- message = FALSE----------------------------------------------------
+library(xts)
+test1A_xts <- fault1A_xts[8460:8520, -1]
+lagTest1A_xts <- lag.xts(test1A_xts, 0:1)
+lagTest1A_xts <- cbind(fault1A_xts[8461:8520,1],
+                       lagTest1A_xts[-1,])
+head(lagTest1A_xts)
+
+## ------------------------------------------------------------------------
+monitor1A_xts <- mspMonitor(observations = lagTest1A_xts[,-1],
+                            labelVector = lagTest1A_xts[,1],
+                            trainingSummary = train1A_ls$TrainingSpecs)
+head(monitor1A_xts)
+
+## ------------------------------------------------------------------------
+alarm1A_xts <- monitor1A_xts
+for(i in 1:nrow(alarm1A_xts)){
+  if(i < (5 + 1)){
+    alarm1A_xts[1:i,] <- mspWarning(alarm1A_xts[1:i,])
+  }else{
+    alarm1A_xts[(i - 5):i,] <- mspWarning(alarm1A_xts[(i - 5):i,])
+  }
+}
+
+## ------------------------------------------------------------------------
+plot(alarm1A_xts[, ncol(alarm1A_xts)],
+     main = "Alarm Codes for Test Data")
+

### 2017-07-07 docs/articles/Simulation_Vignette.R

@@ -1,0 +1,572 @@
+## ----setup, include=FALSE------------------------------------------------
+knitr::opts_chunk$set(echo = TRUE)
+# # To build the documentation PDF, use
+# # Mac
+# system("R CMD Rd2pdf /Users/gabrielodom/Documents/GitHub/mvMonitoring")
+# # PC - still hella buggy
+# system("R CMD Rd2pdf C:\Users\gabriel_odom\Documents\GitHub\mvMonitoring\mvMonitoring")
+
+## ----t_vec_initialized---------------------------------------------------
+omega <- 60 * 24 * 7
+phi <- 0.75
+a <- 0.01; b <- 2
+mean_t_err <- 0.5 * (a + b) # mean of Uniform(0.01,2)
+var_t_err <- (b - a) / 12 # variance of Uniform(0.01,2)
+
+# Create an autocorrelated vector of errors for the random variable t
+t_err <- vector(length = omega)
+# Initialise the errors so that the overall mean and variance match the sim of
+# Kazor et al.
+t_err[1] <- rnorm(n = 1,
+                  mean = mean_t_err * (1 - phi),
+                  sd = sqrt(var_t_err * (1 - phi ^ 2)))
+for(s in 2:omega){
+  t_err[s] <- phi * t_err[(s - 1)] +
+    (1 - phi) * rnorm(n = 1,
+                      mean = mean_t_err * (1 - phi),
+                      sd = sqrt(var_t_err * (1 - phi ^ 2)))
+}
+
+# Now for the vector itself
+t_star <- vector(length = omega)
+t_star[1] <- -cos(2 * pi / omega) + t_err[1]
+for(s in 2:omega){
+  t_star[s] <- -cos(2 * pi * s / omega) +
+    phi * t_err[(s - 1)] + (1 - phi) * t_err[s]
+}
+# Now we scale the ts to match the ts from the Unif(0.01,2)
+t_star_adj <- ((b - a) * (t_star - min(t_star))) /
+  (max(t_star) - min(t_star)) + a
+
+## ----t_vec_graphs, echo = FALSE------------------------------------------
+plot(t_star_adj,
+     type = "l",
+     main = "Plot of t Scaled to [0.1,2]",
+     xlab = "t")
+pacf(t_star,
+     main = "Partial ACF for the Series t")
+
+## ----t_vec_summary-------------------------------------------------------
+mean(t_star); var(t_star)
+cor(t_star_adj[2:omega], t_star_adj[1:(omega - 1)])
[…]

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
pkgdown doesn't like the path in .Rbuildignore, so switch "\" to "/" and it works. Also, I added a thesis paragraph, and labelled all the sections.

@@
 
+We outline this vignette as follows.
+In Section \ref{sec:D_Motivation}, we discuss the motivation for creating this package, and briefly explain the utility of multi-state process monitoring.
+In Section \ref{sec:D_DataGen}, we offer a thorough explination of how to generate the synthetic data we employed to test and compare the new multi-state modification of the process monitoring setup with the \texttt{mspProcessData} function.
+In Section \ref{sec:D_Train}, we describe the necessary information and data formatting to effectively train the fault detection algorithm using the \texttt{mspTrain} function.
+Then, in Section \ref{sec:D_Alarms}, we list and explain the necessary inputs to the \texttt{mspMonitor} and \texttt{mspWarning} functions and examine their outputs.
+Section \ref{sec:D_Workflow} shows a step-by-step walkthrough of how to implement the four \texttt{mvMonitoring} functions in practice.
+We offer some concluding remarks in Section \ref{sec:D_Conclusion}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%  Motivation  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Motivation} \label{sec:D_Motivation}
+
 \subsection{Why use \texttt{mvMonitoring}?}
@@
 
-\section{Simulating Data with \texttt{mspProcessData}}
+\section{Simulating Data with \texttt{mspProcessData}} \ref{sec:D_DataGen}
 This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations.
@@
 
-\section{Training with \texttt{mspTrain}}
+\section{Training with \texttt{mspTrain}} \label{sec:D_Train}
 
@@
 
-\section{Monitor and Issue Alarms with \texttt{mspMonitor} and \texttt{mspWarning}}
+\section{Monitor and Issue Alarms with \texttt{mspMonitor} and \texttt{mspWarning}} \label{sec:D_Alarms}
 
@@
 
-\section{Example Simulation Workflow}
+\section{Example Simulation Workflow} \label{sec:D_Workflow}
 
@@
 The exception is \texttt{BMS}.
-<<r load_mvMonitoring>>=
+<<r load_mvMonitoring, warning=FALSE, message=FALSE>>=
 library(devtools)
@@
 As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.
-% Package Implementation in Practice
-% Kathryn B. Newhart will send me a brief discussion of how she has implemented this package in wastewater treatment monitoring at a facility in Golden, CO.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%  Conclusion  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Conclusion} \label{sec:D_Conclusion}
+We have supplied our motivation for this package, and we have discussed implementing a multivariate process monitoring scheme with this package using the example of a decentralized WWT plant in Golden, CO.
+We believe that this software will provide system engineers with the tools necessary to quickly and accurately detect abnormalities in multivariate, autocorrelated, non-stationary, non-linear, and multi-state water treatment systems.
+Further, we have given a synthetic example showing how the functions within this package would be implemented and tuned in practice.
 

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
pkgdown doesn't like the path in .Rbuildignore, so switch "\" to "/" and it works. Also, I added a thesis paragraph, and labelled all the sections.

@@
 \hlkwd{library}\hlstd{(devtools)}
-\end{alltt}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'devtools' was built under R version 3.4.1}}\begin{alltt}
 \hlkwd{library}\hlstd{(xts)}
-\end{alltt}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'xts' was built under R version 3.4.1}}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Loading required package: zoo}}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# \\\#\# Attaching package: 'zoo'}}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# The following objects are masked from 'package:base':\\\#\# \\\#\#\ \ \ \  as.Date, as.Date.numeric}}\begin{alltt}
 \hlcom{# install.packages("BMS") # If necessary}
@@
 \end{alltt}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# "{}C:/PROGRA\textasciitilde{}1/R/R-34\textasciitilde{}1.0/bin/x64/R"{} --no-site-file --no-environ --no-save\ \ \textbackslash{}\\\#\#\ \  --no-restore --quiet CMD build\ \ \textbackslash{}\\\#\#\ \  "{}C:\textbackslash{}Users\textbackslash{}gabriel\_odom\textbackslash{}Documents\textbackslash{}GitHub\textbackslash{}mvMonitoring\textbackslash{}mvMonitoring"{}\ \ \textbackslash{}\\\#\#\ \  --no-resave-data --no-manual}}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# }}\begin{verbatim}
-## [1] "C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring_0.1.0.tar.gz"
+\begin{verbatim}
+## [1] "C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring_0.1.1.tar.gz"
 \end{verbatim}
@@
 ##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:5] 0.364 0.425 0.821 1.004 0.864 ...
+##   Data: num [1:4142, 1:5] 1.062 0.186 0.364 0.335 0.383 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##   ..$ 1:List of 6
-##   .. ..$ SPE_threshold   : Named num 4.7
+##   .. ..$ SPE_threshold   : Named num 4.61
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 59.7
+##   .. ..$ T2_threshold    : Named num 59.6
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.424 -0.384 0.437 0.433 -0.308 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.206 0 0 1.513
-##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.09 2.96 1.37 -2.05 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.425 -0.378 0.439 0.434 -0.305 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.208 0 0 1.482
+##   .. ..$ muTrain         : Named num [1:6] 1.39 -2.09 2.99 1.38 -2.05 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.54 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.55 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 2:List of 6
-##   .. ..$ SPE_threshold   : Named num 1.35
+##   .. ..$ SPE_threshold   : Named num 1.4
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 76.8
+##   .. ..$ T2_threshold    : Named num 74.6
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4995 -0.0334 0.4931 -0.5255 -0.1688 ...
-##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.72 ...
-##   .. ..$ muTrain         : Named num [1:6] 2.977 -0.566 -4.498 2.951 -0.591 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4962 -0.0673 0.4888 -0.5234 -0.187 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.284 0 0 0 0.732 ...
+##   .. ..$ muTrain         : Named num [1:6] 3.003 -0.564 -4.526 2.977 -0.589 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.07 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.08 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 3:List of 6
-##   .. ..$ SPE_threshold   : Named num 5.85
+##   .. ..$ SPE_threshold   : Named num 6.51
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 80.7
+##   .. ..$ T2_threshold    : Named num 83.4
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.396 0.454 0.454 -0.153 0.461 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.276 0 0 0.499
-##   .. ..$ muTrain         : Named num [1:6] 0.528 0.272 1.44 0.568 0.258 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.393 -0.452 -0.455 0.157 -0.464 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.274 0 0 0.507
+##   .. ..$ muTrain         : Named num [1:6] 0.527 0.273 1.434 0.567 0.259 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.4 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.6 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
@@
 ##                     state         x         y         z       x.1
-## 2015-05-22 07:00:00     1 0.7465717 -1.582803 1.141042 0.3817970
-## 2015-05-22 07:01:00     1 0.8064225 -1.564885 1.226738 0.7465717
-## 2015-05-22 07:02:00     1 0.7621322 -1.603962 1.150504 0.8064225
-## 2015-05-22 07:03:00     1 0.7995411 -1.785750 1.149927 0.7621322
-## 2015-05-22 07:04:00     1 0.8638972 -1.822695 1.116856 0.7995411
-## 2015-05-22 07:05:00     1 0.7735952 -1.505855 1.139623 0.8638972
+## 2015-05-22 07:00:00     1 0.5894923 -1.693457 0.9793838 0.4122657
+## 2015-05-22 07:01:00     1 0.7076477 -1.693444 1.1569904 0.5894923
+## 2015-05-22 07:02:00     1 0.6065543 -1.510750 1.0816650 0.7076477
+## 2015-05-22 07:03:00     1 0.5964738 -1.404200 0.9984129 0.6065543
+## 2015-05-22 07:04:00     1 0.7359302 -1.492578 0.9049884 0.5964738
+## 2015-05-22 07:05:00     1 0.7665503 -1.482806 0.9188497 0.7359302
 ##                            y.1       z.1
-## 2015-05-22 07:00:00  0.1052954 0.3582939
-## 2015-05-22 07:01:00 -1.5828027 1.1410421
-## 2015-05-22 07:02:00 -1.5648852 1.2267384
-## 2015-05-22 07:03:00 -1.6039621 1.1505043
-## 2015-05-22 07:04:00 -1.7857497 1.1499272
-## 2015-05-22 07:05:00 -1.8226952 1.1168557
+## 2015-05-22 07:00:00  0.1370214 0.4769939
+## 2015-05-22 07:01:00 -1.6934574 0.9793838
+## 2015-05-22 07:02:00 -1.6934436 1.1569904
+## 2015-05-22 07:03:00 -1.5107499 1.0816650
+## 2015-05-22 07:04:00 -1.4042005 0.9984129
+## 2015-05-22 07:05:00 -1.4925779 0.9049884
 \end{verbatim}
@@
 ##                             x         y         z       x.1        y.1
-## 2015-05-22 07:00:00 0.7465717 -1.582803 1.141042 0.3817970  0.1052954
-## 2015-05-22 07:01:00 0.8064225 -1.564885 1.226738 0.7465717 -1.5828027
-## 2015-05-22 07:02:00 0.7621322 -1.603962 1.150504 0.8064225 -1.5648852
-## 2015-05-22 07:03:00 0.7995411 -1.785750 1.149927 0.7621322 -1.6039621
-## 2015-05-22 07:04:00 0.8638972 -1.822695 1.116856 0.7995411 -1.7857497
-## 2015-05-22 07:05:00 0.7735952 -1.505855 1.139623 0.8638972 -1.8226952
+## 2015-05-22 07:00:00 0.5894923 -1.693457 0.9793838 0.4122657  0.1370214
+## 2015-05-22 07:01:00 0.7076477 -1.693444 1.1569904 0.5894923 -1.6934574
+## 2015-05-22 07:02:00 0.6065543 -1.510750 1.0816650 0.7076477 -1.6934436
+## 2015-05-22 07:03:00 0.5964738 -1.404200 0.9984129 0.6065543 -1.5107499
+## 2015-05-22 07:04:00 0.7359302 -1.492578 0.9049884 0.5964738 -1.4042005
+## 2015-05-22 07:05:00 0.7665503 -1.482806 0.9188497 0.7359302 -1.4925779
 ##                           z.1        SPE SPE_Flag        T2 T2_Flag Alarm
-## 2015-05-22 07:00:00 0.3582939 0.3441627        0 29.445080       0    NA
-## 2015-05-22 07:01:00 1.1410421 0.3811468        0  3.329163       0    NA
-## 2015-05-22 07:02:00 1.2267384 0.2937754        0  3.222249       0    NA
-## 2015-05-22 07:03:00 1.1505043 0.1424375        0  2.810259       0    NA
-## 2015-05-22 07:04:00 1.1499272 0.2947956        0  2.630555       0    NA
-## 2015-05-22 07:05:00 1.1168557 0.8742699        0  3.708552       0    NA
+## 2015-05-22 07:00:00 0.4769939 1.23315168        0 28.293817       0    NA
+## 2015-05-22 07:01:00 0.9793838 0.06691071        0  3.842885       0    NA
+## 2015-05-22 07:02:00 1.1569904 0.43929620        0  4.405378       0    NA
+## 2015-05-22 07:03:00 1.0816650 0.86684372        0  5.023986       0    NA
+## 2015-05-22 07:04:00 0.9984129 0.45658085        0  4.864228       0    NA
+## 2015-05-22 07:05:00 0.9049884 0.74949850        0  4.396364       0    NA
 \end{verbatim}

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Fixed a label

@@
 
-\section{Simulating Data with \texttt{mspProcessData}} \ref{sec:D_DataGen}
+\section{Simulating Data with \texttt{mspProcessData}} \label{sec:D_DataGen}
 This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations.

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Fixed a label

@@
 ##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:5] 1.062 0.186 0.364 0.335 0.383 ...
+##   Data: num [1:4142, 1:5] 0.2109 0.0632 0.4924 0.7234 0.6277 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##  $ Non_Alarmed_Obs:An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:7] 2 3 1 1 1 1 1 1 1 1 ...
+##   Data: num [1:4141, 1:7] 2 3 1 1 1 1 1 1 1 1 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##  NULL
-##  $ Alarms         :An 'xts' object of zero-width
+##  $ Alarms         :An 'xts' object on 2015-05-19 13:13:00/2015-05-19 13:13:00 containing:
+##   Data: num [1, 1:11] 1.81 -2.32 4.2 2.07 -2.11 ...
+##  - attr(*, "dimnames")=List of 2
+##   ..$ : NULL
+##   ..$ : chr [1:11] "x" "y" "z" "x.1" ...
+##   Indexed by objects of class: [POSIXct,POSIXt] TZ: 
+##   xts Attributes:  
+##  NULL
 ##  $ TrainingSpecs  :List of 3
 ##   ..$ 1:List of 6
-##   .. ..$ SPE_threshold   : Named num 4.61
+##   .. ..$ SPE_threshold   : Named num 4.71
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 59.6
+##   .. ..$ T2_threshold    : Named num 60.5
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.425 -0.378 0.439 0.434 -0.305 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.208 0 0 1.482
-##   .. ..$ muTrain         : Named num [1:6] 1.39 -2.09 2.99 1.38 -2.05 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.423 -0.382 0.437 0.431 -0.315 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.205 0 0 1.579
+##   .. ..$ muTrain         : Named num [1:6] 1.37 -2.1 2.95 1.36 -2.06 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.55 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.6 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 2:List of 6
-##   .. ..$ SPE_threshold   : Named num 1.4
+##   .. ..$ SPE_threshold   : Named num 1.14
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 74.6
+##   .. ..$ T2_threshold    : Named num 76.8
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4962 -0.0673 0.4888 -0.5234 -0.187 ...
-##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.284 0 0 0 0.732 ...
-##   .. ..$ muTrain         : Named num [1:6] 3.003 -0.564 -4.526 2.977 -0.589 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.496 -0.065 0.49 -0.523 -0.183 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.735 ...
+##   .. ..$ muTrain         : Named num [1:6] 2.979 -0.564 -4.508 2.952 -0.589 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.08 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.06 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 3:List of 6
-##   .. ..$ SPE_threshold   : Named num 6.51
+##   .. ..$ SPE_threshold   : Named num 7.2
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 83.4
+##   .. ..$ T2_threshold    : Named num 82.7
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.393 -0.452 -0.455 0.157 -0.464 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.274 0 0 0.507
-##   .. ..$ muTrain         : Named num [1:6] 0.527 0.273 1.434 0.567 0.259 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.393 -0.451 -0.455 0.16 -0.464 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.494
+##   .. ..$ muTrain         : Named num [1:6] 0.528 0.27 1.423 0.569 0.256 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.6 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.9 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
@@
 ##                     state         x         y         z       x.1
-## 2015-05-22 07:00:00     1 0.5894923 -1.693457 0.9793838 0.4122657
-## 2015-05-22 07:01:00     1 0.7076477 -1.693444 1.1569904 0.5894923
-## 2015-05-22 07:02:00     1 0.6065543 -1.510750 1.0816650 0.7076477
-## 2015-05-22 07:03:00     1 0.5964738 -1.404200 0.9984129 0.6065543
-## 2015-05-22 07:04:00     1 0.7359302 -1.492578 0.9049884 0.5964738
-## 2015-05-22 07:05:00     1 0.7665503 -1.482806 0.9188497 0.7359302
+## 2015-05-22 07:00:00     1 0.6844440 -1.565320 1.1324768 0.3534816
+## 2015-05-22 07:01:00     1 0.5454614 -1.369986 0.9184724 0.6844440
+## 2015-05-22 07:02:00     1 0.6468377 -1.593779 0.8900444 0.5454614
+## 2015-05-22 07:03:00     1 0.3543316 -1.361402 0.7855688 0.6468377
+## 2015-05-22 07:04:00     1 0.3831960 -1.455579 0.6319864 0.3543316
+## 2015-05-22 07:05:00     1 0.5734844 -1.406738 0.9210589 0.3831960
 ##                             y.1       z.1
-## 2015-05-22 07:00:00  0.1370214 0.4769939
-## 2015-05-22 07:01:00 -1.6934574 0.9793838
-## 2015-05-22 07:02:00 -1.6934436 1.1569904
-## 2015-05-22 07:03:00 -1.5107499 1.0816650
-## 2015-05-22 07:04:00 -1.4042005 0.9984129
-## 2015-05-22 07:05:00 -1.4925779 0.9049884
+## 2015-05-22 07:00:00  0.08705337 0.4466149
+## 2015-05-22 07:01:00 -1.56532037 1.1324768
+## 2015-05-22 07:02:00 -1.36998580 0.9184724
+## 2015-05-22 07:03:00 -1.59377911 0.8900444
+## 2015-05-22 07:04:00 -1.36140249 0.7855688
+## 2015-05-22 07:05:00 -1.45557880 0.6319864
 \end{verbatim}
@@
 ##                             x         y         z       x.1         y.1
-## 2015-05-22 07:00:00 0.5894923 -1.693457 0.9793838 0.4122657  0.1370214
-## 2015-05-22 07:01:00 0.7076477 -1.693444 1.1569904 0.5894923 -1.6934574
-## 2015-05-22 07:02:00 0.6065543 -1.510750 1.0816650 0.7076477 -1.6934436
-## 2015-05-22 07:03:00 0.5964738 -1.404200 0.9984129 0.6065543 -1.5107499
-## 2015-05-22 07:04:00 0.7359302 -1.492578 0.9049884 0.5964738 -1.4042005
-## 2015-05-22 07:05:00 0.7665503 -1.482806 0.9188497 0.7359302 -1.4925779
+## 2015-05-22 07:00:00 0.6844440 -1.565320 1.1324768 0.3534816  0.08705337
+## 2015-05-22 07:01:00 0.5454614 -1.369986 0.9184724 0.6844440 -1.56532037
+## 2015-05-22 07:02:00 0.6468377 -1.593779 0.8900444 0.5454614 -1.36998580
+## 2015-05-22 07:03:00 0.3543316 -1.361402 0.7855688 0.6468377 -1.59377911
+## 2015-05-22 07:04:00 0.3831960 -1.455579 0.6319864 0.3543316 -1.36140249
+## 2015-05-22 07:05:00 0.5734844 -1.406738 0.9210589 0.3831960 -1.45557880
 ##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
-## 2015-05-22 07:00:00 0.4769939 1.23315168        0 28.293817       0    NA
-## 2015-05-22 07:01:00 0.9793838 0.06691071        0  3.842885       0    NA
-## 2015-05-22 07:02:00 1.1569904 0.43929620        0  4.405378       0    NA
-## 2015-05-22 07:03:00 1.0816650 0.86684372        0  5.023986       0    NA
-## 2015-05-22 07:04:00 0.9984129 0.45658085        0  4.864228       0    NA
-## 2015-05-22 07:05:00 0.9049884 0.74949850        0  4.396364       0    NA
+## 2015-05-22 07:00:00 0.4466149 0.2948716        0 28.028452       0    NA
+## 2015-05-22 07:01:00 1.1324768 0.9816014        0  5.025385       0    NA
+## 2015-05-22 07:02:00 0.9184724 0.0316290        0  4.773963       0    NA
+## 2015-05-22 07:03:00 0.8900444 0.8505646        0  6.333569       0    NA
+## 2015-05-22 07:04:00 0.7855688 0.2234181        0  6.613971       0    NA
+## 2015-05-22 07:05:00 0.6319864 0.4523686        0  5.922610       0    NA
 \end{verbatim}

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Added the knitr chunk for downloading the package. I had it commented out previously.

@@
 This is the accompanying package to the research published by \cite{kazor_comparison_2016} and the previous chapter.
-The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.
+The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the statistical process monitoring component.
 This package can be downloaded from GitHub by running the following:
-%   <<r packLoad_GitHub, eval = FALSE>>=
-%   devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
-% @
+<<r packLoad_GitHub, eval = FALSE>>=
+ devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
+@
 \noindent where you create the value of ``tokenHere'' by generating a personal access token (PAT) at \url{https://github.com/settings/tokens} and copying the quoted string to this argument.

### 2017-07-12 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Added the knitr chunk for downloading the package. I had it commented out previously.

@@
 This is the accompanying package to the research published by \cite{kazor_comparison_2016} and the previous chapter.
-The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.
+The \texttt{mvMonitoring} package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the statistical process monitoring component.
 This package can be downloaded from GitHub by running the following:
-%   <<r packLoad_GitHub, eval = FALSE>>=
-%   devtools::install_github("gabrielodom/mvMonitoring", auth_token = "tokenHere")
-% @
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+ \hlstd{devtools}\hlopt{::}\hlkwd{install_github}\hlstd{(}\hlstr{"gabrielodom/mvMonitoring"}\hlstd{,} \hlkwc{auth_token} \hlstd{=} \hlstr{"tokenHere"}\hlstd{)}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
 \noindent where you create the value of ``tokenHere'' by generating a personal access token (PAT) at \url{https://github.com/settings/tokens} and copying the quoted string to this argument.
@@
 ##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:5] 0.2109 0.0632 0.4924 0.7234 0.6277 ...
+##   Data: num [1:4142, 1:5] 0.042 0.492 1.208 1.139 0.742 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##  $ Non_Alarmed_Obs:An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4141, 1:7] 2 3 1 1 1 1 1 1 1 1 ...
+##   Data: num [1:4142, 1:7] 2 3 1 1 1 1 1 1 1 1 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##  NULL
-##  $ Alarms         :An 'xts' object on 2015-05-19 13:13:00/2015-05-19 13:13:00 containing:
-##   Data: num [1, 1:11] 1.81 -2.32 4.2 2.07 -2.11 ...
-##  - attr(*, "dimnames")=List of 2
-##   ..$ : NULL
-##   ..$ : chr [1:11] "x" "y" "z" "x.1" ...
-##   Indexed by objects of class: [POSIXct,POSIXt] TZ: 
-##   xts Attributes:  
-##  NULL
+##  $ Alarms         :An 'xts' object of zero-width
 ##  $ TrainingSpecs  :List of 3
 ##   ..$ 1:List of 6
-##   .. ..$ SPE_threshold   : Named num 4.71
+##   .. ..$ SPE_threshold   : Named num 4.39
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 60.5
+##   .. ..$ T2_threshold    : Named num 61.4
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.423 -0.382 0.437 0.431 -0.315 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.205 0 0 1.579
-##   .. ..$ muTrain         : Named num [1:6] 1.37 -2.1 2.95 1.36 -2.06 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.424 -0.381 0.437 0.432 -0.313 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.206 0 0 1.565
+##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.09 2.97 1.37 -2.05 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.6 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.58 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 2:List of 6
-##   .. ..$ SPE_threshold   : Named num 1.14
+##   .. ..$ SPE_threshold   : Named num 1.79
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 76.8
+##   .. ..$ T2_threshold    : Named num 76.6
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.496 -0.065 0.49 -0.523 -0.183 ...
-##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.735 ...
-##   .. ..$ muTrain         : Named num [1:6] 2.979 -0.564 -4.508 2.952 -0.589 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4944 -0.0882 0.4873 -0.5234 -0.1921 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.727 ...
+##   .. ..$ muTrain         : Named num [1:6] 3.019 -0.561 -4.533 2.991 -0.586 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.06 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.07 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 3:List of 6
-##   .. ..$ SPE_threshold   : Named num 7.2
+##   .. ..$ SPE_threshold   : Named num 5.58
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 82.7
+##   .. ..$ T2_threshold    : Named num 80.1
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.393 -0.451 -0.455 0.16 -0.464 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.494
-##   .. ..$ muTrain         : Named num [1:6] 0.528 0.27 1.423 0.569 0.256 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.394 0.448 0.452 -0.167 0.464 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.277 0 0 0.498
+##   .. ..$ muTrain         : Named num [1:6] 0.528 0.273 1.441 0.57 0.259 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.9 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 17.2 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
@@
 ##                     state         x         y         z       x.1
-## 2015-05-22 07:00:00     1 0.6844440 -1.565320 1.1324768 0.3534816
-## 2015-05-22 07:01:00     1 0.5454614 -1.369986 0.9184724 0.6844440
-## 2015-05-22 07:02:00     1 0.6468377 -1.593779 0.8900444 0.5454614
-## 2015-05-22 07:03:00     1 0.3543316 -1.361402 0.7855688 0.6468377
-## 2015-05-22 07:04:00     1 0.3831960 -1.455579 0.6319864 0.3543316
-## 2015-05-22 07:05:00     1 0.5734844 -1.406738 0.9210589 0.3831960
+## 2015-05-22 07:00:00     1 0.6516822 -1.487152 0.8868843 0.3772442
+## 2015-05-22 07:01:00     1 0.6959653 -1.524802 0.7687056 0.6516822
+## 2015-05-22 07:02:00     1 0.4693409 -1.202725 0.7970705 0.6959653
+## 2015-05-22 07:03:00     1 0.5744935 -1.239971 0.6663379 0.4693409
+## 2015-05-22 07:04:00     1 0.5872442 -1.238700 0.8654388 0.5744935
+## 2015-05-22 07:05:00     1 0.6820071 -1.452199 0.9107379 0.5872442
 ##                            y.1       z.1
-## 2015-05-22 07:00:00  0.08705337 0.4466149
-## 2015-05-22 07:01:00 -1.56532037 1.1324768
-## 2015-05-22 07:02:00 -1.36998580 0.9184724
-## 2015-05-22 07:03:00 -1.59377911 0.8900444
-## 2015-05-22 07:04:00 -1.36140249 0.7855688
-## 2015-05-22 07:05:00 -1.45557880 0.6319864
+## 2015-05-22 07:00:00  0.1208201 0.5190793
+## 2015-05-22 07:01:00 -1.4871516 0.8868843
+## 2015-05-22 07:02:00 -1.5248019 0.7687056
+## 2015-05-22 07:03:00 -1.2027252 0.7970705
+## 2015-05-22 07:04:00 -1.2399706 0.6663379
+## 2015-05-22 07:05:00 -1.2386996 0.8654388
 \end{verbatim}
@@
 ##                             x         y         z       x.1        y.1
-## 2015-05-22 07:00:00 0.6844440 -1.565320 1.1324768 0.3534816  0.08705337
-## 2015-05-22 07:01:00 0.5454614 -1.369986 0.9184724 0.6844440 -1.56532037
-## 2015-05-22 07:02:00 0.6468377 -1.593779 0.8900444 0.5454614 -1.36998580
-## 2015-05-22 07:03:00 0.3543316 -1.361402 0.7855688 0.6468377 -1.59377911
-## 2015-05-22 07:04:00 0.3831960 -1.455579 0.6319864 0.3543316 -1.36140249
-## 2015-05-22 07:05:00 0.5734844 -1.406738 0.9210589 0.3831960 -1.45557880
+## 2015-05-22 07:00:00 0.6516822 -1.487152 0.8868843 0.3772442  0.1208201
+## 2015-05-22 07:01:00 0.6959653 -1.524802 0.7687056 0.6516822 -1.4871516
+## 2015-05-22 07:02:00 0.4693409 -1.202725 0.7970705 0.6959653 -1.5248019
+## 2015-05-22 07:03:00 0.5744935 -1.239971 0.6663379 0.4693409 -1.2027252
+## 2015-05-22 07:04:00 0.5872442 -1.238700 0.8654388 0.5744935 -1.2399706
+## 2015-05-22 07:05:00 0.6820071 -1.452199 0.9107379 0.5872442 -1.2386996
 ##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
-## 2015-05-22 07:00:00 0.4466149 0.2948716        0 28.028452       0    NA
-## 2015-05-22 07:01:00 1.1324768 0.9816014        0  5.025385       0    NA
-## 2015-05-22 07:02:00 0.9184724 0.0316290        0  4.773963       0    NA
-## 2015-05-22 07:03:00 0.8900444 0.8505646        0  6.333569       0    NA
-## 2015-05-22 07:04:00 0.7855688 0.2234181        0  6.613971       0    NA
-## 2015-05-22 07:05:00 0.6319864 0.4523686        0  5.922610       0    NA
+## 2015-05-22 07:00:00 0.5190793 0.5746873        0 28.479963       0    NA
+## 2015-05-22 07:01:00 0.8868843 0.3065558        0  4.594196       0    NA
+## 2015-05-22 07:02:00 0.7687056 2.2496108        0  6.313058       0    NA
+## 2015-05-22 07:03:00 0.7970705 1.4836139        0  7.071992       0    NA
+## 2015-05-22 07:04:00 0.6663379 1.6703320        0  6.605812       0    NA
+## 2015-05-22 07:05:00 0.8654388 0.4398132        0  5.638591       0    NA
 \end{verbatim}

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Edited section 5.2

@@
 \subsection{Why use \texttt{mvMonitoring}?}
-The \texttt{mvMonitoring} package can be used to detect outliers in a correlated multivariate process with non-linear, non-stationary, or autocorrelated feature behavior.
+The \texttt{mvMonitoring} package can be used to detect outliers in a correlated, non-Gaussian multivariate process with non-linear, non-stationary, or autocorrelated feature behavior.
 These process outliers are often indicative of system fault.
-The common  and naive approach to multivariate process monitoring is to use expert opinion to identify a few important features to monitor visually, and raise an alarm if these features travel outside pre-defined normal operating boundaries.
+The naive (and unfortunately common) approach to multivariate process monitoring is to use expert opinion to identify a few important features to monitor visually, and raise an alarm if these features travel outside pre-defined normal operating boundaries.
 
@@
 In the literature review of the motivating papers, the authors cite how this approach has benefited the science of process monitoring as a whole.
-Unfortunately, this approach has its own shortcomings -- namely, monitoring a multivariate process in its original feature space can lead to exorbitant computational costs.
-To this end, \emph{principal components analysis} (PCA) and its many modifications have been employed to reduce the computation necessary to monitor a multivariate process as a whole.
+Unfortunately, this approach has its own shortcomings.
+One such complication is that monitoring a multivariate process in its original feature space can lead to exorbitant computational costs.
+Additionally, correlated multivariate process over many features may be noisy and often retain redundant information.
+To combat these issues, \emph{principal components analysis} (PCA) and its many modifications have been employed to assist in monitoring multivariate processes as a whole.
 This package is an implementation of one such PCA modification.
@@
 \subsection{Multi- or Single-State AD-PCA}
-AD-PCA is \emph{adaptive-dynamic} PCA, which accounts for non-linearity, non-stationarity, and autocorrelation in the multivariate process, and this modification is thoroughly discussed in \cite{kazor_comparison_2016} as well as in the previous chapter.
-As an additional component to this model, we now consider that the process to monitor may have multiple known system states.
-Thus, \emph{multi-state} monitoring is a modification to PCA which accounts for multiple process states and models them separately.
+\emph{Adaptive-Dynamic} PCA (AD-PCA), thoroughly discussed in \cite{kazor_comparison_2016} as well as in the previous chapter, accounts for non-linearity, non-stationarity, and autocorrelation in non-Gaussian multivariate processes.
+As an additional layer of complexity within this model, consider such a process with multiple known system states.
+\emph{Multi-State} monitoring is thus a modification to PCA which accounts for multiple process states and models them separately.
 States can be any mutually exclusive blocking factor, and states do not necessarily follow a strict order.
-Then, Multi-State AD-PCA (MSAD-PCA) allows process engineers to account for a few very different process states.
+Then, Multi-State AD-PCA (MSAD-PCA) allows process engineers to account for distinct process states.
 Specifically, this modification should be used when features under different process states have different means, correlations, variances, or some combination of these three.

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Edited section 5.2

@@
 ##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:5] 0.042 0.492 1.208 1.139 0.742 ...
+##   Data: num [1:4142, 1:5] 2.084 0.268 0.582 0.694 0.956 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##   ..$ 1:List of 6
-##   .. ..$ SPE_threshold   : Named num 4.39
+##   .. ..$ SPE_threshold   : Named num 4.66
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 61.4
+##   .. ..$ T2_threshold    : Named num 58.1
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.424 -0.381 0.437 0.432 -0.313 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.206 0 0 1.565
-##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.09 2.97 1.37 -2.05 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.421 -0.386 0.434 0.429 -0.325 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.202 0 0 1.685
+##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.08 2.95 1.36 -2.04 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.58 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.47 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 2:List of 6
-##   .. ..$ SPE_threshold   : Named num 1.79
+##   .. ..$ SPE_threshold   : Named num 1.06
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 76.6
+##   .. ..$ T2_threshold    : Named num 77.4
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4944 -0.0882 0.4873 -0.5234 -0.1921 ...
-##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.727 ...
-##   .. ..$ muTrain         : Named num [1:6] 3.019 -0.561 -4.533 2.991 -0.586 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.50267 -0.00244 0.49616 -0.52609 -0.14826 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.706 ...
+##   .. ..$ muTrain         : Named num [1:6] 2.958 -0.564 -4.481 2.931 -0.59 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.07 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.04 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 3:List of 6
-##   .. ..$ SPE_threshold   : Named num 5.58
+##   .. ..$ SPE_threshold   : Named num 6.33
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
@@
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.394 0.448 0.452 -0.167 0.464 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.277 0 0 0.498
-##   .. ..$ muTrain         : Named num [1:6] 0.528 0.273 1.441 0.57 0.259 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.403 -0.456 -0.459 0.135 -0.458 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.273 0 0 0.505
+##   .. ..$ muTrain         : Named num [1:6] 0.523 0.269 1.409 0.565 0.255 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 17.2 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 15.4 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
@@
 ##                     state         x         y         z       x.1
-## 2015-05-22 07:00:00     1 0.6516822 -1.487152 0.8868843 0.3772442
-## 2015-05-22 07:01:00     1 0.6959653 -1.524802 0.7687056 0.6516822
-## 2015-05-22 07:02:00     1 0.4693409 -1.202725 0.7970705 0.6959653
-## 2015-05-22 07:03:00     1 0.5744935 -1.239971 0.6663379 0.4693409
-## 2015-05-22 07:04:00     1 0.5872442 -1.238700 0.8654388 0.5744935
-## 2015-05-22 07:05:00     1 0.6820071 -1.452199 0.9107379 0.5872442
+## 2015-05-22 07:00:00     1 0.6030535 -1.566528 0.8662376 0.3665282
+## 2015-05-22 07:01:00     1 0.4416746 -1.406672 0.3811997 0.6030535
+## 2015-05-22 07:02:00     1 0.5408433 -1.304789 0.4314055 0.4416746
+## 2015-05-22 07:03:00     1 0.5082937 -1.391546 0.8054482 0.5408433
+## 2015-05-22 07:04:00     1 0.4508361 -1.312723 0.8291703 0.5082937
+## 2015-05-22 07:05:00     1 0.7068563 -1.465259 0.7728310 0.4508361
 ##                             y.1       z.1
-## 2015-05-22 07:00:00  0.1208201 0.5190793
-## 2015-05-22 07:01:00 -1.4871516 0.8868843
-## 2015-05-22 07:02:00 -1.5248019 0.7687056
-## 2015-05-22 07:03:00 -1.2027252 0.7970705
-## 2015-05-22 07:04:00 -1.2399706 0.6663379
-## 2015-05-22 07:05:00 -1.2386996 0.8654388
+## 2015-05-22 07:00:00  0.08751379 0.3336879
+## 2015-05-22 07:01:00 -1.56652763 0.8662376
+## 2015-05-22 07:02:00 -1.40667237 0.3811997
+## 2015-05-22 07:03:00 -1.30478897 0.4314055
+## 2015-05-22 07:04:00 -1.39154587 0.8054482
+## 2015-05-22 07:05:00 -1.31272320 0.8291703
 \end{verbatim}
@@
 ##                             x         y         z       x.1         y.1
-## 2015-05-22 07:00:00 0.6516822 -1.487152 0.8868843 0.3772442  0.1208201
-## 2015-05-22 07:01:00 0.6959653 -1.524802 0.7687056 0.6516822 -1.4871516
-## 2015-05-22 07:02:00 0.4693409 -1.202725 0.7970705 0.6959653 -1.5248019
-## 2015-05-22 07:03:00 0.5744935 -1.239971 0.6663379 0.4693409 -1.2027252
-## 2015-05-22 07:04:00 0.5872442 -1.238700 0.8654388 0.5744935 -1.2399706
-## 2015-05-22 07:05:00 0.6820071 -1.452199 0.9107379 0.5872442 -1.2386996
+## 2015-05-22 07:00:00 0.6030535 -1.566528 0.8662376 0.3665282  0.08751379
+## 2015-05-22 07:01:00 0.4416746 -1.406672 0.3811997 0.6030535 -1.56652763
+## 2015-05-22 07:02:00 0.5408433 -1.304789 0.4314055 0.4416746 -1.40667237
+## 2015-05-22 07:03:00 0.5082937 -1.391546 0.8054482 0.5408433 -1.30478897
+## 2015-05-22 07:04:00 0.4508361 -1.312723 0.8291703 0.5082937 -1.39154587
+## 2015-05-22 07:05:00 0.7068563 -1.465259 0.7728310 0.4508361 -1.31272320
 ##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
-## 2015-05-22 07:00:00 0.5190793 0.5746873        0 28.479963       0    NA
-## 2015-05-22 07:01:00 0.8868843 0.3065558        0  4.594196       0    NA
-## 2015-05-22 07:02:00 0.7687056 2.2496108        0  6.313058       0    NA
-## 2015-05-22 07:03:00 0.7970705 1.4836139        0  7.071992       0    NA
-## 2015-05-22 07:04:00 0.6663379 1.6703320        0  6.605812       0    NA
-## 2015-05-22 07:05:00 0.8654388 0.4398132        0  5.638591       0    NA
+## 2015-05-22 07:00:00 0.3336879 0.7953977        0 24.566074       0    NA
+## 2015-05-22 07:01:00 0.8662376 0.3442694        0  5.731867       0    NA
+## 2015-05-22 07:02:00 0.3811997 0.4382832        0  6.232419       0    NA
+## 2015-05-22 07:03:00 0.4314055 0.2334754        0  5.558003       0    NA
+## 2015-05-22 07:04:00 0.8054482 0.5248950        0  5.476091       0    NA
+## 2015-05-22 07:05:00 0.8291703 0.1880696        0  4.896475       0    NA
 \end{verbatim}

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Edited section 5.3

@@
 These process outliers are often indicative of system fault.
-The naive (and unfortunately common) approach to multivariate process monitoring is to use expert opinion to identify a few important features to monitor visually, and raise an alarm if these features travel outside pre-defined normal operating boundaries.
+The naive (but unfortunately common) approach to multivariate process monitoring is to use expert opinion to identify a few important features to monitor visually, and raise an alarm if these features travel outside pre-defined normal operating boundaries.
 
@@
 \section{Simulating Data with \texttt{mspProcessData}} \label{sec:D_DataGen}
-This function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations.
+The \texttt{mspProcessData} function generates three-dimensional multi-state or single-state non-linear, non-stationary, and autocorrelated process observations.
 We follow the seminal work of \cite{dong_batch_1996} for generation of the foundational stationary and independent features.
@@
 \subsection{Latent Feature Creation}
-So that the simulated features have non-zero correlations, Dong and McAvoy created their three features all as polynomial functions of a single latent variable $t(s)$, where $s = 1, \ldots, \omega$ is the observational index of the process.
+So that the simulated features have non-zero correlations, Dong and McAvoy created their three features all as polynomial functions of a single latent variable $t_s$, where $s = 1, \ldots, \omega$ is the observational index of the process.
 
@@
 \[
-  \varepsilon_1 \sim \mathcal{N}\left(\frac{1}{2}(a + b)(1 - \phi), \frac{b - a}{12} (1 - \phi ^ 2)\right),
+  \varepsilon_1 \sim \mathcal{N}\left(\frac{1}{2}(a + b)(1 - \varphi), \frac{b - a}{12} (1 - \varphi ^ 2)\right),
 \]
@@
 \]
-where $\varepsilon$ is as defined in the previous expression and the autocorrelation component $\phi = 0.75$.
-The mean and variance multipliers are the mean and variance of a random variable from the $\mathcal{U}_{[a,b]}$ distribution.
+where $\varepsilon$ is a random innovation drawn from the Normal distribution defined in the previous expression, and the autocorrelation component $\varphi = 0.75$.
+The mean and variance multipliers are the mean and variance of a random variable from the $\text{uniform}_{[a,b]}$ distribution.
 
 \subsubsection{The Non-Linear Latent Process}
-This $t$ vector will be sinusoidal with period $\omega = 7 * 24 * 60$ (signifying a weekly period in  minute-level observations). We then synthesize a $t$ with
+This $t$ vector will be sinusoidal with period $\omega = 7 * 24 * 60$ (signifying a weekly period in  minute-level observations). We then synthesize a $t$ by taking
 \[
@@
 \]
-and scale $t^*$ to
+and then scaling $t^*$ to
 \[
@@
 First \texttt{mspProcessData} simulates three features, with each feature operating under $k$ different states.
-Let $\langle x_k(t), y_k(t), z_k(t) \rangle$ be the notation for State $k$.
-These are the three features under State 1 (normal operating conditions, or \emph{NOC}) as three functions of $t$:
+Let $\langle x_k(t_s), y_k(t_s), z_k(t_s) \rangle$ be the process evaluated at $t_s$ within State $k$.
+These are the three features under State 1 (in control, or \emph{IC}) as three functions of $t$:
 \begin{align}
-\textbf{x}(\textbf{t}) &\equiv \textbf{t} + \boldsymbol\varepsilon_1, \\
-\textbf{y}(\textbf{t}) &\equiv \textbf{t} ^ 2 - 3 * \textbf{t} + \boldsymbol\varepsilon_2, \\
-\textbf{z}(\textbf{t}) &\equiv -\textbf{t} ^ 3 + 3 * \textbf{t} ^ 2 + \boldsymbol\varepsilon_3,
+x(\textbf{t}) &\equiv \textbf{t} + \boldsymbol\varepsilon_1, \\
+y(\textbf{t}) &\equiv \textbf{t} ^ 2 - 3 * \textbf{t} + \boldsymbol\varepsilon_2, \\
+z(\textbf{t}) &\equiv -\textbf{t} ^ 3 + 3 * \textbf{t} ^ 2 + \boldsymbol\varepsilon_3,
 \end{align}
-where $\varepsilon_i \sim N(0, 0.01)$. The \texttt{mspProcessData} function calls the internal \texttt{processNOCdata} function to generate single-state observations under NOC.
+where $\varepsilon_i \sim N(0, 0.01),\ 1 = 1, 2, 3$. The \texttt{mspProcessData} function calls the internal \texttt{processNOCdata} function to generate IC single-state observations.
 
@@
 The third state is yaw, pitch, and roll rotated by (90, 0, -30) degrees, and the scales are multiplied by (0.25, 0.1, 0.75).
+That is,
 \begin{enumerate}
@@
 Faults can be introduced to single- or multi-state data via the \texttt{mspProcessData} function.
-The default fault start index is 8500, or roughly 84\% through the 10,080 observation cycle.
+The default fault start index is 8500, or roughly 84\% through the cycle of 10,080 observations.
 These faults are added through the internal \texttt{faultSwitch} function.
@@
 %
-\item Fault 1C is a positive shift to the $x$ and $z$ features in State 3 only and *after* state rotation: $x^*(t_s) = x(t_s) + 2,\ z^*(t_s) = z(t_s) + 2,\ s \ge 8500$.
+\item Fault 1C is a positive shift to the $x$ and $z$ features in State 3 only and \emph{after} state rotation: $x^*(t_s) = x(t_s) + 2,\ z^*(t_s) = z(t_s) + 2,\ s \ge 8500$.
 %
@@
 The \texttt{mspProcessData} function can generate weeks' worth of non-linear, non-stationary, autocorrelated, multi-state, multivariate process data useful to test new process monitoring techniques.
-Users can generate observations under NOC to measure false alarm rates, or induce one of nine pre-built faults to test detection time and consistency with repeated Monte Carlo sampling.
+Users can generate IC observations to measure false alarm rates, or induce one of nine pre-built faults to test detection time and consistency with repeated Monte Carlo sampling.
 We expect this function will generate interesting data useful enough to compare new and improved process monitoring techniques with existing methods.
+A detailed description of this function's inputs and outputs are shown in Section \ref{sec:D_Workflow}.
 

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Edited section 5.3

@@
 ##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:5] 2.084 0.268 0.582 0.694 0.956 ...
+##   Data: num [1:4142, 1:5] 0.2407 0.0621 0.2815 0.1616 0.3386 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##   ..$ 1:List of 6
-##   .. ..$ SPE_threshold   : Named num 4.66
+##   .. ..$ SPE_threshold   : Named num 3.59
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 58.1
+##   .. ..$ T2_threshold    : Named num 61.6
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.421 -0.386 0.434 0.429 -0.325 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.202 0 0 1.685
-##   .. ..$ muTrain         : Named num [1:6] 1.38 -2.08 2.95 1.36 -2.04 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.421 -0.389 0.433 0.43 -0.32 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.202 0 0 1.646
+##   .. ..$ muTrain         : Named num [1:6] 1.36 -2.09 2.93 1.35 -2.05 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.47 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.58 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 2:List of 6
-##   .. ..$ SPE_threshold   : Named num 1.06
+##   .. ..$ SPE_threshold   : Named num 1.35
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 77.4
+##   .. ..$ T2_threshold    : Named num 77
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.50267 -0.00244 0.49616 -0.52609 -0.14826 ...
-##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.706 ...
-##   .. ..$ muTrain         : Named num [1:6] 2.958 -0.564 -4.481 2.931 -0.59 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:3] 0.5025 -0.0192 -0.4984 0.5267 0.1392 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.686 ...
+##   .. ..$ muTrain         : Named num [1:6] 2.946 -0.565 -4.465 2.92 -0.59 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
@@
 ##   ..$ 3:List of 6
-##   .. ..$ SPE_threshold   : Named num 6.33
+##   .. ..$ SPE_threshold   : Named num 6.42
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 80.1
+##   .. ..$ T2_threshold    : Named num 85.4
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.403 -0.456 -0.459 0.135 -0.458 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.273 0 0 0.505
-##   .. ..$ muTrain         : Named num [1:6] 0.523 0.269 1.409 0.565 0.255 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.399 -0.453 -0.454 0.152 -0.462 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.275 0 0 0.501
+##   .. ..$ muTrain         : Named num [1:6] 0.526 0.268 1.411 0.566 0.254 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 15.4 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.8 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
@@
 ##                     state         x         y         z       x.1
-## 2015-05-22 07:00:00     1 0.6030535 -1.566528 0.8662376 0.3665282
-## 2015-05-22 07:01:00     1 0.4416746 -1.406672 0.3811997 0.6030535
-## 2015-05-22 07:02:00     1 0.5408433 -1.304789 0.4314055 0.4416746
-## 2015-05-22 07:03:00     1 0.5082937 -1.391546 0.8054482 0.5408433
-## 2015-05-22 07:04:00     1 0.4508361 -1.312723 0.8291703 0.5082937
-## 2015-05-22 07:05:00     1 0.7068563 -1.465259 0.7728310 0.4508361
+## 2015-05-22 07:00:00     1 0.4542266 -1.188745 0.6005185 0.3809131
+## 2015-05-22 07:01:00     1 0.4889364 -1.416970 0.5952562 0.4542266
+## 2015-05-22 07:02:00     1 0.6942253 -1.436590 0.9416095 0.4889364
+## 2015-05-22 07:03:00     1 0.5357452 -1.563710 0.9727830 0.6942253
+## 2015-05-22 07:04:00     1 0.6569141 -1.504261 0.9597280 0.5357452
+## 2015-05-22 07:05:00     1 0.5957465 -1.298968 0.6082284 0.6569141
 ##                             y.1       z.1
-## 2015-05-22 07:00:00  0.08751379 0.3336879
-## 2015-05-22 07:01:00 -1.56652763 0.8662376
-## 2015-05-22 07:02:00 -1.40667237 0.3811997
-## 2015-05-22 07:03:00 -1.30478897 0.4314055
-## 2015-05-22 07:04:00 -1.39154587 0.8054482
-## 2015-05-22 07:05:00 -1.31272320 0.8291703
+## 2015-05-22 07:00:00  0.09361165 0.3698668
+## 2015-05-22 07:01:00 -1.18874504 0.6005185
+## 2015-05-22 07:02:00 -1.41696998 0.5952562
+## 2015-05-22 07:03:00 -1.43659004 0.9416095
+## 2015-05-22 07:04:00 -1.56371006 0.9727830
+## 2015-05-22 07:05:00 -1.50426070 0.9597280
 \end{verbatim}
@@
 ##                             x         y         z       x.1         y.1
-## 2015-05-22 07:00:00 0.6030535 -1.566528 0.8662376 0.3665282  0.08751379
-## 2015-05-22 07:01:00 0.4416746 -1.406672 0.3811997 0.6030535 -1.56652763
-## 2015-05-22 07:02:00 0.5408433 -1.304789 0.4314055 0.4416746 -1.40667237
-## 2015-05-22 07:03:00 0.5082937 -1.391546 0.8054482 0.5408433 -1.30478897
-## 2015-05-22 07:04:00 0.4508361 -1.312723 0.8291703 0.5082937 -1.39154587
-## 2015-05-22 07:05:00 0.7068563 -1.465259 0.7728310 0.4508361 -1.31272320
+## 2015-05-22 07:00:00 0.4542266 -1.188745 0.6005185 0.3809131  0.09361165
+## 2015-05-22 07:01:00 0.4889364 -1.416970 0.5952562 0.4542266 -1.18874504
+## 2015-05-22 07:02:00 0.6942253 -1.436590 0.9416095 0.4889364 -1.41696998
+## 2015-05-22 07:03:00 0.5357452 -1.563710 0.9727830 0.6942253 -1.43659004
+## 2015-05-22 07:04:00 0.6569141 -1.504261 0.9597280 0.5357452 -1.56371006
+## 2015-05-22 07:05:00 0.5957465 -1.298968 0.6082284 0.6569141 -1.50426070
 ##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
-## 2015-05-22 07:00:00 0.3336879 0.7953977        0 24.566074       0    NA
-## 2015-05-22 07:01:00 0.8662376 0.3442694        0  5.731867       0    NA
-## 2015-05-22 07:02:00 0.3811997 0.4382832        0  6.232419       0    NA
-## 2015-05-22 07:03:00 0.4314055 0.2334754        0  5.558003       0    NA
-## 2015-05-22 07:04:00 0.8054482 0.5248950        0  5.476091       0    NA
-## 2015-05-22 07:05:00 0.8291703 0.1880696        0  4.896475       0    NA
+## 2015-05-22 07:00:00 0.3698668 2.0491906        0 25.423541       0    NA
+## 2015-05-22 07:01:00 0.6005185 0.1819048        0  6.563964       0    NA
+## 2015-05-22 07:02:00 0.5952562 0.3945702        0  5.086740       0    NA
+## 2015-05-22 07:03:00 0.9416095 0.1778764        0  4.277330       0    NA
+## 2015-05-22 07:04:00 0.9727830 0.1784149        0  4.399492       0    NA
+## 2015-05-22 07:05:00 0.9597280 1.1749990        0  5.393532       0    NA
 \end{verbatim}

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Edited section 5.4

@@
 
-The \texttt{mspTrain} function will generate projection matrices and test statistic thresholds from test data matrices.
+The \texttt{mspTrain} function will generate projection matrices and test statistic thresholds from training data matrices. It requires data matrices to be in the \texttt{xts} matrix format.
 
@@
 An \texttt{xts} data matrix is first and foremost a matrix, \emph{not} a data frame.
-For users very familiar with data frame manipulation (with \texttt{dplyr} for instance), the slight but profound differences between manipulating matrices and data frames become quickly apparent.
-Because of the class requirements for matrices, \emph{all} features must be integer or double objects.
-The \texttt{mspTrain} function cannot train on character information.
+For users very familiar with data frame manipulation (with \texttt{dplyr} for instance), the slight but profound differences between manipulating matrices and data frames quickly become apparent.
+Because of the class requirements for matrices, \emph{all} features must be integer or double vectors.
+The \texttt{mspTrain} function cannot train on non-numeric information.
 
-The \texttt{xts} object class stands for \emph{extendible time series} and comes from the package \texttt{xts}, which is itself built on the package \texttt{zoo}.
-The date and time information (necessarily as \texttt{POSIX} objects) are stored as the row indices of \texttt{xts} matrices.
+The \texttt{xts} object class stands for \emph{extendible time series} and comes from the package \texttt{xts}, which is built on the package \texttt{zoo}.
+The date and time information for the multivariate stochastic process (necessarily as \texttt{POSIX} objects) are stored as the row indices of \texttt{xts} matrices.
 We recommend the package \texttt{lubridate} for manipulating \texttt{POSIX} objects.
 
-\subsection{The Class Vector}
-When implementing single-state AD-PCA, this class vector simply needs to be a numeric column of the same value -- for instance, 1.
-However, for MSAD-PCA, the class vector should be an integer vector of class membership.
-The \texttt{mspTrain} function will split the observations by the class label, apply single-state AD-PCA to each class, then return the class-specific projection matrices and thresholds.
-Because of this split-apply-combine strategy, users must ensure that one or more classes are not too ``rare'' -- that is, the class-specific sample size should be sufficiently large to allow for stable covariance matrix inversion.
-For $p$ features (including lags), covariance inversion requires a class sample size greater than $p ^ 2 / 2$.
-Because of this, pay close attention to model parsimony -- do not block the observations on a factor unless the factor significantly affects the observations' mean vector or covariance matrix.
+\subsection{The State Vector}
+The state membership (or \emph{class}) vector of the data matrix is the column of integer values corresponding to the generation state of the observation.
+When implementing single-state AD-PCA, this class vector will simply be a numeric column of the same value -- for instance, 1.
+However, for MSAD-PCA, the class vector indicates from which state each observation has been drawn.
+
+The \texttt{mspTrain} function will split the observations by the class vector, apply single-state AD-PCA to each class, then return the class-specific projection matrices and thresholds.
+Because of this split-apply-combine strategy, users must ensure that one or more classes are not too ``rare'' -- that is, the class sample sizes should be sufficiently large to allow for stable covariance matrix inversion.
+For $p$ features (including lags), stable covariance inversion requires a class sample size near $p ^ 2 / 2$ at minimum.
+Because of this, attention must be given to model parsimony -- we recommend against blocking observations on a factor unless that factor has sufficent observations and significantly affects the observations' mean vector or covariance matrix.
 
 \subsection{Adaptive and Dynamic Modeling}
-Because of the non-linear, non-stationary, and autocorrelated nature of some process monitoring applications, the \texttt{mspTrain} function allows users to include lags of all feature variables and also to update the training window over time.
-Including lags of the features in the data matrix can significantly reduce the negative effects of autocorrelation.
-Re-estimating the projection matrix and test statistic thresholds at pre-specified time intervals reduces the negative effects of non-linearity and non-stationarity in the observations.
-
-The idea is to divide a non-linear and non-stationary process along some boundaries (every day, for instance), and then the process becomes locally linear and stationary within the window.
-As time progresses, the oldest observations are ``forgotten'' and the newest observations are ``learned'', which causes the projection and NOC thresholds to update over time.
+Because of the non-linear, non-stationary, and autocorrelated nature of some process monitoring applications, the \texttt{mspTrain} function allows users to include lags of all feature variables.
+Including lags of the features in the data matrix (dynamic) can significantly reduce the negative effects of modeling autocorrelated observations.
+Further, the \texttt{mspTrain} function includes the option to update the training window over time.
+Re-estimating the projection matrix and test statistic thresholds at pre-specified time intervals  (adaptive) can reduce the negative effects of non-linearity and non-stationarity when modeling the observations.
+The idea is to divide a non-linear and non-stationary process between some equally-spaced boundaries (every day, for instance), so that the process becomes locally linear and stationary within these boundaries.
+As time progresses, the oldest observations are ``forgotten'' and the newest observations are ``learned''.
+This causes the projection and IC thresholds to ``adapt'' over time.
 
 \subsection{Model Training}
-After the observations have been split by class, the \texttt{mspTrain} function will call the internal function \texttt{processMonitor}, which in turn calls the internal function \texttt{faultFilter}.
+After the observations have been split by class, the \texttt{mspTrain} function will call the internal function \texttt{processMonitor}, which subsequently calls the internal function \texttt{faultFilter}.
 This function will calculate a linear projection matrix of the data by taking the PCA of the training data matrix.
@@
 
-Furthermore, non-parametric threshold values are calculated for the two process monitoring statistics -- \emph{Squared Prediction Error} and \emph{Hotelling's} $T^2$.
-These monitoring statistics are described in the motivating paper.
-These threshold values are found in the internal \texttt{threshold} function, and passed through the function pipe to be returned by \texttt{mspTrain}.
-The $\alpha$-level of the nonparametric threshold is controlled by the user, and its default value is 0.001.
+Furthermore, non-parametric threshold values are calculated for the two process monitoring statistics -- \emph{Squared Prediction Error} (SPE) and \emph{Hotelling's} $T^2$ ($T^2$).
+These monitoring statistics are described in the motivating paper (Chapter \ref{chap:MS_MVSPC}).
+These threshold values are calculated by the internal \texttt{threshold} function, and passed up through the function pipe to be returned by \texttt{mspTrain}.
+The $\alpha$-level of the nonparametric threshold is controlled by the user, but defaults to 0.001.
 
-Finally, the \texttt{mspTrain} function will remove any observation which would cause an alarm from the training data set.
-The alarm free observations will be returned in one \texttt{xts} matrix, while the alarmed observations will be returned by another.
-When training your process monitor, pay attention to the observations flagged as alarms.
+Finally, the \texttt{mspTrain} function will remove any observation(s) which would cause an alarm from the training data set.
+The alarm-free observations will be returned in one \texttt{xts} matrix, while the alarmed observations will be returned by another.
+The alarm criteria are discussed in Section \ref{sec:D_Alarms}.
+When training the process monitor, pay attention to any observations flagged as alarms.
 The proportion of observations flagged as faults may be higher than the $\alpha$-level specified, so some tuning may be necessary.
+As with the \texttt{mspProcessData} function, a detailed description of the inputs and outputs from the \texttt{mspTrain} function are shown in Section \ref{sec:D_Workflow}.
 

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Edited section 5.4

@@
 ##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:5] 0.2407 0.0621 0.2815 0.1616 0.3386 ...
+##   Data: num [1:4142, 1:5] 0.823 0.495 0.321 0.537 0.212 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##   ..$ 1:List of 6
-##   .. ..$ SPE_threshold   : Named num 3.59
+##   .. ..$ SPE_threshold   : Named num 4.8
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 61.6
+##   .. ..$ T2_threshold    : Named num 61.3
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.421 -0.389 0.433 0.43 -0.32 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.202 0 0 1.646
-##   .. ..$ muTrain         : Named num [1:6] 1.36 -2.09 2.93 1.35 -2.05 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.42 -0.391 0.432 0.428 -0.326 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.201 0 0 1.713
+##   .. ..$ muTrain         : Named num [1:6] 1.33 -2.09 2.85 1.31 -2.05 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.58 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.66 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 2:List of 6
-##   .. ..$ SPE_threshold   : Named num 1.35
+##   .. ..$ SPE_threshold   : Named num 2.02
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 77
+##   .. ..$ T2_threshold    : Named num 80
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:3] 0.5025 -0.0192 -0.4984 0.5267 0.1392 ...
-##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.686 ...
-##   .. ..$ muTrain         : Named num [1:6] 2.946 -0.565 -4.465 2.92 -0.59 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:3] 0.506 -0.0868 -0.4999 0.5265 0.1125 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.679 ...
+##   .. ..$ muTrain         : Named num [1:6] 2.885 -0.576 -4.422 2.86 -0.601 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.04 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.06 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 3:List of 6
-##   .. ..$ SPE_threshold   : Named num 6.42
+##   .. ..$ SPE_threshold   : Named num 4.46
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 85.4
+##   .. ..$ T2_threshold    : Named num 82.6
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.399 -0.453 -0.454 0.152 -0.462 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.275 0 0 0.501
-##   .. ..$ muTrain         : Named num [1:6] 0.526 0.268 1.411 0.566 0.254 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.411 -0.456 -0.458 0.131 -0.453 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.272 0 0 0.499
+##   .. ..$ muTrain         : Named num [1:6] 0.525 0.261 1.377 0.564 0.247 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 16.8 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 15.4 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
@@
 ##                     state         x         y         z       x.1
-## 2015-05-22 07:00:00     1 0.4542266 -1.188745 0.6005185 0.3809131
-## 2015-05-22 07:01:00     1 0.4889364 -1.416970 0.5952562 0.4542266
-## 2015-05-22 07:02:00     1 0.6942253 -1.436590 0.9416095 0.4889364
-## 2015-05-22 07:03:00     1 0.5357452 -1.563710 0.9727830 0.6942253
-## 2015-05-22 07:04:00     1 0.6569141 -1.504261 0.9597280 0.5357452
-## 2015-05-22 07:05:00     1 0.5957465 -1.298968 0.6082284 0.6569141
+## 2015-05-22 07:00:00     1 0.7579571 -1.518032 1.3443886 0.3906853
+## 2015-05-22 07:01:00     1 0.7644197 -1.489935 0.8451787 0.7579571
+## 2015-05-22 07:02:00     1 0.5797654 -1.585442 0.7934814 0.7644197
+## 2015-05-22 07:03:00     1 0.5630561 -1.502471 0.8140064 0.5797654
+## 2015-05-22 07:04:00     1 0.6274190 -1.342661 0.6885947 0.5630561
+## 2015-05-22 07:05:00     1 0.4543723 -1.331050 1.0142873 0.6274190
 ##                            y.1       z.1
-## 2015-05-22 07:00:00  0.09361165 0.3698668
-## 2015-05-22 07:01:00 -1.18874504 0.6005185
-## 2015-05-22 07:02:00 -1.41696998 0.5952562
-## 2015-05-22 07:03:00 -1.43659004 0.9416095
-## 2015-05-22 07:04:00 -1.56371006 0.9727830
-## 2015-05-22 07:05:00 -1.50426070 0.9597280
+## 2015-05-22 07:00:00  0.1067118 0.4294944
+## 2015-05-22 07:01:00 -1.5180323 1.3443886
+## 2015-05-22 07:02:00 -1.4899346 0.8451787
+## 2015-05-22 07:03:00 -1.5854425 0.7934814
+## 2015-05-22 07:04:00 -1.5024712 0.8140064
+## 2015-05-22 07:05:00 -1.3426613 0.6885947
 \end{verbatim}
@@
 ##                             x         y         z       x.1        y.1
-## 2015-05-22 07:00:00 0.4542266 -1.188745 0.6005185 0.3809131  0.09361165
-## 2015-05-22 07:01:00 0.4889364 -1.416970 0.5952562 0.4542266 -1.18874504
-## 2015-05-22 07:02:00 0.6942253 -1.436590 0.9416095 0.4889364 -1.41696998
-## 2015-05-22 07:03:00 0.5357452 -1.563710 0.9727830 0.6942253 -1.43659004
-## 2015-05-22 07:04:00 0.6569141 -1.504261 0.9597280 0.5357452 -1.56371006
-## 2015-05-22 07:05:00 0.5957465 -1.298968 0.6082284 0.6569141 -1.50426070
+## 2015-05-22 07:00:00 0.7579571 -1.518032 1.3443886 0.3906853  0.1067118
+## 2015-05-22 07:01:00 0.7644197 -1.489935 0.8451787 0.7579571 -1.5180323
+## 2015-05-22 07:02:00 0.5797654 -1.585442 0.7934814 0.7644197 -1.4899346
+## 2015-05-22 07:03:00 0.5630561 -1.502471 0.8140064 0.5797654 -1.5854425
+## 2015-05-22 07:04:00 0.6274190 -1.342661 0.6885947 0.5630561 -1.5024712
+## 2015-05-22 07:05:00 0.4543723 -1.331050 1.0142873 0.6274190 -1.3426613
 ##                           z.1        SPE SPE_Flag        T2 T2_Flag Alarm
-## 2015-05-22 07:00:00 0.3698668 2.0491906        0 25.423541       0    NA
-## 2015-05-22 07:01:00 0.6005185 0.1819048        0  6.563964       0    NA
-## 2015-05-22 07:02:00 0.5952562 0.3945702        0  5.086740       0    NA
-## 2015-05-22 07:03:00 0.9416095 0.1778764        0  4.277330       0    NA
-## 2015-05-22 07:04:00 0.9727830 0.1784149        0  4.399492       0    NA
-## 2015-05-22 07:05:00 0.9597280 1.1749990        0  5.393532       0    NA
+## 2015-05-22 07:00:00 0.4294944 0.20931587        0 29.288660       0    NA
+## 2015-05-22 07:01:00 1.3443886 0.62648522        0  3.367017       0    NA
+## 2015-05-22 07:02:00 0.8451787 0.26807516        0  3.992137       0    NA
+## 2015-05-22 07:03:00 0.7934814 0.06664741        0  4.743184       0    NA
+## 2015-05-22 07:04:00 0.8140064 0.65173294        0  5.120512       0    NA
+## 2015-05-22 07:05:00 0.6885947 0.82470301        0  5.330486       0    NA
 \end{verbatim}

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Edited section 5.5

@@
 
-After training the model with \texttt{mspTrain}, the projection matrices and non-parametric monitoring statistic thresholds can be used to flag incoming observations.
-This function can check every observation in a test matrix (useful when analyzing past data), but was instead designed to test a single incoming observation at a time via a script or batch file.
-To this end, the \texttt{mspMonitor} function projects a single observation with the class projection matrices returned by \texttt{mspTrain} and checks the observation's \emph{SPE} and $T^2$ statistics against the thresholds returned by \texttt{mspTrain}.
-The \texttt{mspMonitor} will then append the monitoring statistic values and indicators to the end of the observation row.
-Indicator values will be returned as a ``1'' if the values of these statistics exceed normal thresholds.
+After training the model with \texttt{mspTrain}, the projection matrices and non-parametric monitoring statistic thresholds can be used to flag incoming observations which are potentially out of control.
+The \texttt{mspMonitor} function was instead designed to test a single incoming observation at a time via a script or batch file, but \emph{can} check every observation in a test matrix, which is useful for analyzing past data.
+To this end, the \texttt{mspMonitor} function projects a single observation with the class projection matrices returned by \texttt{mspTrain} and checks the observation's \emph{SPE} and $T^2$ statistics against the thresholds also returned by \texttt{mspTrain}.
+The \texttt{mspMonitor} function will then append the monitoring statistic values and indicators to the end of the observation row.
+Indicator values will be returned as a ``1'' if the values of these statistics exceed their IC thresholds.
 This new appended observation will be passed to the \texttt{mspWarning} function.
 
-If an observation returned by the \texttt{mspMonitor} function has positive statistic indicator values for either the SPE or $T^2$ monitoring statistics, then the \texttt{mspWarning} function will query the last set $r$ observations for other flags.
+The \texttt{mspWarning} function takes in an observation returned by the \texttt{mspMonitor} function and an integer value (denoted $r$ for this discussion) dictating the number of sequential flagged observations observed before an alarm is raised.
+If an observation returned by the \texttt{mspMonitor} function has positive statistic indicator values for either the SPE or $T^2$ monitoring statistics, then the \texttt{mspWarning} function will query the most recent $r$ observations for other flags.
 If all $r$ observations are positive for anomalies, then the \texttt{mspWarning} function will issue an alarm.
-This $r$ is the parameter \texttt{faultsToTriggerAlarm}, and it defaults to 5.
-However, this default value depends heavily on the scale of the data: for continuous observations aggregated and recorded every five seconds, the number of sequential faults necessary to trigger an alarm should be very high, perhaps even 20 or more.
-For observations aggregated to the 10-minute-scale, only three sequential faults may be necessary.
+The number of flags necessary to trigger an alarm defaults to 5.
+However, this default value depends heavily on the scale of the data: for continuous observations aggregated and recorded every five seconds, the number of sequential flags necessary to trigger an alarm could be much higher, perhaps even 20 or more.
+In contrast, for observations aggregated to the 10-minute-scale, only three sequential flags may be necessary.
 
-In future updates of this package, this function will also have an option to issue an alarm if a critical mass of non-sequential alarms is reached in a set period of observations.
+In future updates of this package, this function will also have an option to issue an alarm if a critical mass of non-sequential flags is reached in a set period of observations.
 This modification may be necessary if the observation level becomes more fine than the 1-minute-level.
 Additionally, this function will also be equipped to take in a cell phone number and service provider and issue an alarm via SMS through email.
+Detailed descriptions of the inputs and outputs from the \texttt{mspMonitor} and \texttt{mspWarning} functions are shown in the next section.
 

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Edited section 5.5

@@
 ##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:5] 0.823 0.495 0.321 0.537 0.212 ...
+##   Data: num [1:4142, 1:5] 0.28 0.201 1.208 0.919 0.418 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##   ..$ 1:List of 6
-##   .. ..$ SPE_threshold   : Named num 4.8
+##   .. ..$ SPE_threshold   : Named num 4.29
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 61.3
+##   .. ..$ T2_threshold    : Named num 62.6
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.42 -0.391 0.432 0.428 -0.326 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.201 0 0 1.713
-##   .. ..$ muTrain         : Named num [1:6] 1.33 -2.09 2.85 1.31 -2.05 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.422 -0.386 0.435 0.431 -0.318 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.204 0 0 1.606
+##   .. ..$ muTrain         : Named num [1:6] 1.37 -2.1 2.95 1.36 -2.06 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.66 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.64 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 2:List of 6
-##   .. ..$ SPE_threshold   : Named num 2.02
+##   .. ..$ SPE_threshold   : Named num 1.16
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 80
+##   .. ..$ T2_threshold    : Named num 74.2
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:3] 0.506 -0.0868 -0.4999 0.5265 0.1125 ...
-##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.285 0 0 0 0.679 ...
-##   .. ..$ muTrain         : Named num [1:6] 2.885 -0.576 -4.422 2.86 -0.601 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4957 -0.0668 0.4887 -0.5236 -0.1866 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.284 0 0 0 0.712 ...
+##   .. ..$ muTrain         : Named num [1:6] 2.978 -0.566 -4.508 2.95 -0.592 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.06 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.08 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 3:List of 6
-##   .. ..$ SPE_threshold   : Named num 4.46
+##   .. ..$ SPE_threshold   : Named num 8.04
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 82.6
+##   .. ..$ T2_threshold    : Named num 80.8
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.411 -0.456 -0.458 0.131 -0.453 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.272 0 0 0.499
-##   .. ..$ muTrain         : Named num [1:6] 0.525 0.261 1.377 0.564 0.247 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.392 -0.452 -0.454 0.163 -0.462 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.493
+##   .. ..$ muTrain         : Named num [1:6] 0.528 0.268 1.413 0.57 0.254 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 15.4 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 17.4 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
@@
 ##                     state         x         y         z       x.1
-## 2015-05-22 07:00:00     1 0.7579571 -1.518032 1.3443886 0.3906853
-## 2015-05-22 07:01:00     1 0.7644197 -1.489935 0.8451787 0.7579571
-## 2015-05-22 07:02:00     1 0.5797654 -1.585442 0.7934814 0.7644197
-## 2015-05-22 07:03:00     1 0.5630561 -1.502471 0.8140064 0.5797654
-## 2015-05-22 07:04:00     1 0.6274190 -1.342661 0.6885947 0.5630561
-## 2015-05-22 07:05:00     1 0.4543723 -1.331050 1.0142873 0.6274190
+## 2015-05-22 07:00:00     1 0.5454353 -1.494528 0.9296569 0.4159290
+## 2015-05-22 07:01:00     1 0.5752773 -1.638525 1.1806822 0.5454353
+## 2015-05-22 07:02:00     1 0.5381703 -1.448424 1.0029127 0.5752773
+## 2015-05-22 07:03:00     1 0.6097887 -1.320156 0.9345597 0.5381703
+## 2015-05-22 07:04:00     1 0.8534018 -1.555631 1.0922745 0.6097887
+## 2015-05-22 07:05:00     1 0.7252695 -1.792569 1.1605990 0.8534018
 ##                            y.1       z.1
-## 2015-05-22 07:00:00  0.1067118 0.4294944
-## 2015-05-22 07:01:00 -1.5180323 1.3443886
-## 2015-05-22 07:02:00 -1.4899346 0.8451787
-## 2015-05-22 07:03:00 -1.5854425 0.7934814
-## 2015-05-22 07:04:00 -1.5024712 0.8140064
-## 2015-05-22 07:05:00 -1.3426613 0.6885947
+## 2015-05-22 07:00:00  0.1063122 0.3767823
+## 2015-05-22 07:01:00 -1.4945284 0.9296569
+## 2015-05-22 07:02:00 -1.6385255 1.1806822
+## 2015-05-22 07:03:00 -1.4484243 1.0029127
+## 2015-05-22 07:04:00 -1.3201558 0.9345597
+## 2015-05-22 07:05:00 -1.5556311 1.0922745
 \end{verbatim}
@@
 ##                             x         y         z       x.1        y.1
-## 2015-05-22 07:00:00 0.7579571 -1.518032 1.3443886 0.3906853  0.1067118
-## 2015-05-22 07:01:00 0.7644197 -1.489935 0.8451787 0.7579571 -1.5180323
-## 2015-05-22 07:02:00 0.5797654 -1.585442 0.7934814 0.7644197 -1.4899346
-## 2015-05-22 07:03:00 0.5630561 -1.502471 0.8140064 0.5797654 -1.5854425
-## 2015-05-22 07:04:00 0.6274190 -1.342661 0.6885947 0.5630561 -1.5024712
-## 2015-05-22 07:05:00 0.4543723 -1.331050 1.0142873 0.6274190 -1.3426613
+## 2015-05-22 07:00:00 0.5454353 -1.494528 0.9296569 0.4159290  0.1063122
+## 2015-05-22 07:01:00 0.5752773 -1.638525 1.1806822 0.5454353 -1.4945284
+## 2015-05-22 07:02:00 0.5381703 -1.448424 1.0029127 0.5752773 -1.6385255
+## 2015-05-22 07:03:00 0.6097887 -1.320156 0.9345597 0.5381703 -1.4484243
+## 2015-05-22 07:04:00 0.8534018 -1.555631 1.0922745 0.6097887 -1.3201558
+## 2015-05-22 07:05:00 0.7252695 -1.792569 1.1605990 0.8534018 -1.5556311
 ##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
-## 2015-05-22 07:00:00 0.4294944 0.20931587        0 29.288660       0    NA
-## 2015-05-22 07:01:00 1.3443886 0.62648522        0  3.367017       0    NA
-## 2015-05-22 07:02:00 0.8451787 0.26807516        0  3.992137       0    NA
-## 2015-05-22 07:03:00 0.7934814 0.06664741        0  4.743184       0    NA
-## 2015-05-22 07:04:00 0.8140064 0.65173294        0  5.120512       0    NA
-## 2015-05-22 07:05:00 0.6885947 0.82470301        0  5.330486       0    NA
+## 2015-05-22 07:00:00 0.3767823 0.8309122        0 27.233955       0    NA
+## 2015-05-22 07:01:00 0.9296569 0.0575549        0  4.361359       0    NA
+## 2015-05-22 07:02:00 1.1806822 0.4782941        0  5.062568       0    NA
+## 2015-05-22 07:03:00 1.0029127 1.0857386        0  5.471633       0    NA
+## 2015-05-22 07:04:00 0.9345597 0.2959896        0  4.626291       0    NA
+## 2015-05-22 07:05:00 1.0922745 0.3100297        0  2.913877       0    NA
 \end{verbatim}

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Finished draft 2 edits.

@@
 
-\subsection{Synthetic Fault Induction}
+\subsection{Synthetic Fault Induction} \label{subsec:D_FaultDefns}
 Faults can be introduced to single- or multi-state data via the \texttt{mspProcessData} function.
@@
 
-This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package.
-This package depends on a few other packages, but most of these dependencies are on commonly-used packages.
+This section provides a fully commented code walk-through for the main \texttt{msp.*} functions in the \texttt{mvMonitoring} package.
+This package depends on few other packages, and most of these dependencies are on commonly-used packages.
 The exception is \texttt{BMS}.
@@
 \subsection{Generating Synthetic Data}
-First begin by generating multi-state data from a fault scenario.
-This code will yield observations under Fault 2A, as described the Synthetic Fault Induction section.
+First, begin by generating multi-state data from a fault scenario.
+This code will yield observations under Fault 2A, as described in Section \ref{subsec:D_FaultDefns}.
 We choose the default options for the period length (7 days * 24 hours * 60 minutes = 10,080 observations), the starting index of the fault (8500 out of 10080), and the time stamp for beginning the data is 16 May of 2016 at 10:00AM (my wedding anniversary).
-As we can see from the \texttt{str()} function, we have an \texttt{xts} matrix with 10080 rows and four columns (the state indicator and the three features).
+As we can see from the structure of the output, \texttt{mspProcessData} returns an \texttt{xts} matrix with 10080 rows and four columns (the state indicator and the three features).
 
@@
 Now that these observations are generated and stored in memory, the \texttt{mspTrain} function can train the MSAD-PCA model.
-The last 1620 observations (27 hours' worth) will be saved for testing.
-The \texttt{mspTrain} function takes in the training data set partitioned between the observation and the label column.
-If this function errors, make sure the label column is not included in the data matrix -- this will cause a singularity in the data.
-The function will
+The last 1620 observations (27 hours' worth) will be saved for validation.
+The \texttt{mspTrain} function takes in the training data matrix and corresponding class label column.
+If this function errors, make sure the label column is not included in the data matrix -- the constant values will cause a rank deficiency training covariance matrix.
+The \texttt{mspTrain} function will
 \begin{enumerate}
@@
 %
-\item Retrain and repeat until the end of the data matrix
+\item Retrain and repeat until the end of the training matrix.
 \end{enumerate}
@@
 \item \texttt{FaultChecks}: An \texttt{xts} matrix of monitoring statistics and associated indicators for all observations after the burn-in of \texttt{trainObs}.
-It will have 10080 - \texttt{trainObs} number of rows and five columns:
+It will have 8461 - \texttt{trainObs} number of rows and five columns:
 	\begin{enumerate}
@@
 %
-\item \texttt{Non\_Alarmed\_Obs}: An \texttt{xts} matrix will all observations with an alarm code of 0 from \texttt{FaultChecks}.
+\item \texttt{Non\_Alarmed\_Obs}: An \texttt{xts} matrix containing all observations with an alarm code of 0 from \texttt{FaultChecks}.
 Of note, this matrix contains the data, while the \texttt{FaultChecks} matrix only contains the monitoring statistics and indicators.
@@
 Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}.
-Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
+Notice that the first six rows of the matrix returned by \texttt{mspMonitor} are the exact same as the first six rows of the lagged test matrix, except that the rows of the matrix from the \texttt{mspMonitor} function have the monitoring statistics and corresponding indicator columns appended.
 <<r monitor>>=
@@
 \subsection{Warn Operators During Alarms}
-Note that all `Alarm` codes in the monitor matrix above are recorded with \texttt{NA} values.
-This is because the \texttt{mspMonitor} function does not check the sequential flag conditions of the monitor matrix.
+Note that all values in the \texttt{Alarm} column of the returned matrix above are recorded with \texttt{NA} values.
+This is because the \texttt{mspMonitor} function does not check the monitor output matrix for the sequential flags necessary to trigger an alarm.
 This is the responsibility of the \texttt{mspWarning} function.
@@
 @
-The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
+\noindent The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
 <<r warning_Plot>>=
@@
 @
-The alarm codes are
+\noindent The alarm codes are
 \begin{enumerate}
@@
 \end{enumerate}
-As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.
+\noindent As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.
 

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Finished draft 2 edits.

@@
 ##  $ FaultChecks    :An 'xts' object on 2015-05-19 08:59:00/2015-05-22 07:00:00 containing:
-##   Data: num [1:4142, 1:5] 0.28 0.201 1.208 0.919 0.418 ...
+##   Data: num [1:4142, 1:5] 1.205 0.195 1.304 1.5 1.458 ...
 ##  - attr(*, "dimnames")=List of 2
@@
 ##   ..$ 1:List of 6
-##   .. ..$ SPE_threshold   : Named num 4.29
+##   .. ..$ SPE_threshold   : Named num 5.59
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 62.6
+##   .. ..$ T2_threshold    : Named num 59.1
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.422 -0.386 0.435 0.431 -0.318 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.204 0 0 1.606
-##   .. ..$ muTrain         : Named num [1:6] 1.37 -2.1 2.95 1.36 -2.06 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.426 -0.378 0.439 0.435 -0.303 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.209 0 0 1.458
+##   .. ..$ muTrain         : Named num [1:6] 1.39 -2.1 2.99 1.37 -2.06 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.64 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.67 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 2:List of 6
-##   .. ..$ SPE_threshold   : Named num 1.16
+##   .. ..$ SPE_threshold   : Named num 0.851
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 74.2
+##   .. ..$ T2_threshold    : Named num 74.8
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4957 -0.0668 0.4887 -0.5236 -0.1866 ...
-##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.284 0 0 0 0.712 ...
-##   .. ..$ muTrain         : Named num [1:6] 2.978 -0.566 -4.508 2.95 -0.592 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.494 -0.0815 0.4886 -0.522 -0.195 ...
+##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.732 ...
+##   .. ..$ muTrain         : Named num [1:6] 2.981 -0.57 -4.51 2.954 -0.597 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.08 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.1 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
 ##   ..$ 3:List of 6
-##   .. ..$ SPE_threshold   : Named num 8.04
+##   .. ..$ SPE_threshold   : Named num 5.49
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ T2_threshold    : Named num 80.8
+##   .. ..$ T2_threshold    : Named num 82.5
 ##   .. .. ..- attr(*, "names")= chr "99.9%"
-##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.392 -0.452 -0.454 0.163 -0.462 ...
-##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.493
-##   .. ..$ muTrain         : Named num [1:6] 0.528 0.268 1.413 0.57 0.254 ...
+##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.393 0.445 0.448 -0.18 0.466 ...
+##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.496
+##   .. ..$ muTrain         : Named num [1:6] 0.531 0.272 1.437 0.573 0.258 ...
 ##   .. .. ..- attr(*, "names")= chr [1:6] "x" "y" "z" "x.1" ...
-##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 17.4 0 0 0 0 ...
+##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 18.4 0 0 0 0 ...
 ##   .. ..- attr(*, "class")= chr [1:2] "threshold" "pca"
@@
 ##                     state         x         y         z       x.1
-## 2015-05-22 07:00:00     1 0.5454353 -1.494528 0.9296569 0.4159290
-## 2015-05-22 07:01:00     1 0.5752773 -1.638525 1.1806822 0.5454353
-## 2015-05-22 07:02:00     1 0.5381703 -1.448424 1.0029127 0.5752773
-## 2015-05-22 07:03:00     1 0.6097887 -1.320156 0.9345597 0.5381703
-## 2015-05-22 07:04:00     1 0.8534018 -1.555631 1.0922745 0.6097887
-## 2015-05-22 07:05:00     1 0.7252695 -1.792569 1.1605990 0.8534018
+## 2015-05-22 07:00:00     1 0.4945284 -1.376417 0.7072224 0.3745871
+## 2015-05-22 07:01:00     1 0.6357969 -1.547100 0.9991109 0.4945284
+## 2015-05-22 07:02:00     1 0.6318896 -1.535374 1.0846997 0.6357969
+## 2015-05-22 07:03:00     1 0.6712189 -1.521690 0.8632718 0.6318896
+## 2015-05-22 07:04:00     1 0.6971078 -1.665835 0.8971302 0.6712189
+## 2015-05-22 07:05:00     1 0.9239645 -1.632949 1.0113845 0.6971078
 ##                             y.1       z.1
-## 2015-05-22 07:00:00  0.1063122 0.3767823
-## 2015-05-22 07:01:00 -1.4945284 0.9296569
-## 2015-05-22 07:02:00 -1.6385255 1.1806822
-## 2015-05-22 07:03:00 -1.4484243 1.0029127
-## 2015-05-22 07:04:00 -1.3201558 0.9345597
-## 2015-05-22 07:05:00 -1.5556311 1.0922745
+## 2015-05-22 07:00:00  0.08531597 0.3699029
+## 2015-05-22 07:01:00 -1.37641739 0.7072224
+## 2015-05-22 07:02:00 -1.54709995 0.9991109
+## 2015-05-22 07:03:00 -1.53537382 1.0846997
+## 2015-05-22 07:04:00 -1.52168971 0.8632718
+## 2015-05-22 07:05:00 -1.66583498 0.8971302
 \end{verbatim}
@@
 Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}.
-Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
+Notice that the first six rows of the matrix returned by \texttt{mspMonitor} are the exact same as the first six rows of the lagged test matrix, except that the rows of the matrix from the \texttt{mspMonitor} function have the monitoring statistics and corresponding indicator columns appended.
 \begin{knitrout}
@@
 ##                             x         y         z       x.1         y.1
-## 2015-05-22 07:00:00 0.5454353 -1.494528 0.9296569 0.4159290  0.1063122
-## 2015-05-22 07:01:00 0.5752773 -1.638525 1.1806822 0.5454353 -1.4945284
-## 2015-05-22 07:02:00 0.5381703 -1.448424 1.0029127 0.5752773 -1.6385255
-## 2015-05-22 07:03:00 0.6097887 -1.320156 0.9345597 0.5381703 -1.4484243
-## 2015-05-22 07:04:00 0.8534018 -1.555631 1.0922745 0.6097887 -1.3201558
-## 2015-05-22 07:05:00 0.7252695 -1.792569 1.1605990 0.8534018 -1.5556311
+## 2015-05-22 07:00:00 0.4945284 -1.376417 0.7072224 0.3745871  0.08531597
+## 2015-05-22 07:01:00 0.6357969 -1.547100 0.9991109 0.4945284 -1.37641739
+## 2015-05-22 07:02:00 0.6318896 -1.535374 1.0846997 0.6357969 -1.54709995
+## 2015-05-22 07:03:00 0.6712189 -1.521690 0.8632718 0.6318896 -1.53537382
+## 2015-05-22 07:04:00 0.6971078 -1.665835 0.8971302 0.6712189 -1.52168971
+## 2015-05-22 07:05:00 0.9239645 -1.632949 1.0113845 0.6971078 -1.66583498
 ##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
-## 2015-05-22 07:00:00 0.3767823 0.8309122        0 27.233955       0    NA
-## 2015-05-22 07:01:00 0.9296569 0.0575549        0  4.361359       0    NA
-## 2015-05-22 07:02:00 1.1806822 0.4782941        0  5.062568       0    NA
-## 2015-05-22 07:03:00 1.0029127 1.0857386        0  5.471633       0    NA
-## 2015-05-22 07:04:00 0.9345597 0.2959896        0  4.626291       0    NA
-## 2015-05-22 07:05:00 1.0922745 0.3100297        0  2.913877       0    NA
+## 2015-05-22 07:00:00 0.3699029 1.2098887        0 27.458819       0    NA
+## 2015-05-22 07:01:00 0.7072224 0.1235024        0  5.798909       0    NA
+## 2015-05-22 07:02:00 0.9991109 0.3013605        0  4.793520       0    NA
+## 2015-05-22 07:03:00 1.0846997 0.4092379        0  4.901590       0    NA
+## 2015-05-22 07:04:00 0.8632718 0.1091666        0  4.492368       0    NA
+## 2015-05-22 07:05:00 0.8971302 0.6033914        0  3.749758       0    NA
 \end{verbatim}
@@
 \end{knitrout}
-The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
+\noindent The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
 \begin{knitrout}
@@
 \end{knitrout}
-The alarm codes are
+\noindent The alarm codes are
 \begin{enumerate}
@@
 \section{Conclusion} \label{sec:D_Conclusion}
-We have supplied our motivation for this package, and we have discussed implementing a multivariate process monitoring scheme with this package using the example of a decentralized WWT plant in Golden, CO.
-We believe that this software will provide system engineers with the tools necessary to quickly and accurately detect abnormalities in multivariate, autocorrelated, non-stationary, non-linear, and multi-state water treatment systems.
+We have supplied our motivation for this package, and we have discussed implementing a multivariate process monitoring scheme with this package using synthetic data.
+We believe that this software will provide system engineers with the tools necessary to quickly and accurately detect abnormalities in multivariate, autocorrelated, non-stationary, non-linear, and multi-state industrial and engineering systems.
 Further, we have given a synthetic example showing how the functions within this package would be implemented and tuned in practice.

### 2017-09-08 R/mspSubset.R
Added mspSubset function

@@ -1,0 +1,65 @@
+#' Multi-State Subsetting
+#'
+#' @description This function separates the data into k subsets, one for each
+#' of the k states, containing the subset of the original variables that are of interest
+#' for a given state.
+#' @param data An xts data matrix
+#' @param labelVector Class labels as a logical (two states only) or
+#' finite numeric (two or more states) vector or matrix column (not
+#' from a data frame) with length equal to the number of rows in "data."
+#' For data with only one state, this will be a vector of 1s.
+#' @param subsetMatrix A matrix of logicals with number of rows equal to the number of
+#' states and number of columns equal to the number of columns in data. The i,j entry in
+#' the matrix indicates whether or not to monitor the jth variable in the
+#' ith state.
+#' @return A list with the following components:
+#' \item{Class1Data -- }{an xts data matrix containing the subset of the state 1 data.}
+#' \item{Class2Data -- }{an xts data matrix containing the subset of the state 2 data.}
+#' \item{Class3Data -- }{an xts data matrix containing the subset of the state 3 data.}
+#'
+#' @details This function is designed to be used in conjunction with \code{\link{mspTrain}}
+#' and to allow the user to monitor a different subset of the variables during each state.
+#' @examples
+#' nrml <- mspProcessData(faults = "NOC")
+#'
+#' sub1 <- c(T,T,F)
+#' sub2 <- c(T,F,T)
+#' sub3 <- c(T,F,F)
+#' submatrix <- t(matrix(c(sub1,sub2,sub3),nrow=3,ncol=3))
+#'
+#' subsets <- mspSubset(data = nrml[,-1],
+#' labelVector = nrml[,1],
+#' subsetMatrix = submatrix)
+
+mspSubset <- function(data,
+                      labelVector = rep(1, nrow(data)),
+                      subsetMatrix = matrix(TRUE,nrow = length(unique(labelVector)), ncol = ncol(data))){
+
+  # Is data an xts object?
+   if(!is.xts(data)){
+    stop("Object 'data' is not an xts object. Please transform your data to an
+         extendible time series.")
+  }
+
+  # What are the states?
+  classes <- unique(labelVector)
+
+  # We have to do this because of how xts objects are subsetted
+  names(classes) <- LETTERS[1:length(classes)]
+
+  if(is.vector(labelVector)){
+    labelVector <- matrix(labelVector, ncol = 1)
+  }
[…]

### 2017-10-13 vignettes/MVSPC-Workflow.R
Updated figure display in vignette: the text in the figure was all squished together.

@@ -42,7 +42,7 @@ for(i in 1:nrow(alarm1A_xts)){
   }
 }
 
-## ------------------------------------------------------------------------
+## ---- fig.width = 5, out.width = '100%'----------------------------------
 plot(alarm1A_xts[, ncol(alarm1A_xts)],
      main = "Alarm Codes for Test Data")
 

### 2017-10-18 README.Rmd
Last preparations before CRAN submission. Build passing on mac OS. Will check on Windows 7 Enterprise once I get to the office.

@@
 
-## Installation
+## Installation from CRAN
+As of 18 October, 2017, we have submitted this package to CRAN. Shortly thereafter, you will be able to install the stable version of the package via
+```{r packLoad_CRAN, eval=FALSE}
+install.packages("mvMonitoring")
+```
+
+## Installation of Development Version
 Make sure you have the latest version of the `devtools` package, and pull the package from GitHub.
@@
 # minute level
-noc_xts <- mspProcessData(faults = "NOC")
+nrml <- mspProcessData(faults = "NOC")
 # The state values are recorded in the first column.
-n <- nrow(noc_xts)
+n <- nrow(nrml)
 
@@
 # the training window each day.
-trainResults_ls <- mspTrain(data = noc_xts[1:(n - 5), -1],
-                            labelVector = noc_xts[1:(n - 5), 1],
+trainResults_ls <- mspTrain(data = nrml[1:(n - 5), -1],
+                            labelVector = nrml[1:(n - 5), 1],
                             trainObs = 4320)
@@
 # observations we will test.
-testObs <- noc_xts[(n - 6):n, -1]
+testObs <- nrml[(n - 6):n, -1]
 testObs <- xts:::lag.xts(testObs, 0:1)
 testObs <- testObs[-1,]
-testObs <- cbind(noc_xts[(n - 5):n, 1], testObs)
+testObs <- cbind(nrml[(n - 5):n, 1], testObs)
 

### 2017-10-18 README.Rmd
On my mac, I used devtools::build() to create the .tar.gz file for CRAN submission. After a few hours of reading, I settled on the GPLv2 license: it does not conflict with university IP regulations, it's supported by OSI, recognised by the NSF, and seems to offer adequate protection.
I also used the --as-cran option for devtools::check() and still passed with 0-0-0. The last push passed with 0-0-0 on Travis as well.

@@
 We create this package, `mvMonitoring`, from the foundation laid by Kazor et al (2016).
-The `mvMonitor` package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.
+This package is designed to make simulation of multi-state multivariate process monitoring statistics easy and straightforward, as well as streamlining the online process monitoring component.
 
@@
 ```
+
+## Acknowledgements
+This work is  supported by the King Abdullah University of Science and Technology (KAUST) Office of Sponsored Research (OSR) under Award No: OSR-2015-CRG4-2582 and by the National Science Foundation PFI:BIC Award No: 1632227.

### 2017-11-03 README.Rmd
Added CRAN tags to the README file. I'm leaving the Travis-CI tag for the development version of the package. Closes #26.

@@
 
+Travis Status (Devel v. 0.1.1) and CRAN Status (Stable v. 0.1.0)
+
 [![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?token=ZzKTz9X2qQxWeqCPkaKq&branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)
+![CRAN Build Status](http://www.r-pkg.org/badges/version/mvMonitoring)
 

### 2017-11-03 README.Rmd
Website rebuild with updated travis

--- 2017-10-18 README.Rmd
@@
 
-[![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?token=ZzKTz9X2qQxWeqCPkaKq&branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)
+Travis Status (Devel v. 0.1.1) and CRAN Status (Stable v. 0.1.0)
+
+[![Travis-CI Build Status](https://travis-ci.org/gabrielodom/mvmonitoring.svg?branch=master)](https://travis-ci.org/gabrielodom/mvmonitoring)
+![CRAN Build Status](http://www.r-pkg.org/badges/version/mvMonitoring)
 

### 2017-12-29 README.Rmd
update
Updated package site to new CRAN and Travis badges, including number of downloads badge.

--- 2017-10-18 README.Rmd
@@
 
-[![Travis-CI Build Status](https://travis-ci.com/gabrielodom/mvMonitoring.svg?token=ZzKTz9X2qQxWeqCPkaKq&branch=master)](https://travis-ci.com/gabrielodom/mvMonitoring)
+[![Travis-CI Build Status](https://travis-ci.org/gabrielodom/mvMonitoring.svg?branch=master)](https://travis-ci.org/gabrielodom/mvMonitoring)
+[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/grand-total/mvMonitoring)](https://cranlogs.r-pkg.org/badges/grand-total/mvMonitoring)
+![CRAN Build Status](http://www.r-pkg.org/badges/version/mvMonitoring)
 

### 2018-01-25 inst/mspGraphsGrid.R
Reminder, the code to build the simulation graphs in the paper is in inst/.

@@ -24,13 +24,18 @@ adpcaObs_ls %>% str
 faultStart <- index(adpcaObs_ls$NOC[8500,])
 
 ######  Create Graphing Function  ######
-mspGraphsGrid <- function(data_xts){
+mspGraphsGrid <- function(data_xts,
+                          rows = 7741:9600,
+                          faultStart = "2016-12-02 21:39:00 EST",
+                          Xlims = c(-0.5, 3.5),
+                          Ylims = c(-2.5, 2),
+                          Zlims = c(-6, 3)){
   # The fault is in the state from 8460:8520 (8500 / 60 = 141.67). Dr. Hering
   # wants to see four full cycles before this state, and six full cycles after.
   # Thus, we start at 141 * 60 - 4 * 3 * 60 = 7740 and end at
   # 142 * 60 + 6 * 3 * 60 = 9600.
-  obs_df <- data_xts[7741:9600, 1:4] %>% as.data.frame()
-  obs_df$dateTime <- index(data_xts[7741:9600,])
+  obs_df <- data_xts[rows, 1:4] %>% as.data.frame()
+  obs_df$dateTime <- index(data_xts[rows,])
   obs_df <- obs_df %>% mutate(State = as.factor(state))
 
   # Friendly colours for the Colour-Blind
@@ -49,7 +54,7 @@ mspGraphsGrid <- function(data_xts){
                                 as.POSIXct("2016-12-03 12:00:00 CST")),
                      date_labels = "%m-%d %H:%M",
                      name = "") +
-    scale_y_continuous(limits = c(-0.5, 3.5)) +
+    scale_y_continuous(limits = Xlims) +
     theme_bw() +
     theme(panel.grid = element_blank(),
           axis.title.y = element_blank(),
@@ -58,7 +63,7 @@ mspGraphsGrid <- function(data_xts){
           legend.background = element_blank()) + # legend.justification = c(1,0),
     guides(color = guide_legend(override.aes = list(size = 2))) +
     ggtitle("Feature X") +
-    geom_vline(xintercept = as.numeric(faultStart), size = 1)
+    geom_vline(xintercept = as.numeric(as.POSIXct(faultStart)), size = 1)
 
   p2 <- ggplot(data = obs_df,
                aes(x = dateTime, y = y, color = State, group = 1)) +
@@ -70,13 +75,13 @@ mspGraphsGrid <- function(data_xts){
[…]

### 2022-04-27 R/mspTrain.R
After the resubmit for Issue #28, CRAN marked a few older hyperlinks in our documentation.

@@ -109,7 +109,7 @@
 #'
 #'   For more details, see Kazor et al (2016):
 #'
-#'   \url{http://link.springer.com/article/10.1007/s00477-016-1246-2}
+#'   \url{https://doi.org/10.1007/s00477-016-1246-2}
 #'
 #' @seealso Calls: \code{\link{processMonitor}}. Pipe flow: \code{mspTrain}
 #'   into \code{\link{mspMonitor}} into \code{\link{mspWarning}}.

### 2022-04-29 R/mspTrain.R
Fixing hyperlinks for the CRAN resubmission (per Issue #28 still)

@@ -109,7 +109,7 @@
 #'
 #'   For more details, see Kazor et al (2016):
 #'
-#'   \url{https://doi.org/10.1007/s00477-016-1246-2}
+#'   \doi{10.1007/s00477-016-1246-2}
 #'
 #' @seealso Calls: \code{\link{processMonitor}}. Pipe flow: \code{mspTrain}
 #'   into \code{\link{mspMonitor}} into \code{\link{mspWarning}}.

### 2022-04-29 R/quantile_density_port.R

@@ -22,7 +22,7 @@
 #'   function from package BMS (\url{https://CRAN.R-project.org/package=BMS}).
 #'   In spring of 2022, CRAN informed us that the BMS has been orphaned, so we
 #'   copied the code (and corresponding documentation) we needed from it. See
-#'   \url{https://www.doi.org/10.18637/jss.v068.i04} for their paper.
+#'   \doi{10.18637/jss.v068.i04} for their paper.
 #'
 #'   The function \code{quantile.density()} applies generically to the built-in
 #'   class \code{density} (as least for versions where there is no such method

### 2023-06-29 LaTeX_Vignette/MS-MVSPC_DissertationVignette.Rnw
Spell checking

@@
 In Section \ref{sec:D_Motivation}, we discuss the motivation for creating this package, and briefly explain the utility of multi-state process monitoring.
-In Section \ref{sec:D_DataGen}, we offer a thorough explination of how to generate the synthetic data we employed to test and compare the new multi-state modification of the process monitoring setup with the \texttt{mspProcessData} function.
+In Section \ref{sec:D_DataGen}, we offer a thorough explanation of how to generate the synthetic data we employed to test and compare the new multi-state modification of the process monitoring setup with the \texttt{mspProcessData} function.
 In Section \ref{sec:D_Train}, we describe the necessary information and data formatting to effectively train the fault detection algorithm using the \texttt{mspTrain} function.
@@
 
-The \texttt{xts} object class stands for \emph{extendible time series} and comes from the package \texttt{xts}, which is built on the package \texttt{zoo}.
+The \texttt{xts} object class stands for \emph{extendable time series} and comes from the package \texttt{xts}, which is built on the package \texttt{zoo}.
 The date and time information for the multivariate stochastic process (necessarily as \texttt{POSIX} objects) are stored as the row indices of \texttt{xts} matrices.

### 2023-06-29 inst/Simulation_Vignette.Rmd
Spell checking

--- 2017-07-07 docs/articles/Simulation_Vignette.Rmd
@@
 ###  Features and State Features
-We will simulate three features, with each feaure operating under $k$ different states.
+We will simulate three features, with each feature operating under $k$ different states.
 We will use $<x(t), y(t), z(t)>$ instead of the $<x_1(t), x_2(t), x_3(t)>$ notation used in Kazor et al.
@@
 ```{r sweepEnv}
-# # uncomment these lines to use the data from the package. Comment them out
-# # when generating new data.
-# rm(list = ls())
-# load("~/Documents/GitHub/mvMonitoring/data/normal_switch_xts.rda")
-# load("~/Documents/GitHub/mvMonitoring/data/fault1A_xts.rda")
-# load("~/Documents/GitHub/mvMonitoring/data/fault1B_xts.rda")
-# load("~/Documents/GitHub/mvMonitoring/data/fault2A_xts.rda")
-# load("~/Documents/GitHub/mvMonitoring/data/fault2B_xts.rda")
-# load("~/Documents/GitHub/mvMonitoring/data/fault3A_xts.rda")
-# load("~/Documents/GitHub/mvMonitoring/data/fault3B_xts.rda")
+# uncomment these lines to use the data from the package. Comment them out
+# when generating new data.
+rm(list = ls())
+data("normal_switch_xts")
+data("fault1A_xts")
+data("fault1B_xts")
+data("fault2A_xts")
+data("fault2B_xts")
+data("fault3A_xts")
+data("fault3B_xts")
 
@@
 # False Alarms? 
-alarmData[,15] %>% sum(na.rm = T)
-alarmData[,11:15] %>% head
-alarmData[,11:15] %>% tail
+alarmData[,ncol(alarmData)] %>% sum(na.rm = T)
+alarmData[,(ncol(alarmData) - 4):ncol(alarmData)] %>% head
+alarmData[,(ncol(alarmData) - 4):ncol(alarmData)] %>% tail
 
@@
 ```{r realData_import}
-library(readr)
+# # If you start working in the vignette here, then load these.
+# # Otherwise, they were loaded on lines 88 and 529, respectively
+# library(magrittr)
+# library(tidyverse) # Includes readr
+# library(mvMonitoring)
+# library(xts)
 if(.Platform$OS.type == "windows"){
-  tenDayData_v2 <- read_csv("~/GitHub/mvMonitoring/mvMonitoring/inst/tenDayData_v2.csv", 
+  tenDayData_v2 <- read_csv("~/GitHub/mvMonitoring/inst/tenDayData_v2.csv", 
   col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
-currentDayData_v2 <- read_csv("~/GitHub/mvMonitoring/mvMonitoring/inst/currentDayData_v2.csv", 
+currentDayData_v2 <- read_csv("~/GitHub/mvMonitoring/inst/currentDayData_v2.csv", 
   col_types = cols(X1 = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
@@
 ```{r trainRealData}
-tenDayResults_ls <- mvMonitoring::mspTrain(data = tenDay_clean,
+tenDayResults_ls <- mspTrain(data = tenDay_clean,
                          labelVector = rep(1, nrow(tenDay_clean)),
@@
 
-realDataandFlags <- mvMonitoring::mspMonitor(observations = laggedOneDay,
+realDataandFlags <- mspMonitor(observations = laggedOneDay,
                                labelVector = rep(1, nrow(laggedOneDay)),
@@
 for(i in 1:nrow(realDataandFlags)){
-  realAlarmData[1:i,] <- mvMonitoring::mspWarning(realAlarmData[1:i,])
+  realAlarmData[1:i,] <- mspWarning(realAlarmData[1:i,])
 }
@@
 ```{r mspProcessEg}
+# If you start working in the vignette here, then load these.
+# Otherwise, they were loaded on lines 88 and 529, respectively
+library(magrittr)
+library(tidyverse) # Includes readr
+library(mvMonitoring)
+library(xts)
 simFaults_ls <- mspProcessData(faults = "All",
@@
 library(parallel) # use mclapply on Mac, parLapply on Windows
-library(tidyverse)
-library(xts)
 a <- Sys.time()
-cl <- makeCluster(getOption("cl.cores", 8))
+cl <- makeCluster(getOption("cl.cores", 5))
 clusterEvalQ(cl, library(tidyverse))
@@
 clusterEvalQ(cl, library(mvMonitoring))
-msadResults5_ls <- parLapply(cl = cl, 1:100, function(void){
+msadResults5_ls <- parLapply(cl = cl, 1:5, function(void){
 # msadResults2_ls <- mclapply(1:1000, mc.cores = 8L, function(void){
+# msadResults5_ls <- lapply(1:1, function(void){
 
   ##########   Draw a Random Data Set   ##########
-  msadpcaObs_ls <- mspProcessData(faults = c("NOC", "C1", "C2", "C3"), # "All"
+  msadpcaObs_ls <- mspProcessData(faults = "All",
                               faultStartIndex = 8500,
@@
                          function(mat){
+
     # Testing the apply statement
@@
     ## Time to first alarm
+    alarmCol <- ncol(msad_MS_Alarm)
     # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
@@
     # SPE
-    # All alarms: which(msad_MS_Alarm[1:2580,15] %in% c(2,3))
-    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(2,3))
+    # All alarms: which(msad_MS_Alarm[1:2580,alarmCol] %in% c(2,3))
+    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,alarmCol] %in% c(2,3))
     time2SPE_msad <- suppressWarnings(min(time2SPE_msad))
     # T2
-    # All alarms: which(msad_MS_Alarm[1:2580,15] %in% c(1,3))
-    time2T2_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(1,3))
+    # All alarms: which(msad_MS_Alarm[1:2580,alarmCol] %in% c(1,3))
+    time2T2_msad <- which(msad_MS_Alarm[1000:2580,alarmCol] %in% c(1,3))
     time2T2_msad <- suppressWarnings(min(time2T2_msad))
@@
     ## Time to first alarm
+    alarmCol <- ncol(ad_MS_Alarm)
     # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
     # SPE
-    # All alarms: which(ad_MS_Alarm[,15] %in% c(2,3))
-    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(2,3))
+    # All alarms: which(ad_MS_Alarm[,alarmCol] %in% c(2,3))
+    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,alarmCol] %in% c(2,3))
     time2SPE_ad <- suppressWarnings(min(time2SPE_ad))
     # T2
-    # All alarms: which(ad_MS_Alarm[,15] %in% c(1,3))
-    time2T2_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(1,3))
+    # All alarms: which(ad_MS_Alarm[,alarmCol] %in% c(1,3))
+    time2T2_ad <- which(ad_MS_Alarm[1000:2580,alarmCol] %in% c(1,3))
     time2T2_ad <- suppressWarnings(min(time2T2_ad))
@@
 }) %>% do.call(bind_rows, .)
-write_csv(ms_FA_rates4, path = "false_alarm_rates_ms_1000_20170323.csv")
+# write_csv(ms_FA_rates4, path = "false_alarm_rates_ms_1000_20170323.csv")
 ms_detectionTimes5 <- lapply(1:length(msadResults5_ls), function(i){
@@
 }) %>% do.call(bind_rows, .)
-write_csv(ms_detectionTimes4, path = "detection_times_ms_1000_20170323.csv")
+# write_csv(ms_detectionTimes4, path = "detection_times_ms_1000_20170323.csv")
 ```
@@
 # False Alarm Rates
-ms_FA_rates3[,1] %>% hist(xlim = c(0, 0.05), main = "MSAD SPE False Alarm Rates")
-ms_FA_rates3[,2] %>% hist(xlim = c(0, 0.05), main = "MSAD T2 False Alarm Rates")
-ms_FA_rates3[,3] %>% hist(xlim = c(0, 0.05), main = "AD SPE False Alarm Rates")
-ms_FA_rates3[,4] %>% hist(xlim = c(0, 0.05), main = "AD T2 False Alarm Rates")
+ms_FA_rates5[,1] %>% hist(xlim = c(0, 0.05), main = "MSAD SPE False Alarm Rates")
+ms_FA_rates5[,2] %>% hist(xlim = c(0, 0.05), main = "MSAD T2 False Alarm Rates")
+ms_FA_rates5[,3] %>% hist(xlim = c(0, 0.05), main = "AD SPE False Alarm Rates")
+ms_FA_rates5[,4] %>% hist(xlim = c(0, 0.05), main = "AD T2 False Alarm Rates")
 
@@
 # Fault 1A
-ms_detectionTimes3 %>%
+ms_detectionTimes5 %>%
   filter(Faults == "A1") %>%
@@
 # Fault 1B
-ms_detectionTimes3 %>%
+ms_detectionTimes5 %>%
   filter(Faults == "B1") %>%
@@
 # Fault 2A
-ms_detectionTimes3 %>%
+ms_detectionTimes5 %>%
   filter(Faults == "A2") %>%
@@
 # Fault 2B
-ms_detectionTimes3 %>%
+ms_detectionTimes5 %>%
   filter(Faults == "B2") %>%
@@
 # Fault 3A
-ms_detectionTimes3 %>%
+ms_detectionTimes5 %>%
   filter(Faults == "A3") %>%
@@
 # Fault 3B
-ms_detectionTimes3 %>%
+ms_detectionTimes5 %>%
   filter(Faults == "B3") %>%
@@
 ```{r trueSingleState_sim, message = FALSE}
-library(parallel) # use mclapply on Mac, parLapply on Windows
-library(tidyverse)
-library(xts)
+# library(parallel) # use mclapply on Mac, parLapply on Windows
+# library(tidyverse)
+# library(xts)
 a <- Sys.time()
-cl <- makeCluster(getOption("cl.cores", 8))
+cl <- makeCluster(getOption("cl.cores", 5))
 clusterEvalQ(cl, library(tidyverse))
@@
 clusterEvalQ(cl, library(mvMonitoring))
-adResults3_ls <- parLapply(cl = cl, 1:1000, function(void){
+adResults3_ls <- parLapply(cl = cl, 1:5, function(void){
 # adResults_ls <- mclapply(1:1000, mc.cores = 8L, function(void){
@@
     # SPE
-    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(2,3))
+    time2SPE_msad <- which(msad_MS_Alarm[1000:2580,alarmCol] %in% c(2,3))
     time2SPE_msad <- suppressWarnings(min(time2SPE_msad))
     # T2
-    time2T2_msad <- which(msad_MS_Alarm[1000:2580,15] %in% c(1,3))
+    time2T2_msad <- which(msad_MS_Alarm[1000:2580,alarmCol] %in% c(1,3))
     time2T2_msad <- suppressWarnings(min(time2T2_msad))
@@
     ## Time to first alarm
+    alarmCol <- ncol(msad_MS_Alarm)
     # Alarm code: 1 = T2 alarm; 2 = SPE alarm; 3 = both
     # SPE
-    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(2,3))
+    time2SPE_ad <- which(ad_MS_Alarm[1000:2580,alarmCol] %in% c(2,3))
     time2SPE_ad <- suppressWarnings(min(time2SPE_ad))
     # T2
-    time2T2_ad <- which(ad_MS_Alarm[1000:2580,15] %in% c(1,3))
+    time2T2_ad <- which(ad_MS_Alarm[1000:2580,alarmCol] %in% c(1,3))
     time2T2_ad <- suppressWarnings(min(time2T2_ad))
@@
 ```{r adSim_Cleaning}
-ss_FA_rates <- lapply(1:length(adResults_ls), function(i){
+ss_FA_rates <- lapply(1:length(adResults3_ls), function(i){
   adResults3_ls[[i]]$falseAlarmRates
 }) %>% do.call(bind_rows, .)
-write_csv(ss_FA_rates, path = "false_alarm_rates_ss_1000_20170320.csv")
-ss_detectionTimes <- lapply(1:length(adResults_ls), function(i){
+# write_csv(ss_FA_rates, path = "false_alarm_rates_ss_1000_20170320.csv")
+ss_detectionTimes <- lapply(1:length(adResults3_ls), function(i){
   adResults3_ls[[i]]$time2Detect
 }) %>% do.call(bind_rows, .)
-write_csv(ss_detectionTimes, path = "detection_times_ss_1000_20170320.csv")
+# write_csv(ss_detectionTimes, path = "detection_times_ss_1000_20170320.csv")
 ```

### 2023-06-29 R/fault1A_xts.R

@@ -28,5 +28,5 @@
 #'   (0.25 * x, 0.1 * y , 0.75 * z).}
 #' }
 #' See the vignette for more details.
-#' @source Simluated in R.
+#' @source Simulated in R.
 "fault1A_xts"

### 2023-06-29 R/fault2A_xts.R

@@ -28,5 +28,5 @@
 #'   (0.25 * x, 0.1 * y , 0.75 * z).}
 #' }
 #' See the vignette for more details.
-#' @source Simluated in R.
+#' @source Simulated in R.
 "fault2A_xts"

### 2023-06-29 R/fault3A_xts.R

@@ -7,7 +7,7 @@
 #' @format An xts data matrix with 10080 rows and four columns, corresponding to
 #'   one week worth of data recorded at a 1-minute interval. The columns under
 #'   normal conditions are defined in the help file for normal_switch_xts. The
-#'   fault is a signal amplificaton in the underlying determining t vector. The
+#'   fault is a signal amplification in the underlying determining t vector. The
 #'   fault starts at row 8500, and the four columns under the fault state are
 #'   defined here:
 #' \itemize{
@@ -29,5 +29,5 @@
 #'   (0.25 * x, 0.1 * y , 0.75 * z).}
 #' }
 #' See the vignette for more details.
-#' @source Simluated in R.
+#' @source Simulated in R.
 "fault3A_xts"

### 2023-06-29 R/faultSwitch.R

@@ -83,7 +83,7 @@
 #'     }
 #'     This drift is applied only in State 2.
 #'   }
-#'   \item{A3 -- }{The fault is a signal amplificaton in the determining latent
+#'   \item{A3 -- }{The fault is a signal amplification in the determining latent
 #'     t vector. The fault starts at "faultStartIndex", and the x, y, and z
 #'     features under the fault state are defined here: \itemize{
 #'       \item{x : }{x(t_*) = t_* + error}
@@ -93,7 +93,7 @@
 #'     where t_* = 5 x t x (period - s) / (period - faultStartIndex) and s is
 #'     the observation index.
 #'   }
-#'   \item{B3 -- }{The fault is a signal amplificaton in the determining latent
+#'   \item{B3 -- }{The fault is a signal amplification in the determining latent
 #'     t vector for the "z" feature only. The fault starts at "faultStartIndex",
 #'     and the x, y, and z features under the fault state are defined here:
 #'     \itemize{

### 2023-06-29 R/mspMonitor.R

@@ -120,7 +120,7 @@ mspMonitor <- function(observations,
     xx <- cbind(classData[i,], faultObj)
     data.frame(dateTime = index(xx), xx[,-1])
   })
-  # Use ldply instead of do.call(rbind, .) becuase rbind.xts() can't handle the
+  # Use ldply instead of do.call(rbind, .) because rbind.xts() can't handle the
   # object size necessary to bind a large list.
   obsAndFlags <- ldply(dataAndFaults)
   obsAndFlags <- xts(obsAndFlags[,-1], order.by = obsAndFlags[,1])

### 2023-06-29 R/mspSubset.R

@@ -39,7 +39,7 @@ mspSubset <- function(data,
   # Is data an xts object?
    if(!is.xts(data)){
     stop("Object 'data' is not an xts object. Please transform your data to an
-         extendible time series.")
+         extendable time series.")
   }
 
   # What are the states?

### 2023-06-29 R/mspTrain.R

@@ -63,7 +63,7 @@
 #'   estimation to calculate the 1 - alpha quantiles of the SPE and Hotelling's
 #'   T2 statistics from a set of training observations, then flags any
 #'   observation in the testing data set with process monitoring statistics
-#'   beyond these calculated critical values. Becuase of natural variablity
+#'   beyond these calculated critical values. Because of natural variability
 #'   inherent in all real data, we do not remove observations simply because
 #'   they are have been flagged as outside normal operating conditions. This
 #'   function records an alarm only for observations having five flags in a
@@ -71,7 +71,7 @@
 #'   alarm-positive observations are then removed from the data set and held in
 #'   a separate xts matrix for inspection.
 #'
-#'   Concering the lagsIncluded variable: the argument lagsIncluded = c(0,1)
+#'   Concerning the lagsIncluded variable: the argument lagsIncluded = c(0,1)
 #'   will column concatenate the current data with the same data from one
 #'   discrete time step back. This will necessarily remove the first row of the
 #'   data matrix, as we will have NA values under the lagged features. The
@@ -79,9 +79,9 @@
 #'   observations with the observations from one step previous and the
 #'   observations from two steps previous, which will necessarily require the
 #'   removal of the first two rows of the data matrix. To include only certain
-#'   lags with the current data, specify lagsIncluded = c(0, lag_1, lag_2, ... ,
-#'   lag_K). This induce NA values in the first max(lag_k) rows, for k = 1, ...
-#'   , K, and these rows will be removed from consideration. From the lag.xts()
+#'   lags with the current data, specify lagsIncluded = c(0, lag_1, lag_2, ...,
+#'   lag_K). This induce NA values in the first max(lag_k) rows, for k = 1, ...,
+#'   K, and these rows will be removed from consideration. From the lag.xts()
 #'   function helpfile: "The primary motivation for having methods specific to
 #'   xts was to make use of faster C-level code within xts. Additionally, it was
 #'   decided that lag's default behavior should match the common time-series
@@ -149,7 +149,7 @@ mspTrain <- function(data,
 
   if(!is.xts(data)){
     stop("Object 'data' is not an xts object. Please transform your data to an
-         extendible time series.")
+         extendable time series.")
   }
 
   # Lag the data

### 2023-06-29 R/mvMonitoring.R

@@ -6,7 +6,7 @@
 #'   external use, all of which begin with the string "msp" (for "multivariate
 #'   statistical process") followed by the function use. Functions without this
 #'   "msp" key are primarily internal functions. They are available to see and
-#'   use, but will largely be uneccesary to call in common workflows.
+#'   use, but will largely be unnecessary to call in common workflows.
 #'
 #' @section \code{mvMonitoring} external functions:
 #'   \itemize{
@@ -15,7 +15,7 @@
 #'     }
 #'     \item{\code{\link{mspTrain}} - }{A function to take in observations for
 #'       training under normal conditions, and to return the training summary
-#'       fromt these observations.
+#'       from these observations.
 #'     }
 #'     \item{\code{\link{mspMonitor}} - }{A function to take in real-time
 #'       process observations and detect system anomalies based on the training

### 2023-06-29 R/normal_switch_xts.R

@@ -24,5 +24,5 @@
 #'   (0.25 * x, 0.1 * y , 0.75 * z).}
 #' }
 #' See the vignette for more details.
-#' @source Simluated in R.
+#' @source Simulated in R.
 "normal_switch_xts"

### 2023-06-29 R/processNOCdata.R

@@ -9,7 +9,7 @@
 #'   minute-level observations (10,080 observations).
 #' @param stateDuration The number of observations generated during a stay in
 #'   each state. Defaults to 60.
-#' @param increment The time-sequence base increment. See "Deatails" of the
+#' @param increment The time-sequence base increment. See "Details" of the
 #'   seq.POSIXt() function options. Defaults to "min" for minutes.
 #' @param multiState Should the observations be generated from a multi-state
 #'   process? Defaults to TRUE.

### 2023-06-29 R/rotateScaleMatrix.R

@@ -4,15 +4,15 @@
 #'   negative degree changes in yaw, pitch, and / or roll and increment or
 #'   decrement feature scales.
 #'
-#' @param rot_angles a list or vector containg the rotation angles in the order
-#'   following: yaw, pitch, roll. Defaults to <0,0,0>.
+#' @param rot_angles a list or vector containing the rotation angles in the
+#'   order following: yaw, pitch, roll. Defaults to <0,0,0>.
 #' @param scale_factors a list or vector containing the values by which to
 #'   multiply each dimension. Defaults to <1,1,1>.
 #'
 #' @return A 3 x 3 projection matrix corresponding to the degree and scale
 #'   changes entered.
 #'
-#' @details See the help file of function rotate_3D() for a brief explination of
+#' @details See the help file of function rotate_3D() for a brief explanation of
 #'   how these angles behave in scatterplot3d functionality (from package
 #'   scatterplot3d).
 #'

### 2023-06-29 R/rotationMatrix.R

@@ -12,9 +12,9 @@
 #'
 #' @return A 3 x 3 projection matrix corresponding to the degree changes entered.
 #'
-#' @details When plotting with the package scatterplot3d, the default perpective
-#'   is such that the pitch action appears as a roll while the roll action
-#'   appears as a pitch.
+#' @details When plotting with the package scatterplot3d, the default
+#'   perspective is such that the pitch action appears as a roll while the roll
+#'   action appears as a pitch.
 #'
 #'   This function is used only in data generation of the package vignette. This
 #'   function is called by rotateScale3D().
